### 2023-03-07 README.qmd
Initial commit

---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.retina = 3
)

library(emoji)
```

# Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space

<!-- badges: start -->
<!-- badges: end -->

### `r emoji_glue(":smiling_face_with_halo::fish:")`: Note on "truthful tuna" project name

Because project titles change all the time with revisions, rewriting, and peer review, I used [**codename**](http://svmiller.com/codename/) to generate an [Ubuntu-style](https://wiki.ubuntu.com/DevelopmentCodeNames) internal-to-me project name that won't change.

```{r generate-code-name, eval=FALSE}
library(codename)
codename_message()
#> code name generated by {codename} v.0.4.0

codename(seed = "amicable contempt", type = "ubuntu")
#> [1] "truthful tuna"
```

## Licenses

**Text and figures:** All prose and images are licensed under Creative Commons ([CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)).

**Code:** All code is licensed under the [MIT License](LICENSE.md).

## Contributions and Code of Conduct

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

### 2023-03-07 manuscript/manuscript.qmd
Add separate folder for manuscript

---
title: "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
link-citations: true
format: 
  html:
    toc: true
  pdf: default
  docx: default
language: 
  title-block-published: "Latest version"
---

Lorem ipsum dolor sit amet, consectetur adipisicing elit [@Mayer:2010], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

## References

### 2023-03-07 _targets.R
Start targets + renv

@@ -1,0 +1,33 @@
+library(targets)
+library(tarchetypes)
+library(tibble)
+
+# Set the _targets store so that scripts in subdirectories can access targets
+# without using withr::with_dir() (see https://github.com/ropensci/targets/discussions/885)
+#
+# This hardcodes the absolute path in _targets.yaml, so to make this more
+# portable, we rewrite it every time this pipeline is run (and we don't track
+# _targets.yaml with git)
+tar_config_set(store = here::here('_targets'),
+               script = here::here('_targets.R'))
+
+options(tidyverse.quiet = TRUE,
+        dplyr.summarise.inform = FALSE)
+
+set.seed(71215)  # From random.org
+
+tar_option_set(packages = c("tidyverse"),
+               format = "qs")
+
+# here::here() returns an absolute path, which then gets stored in tar_meta and
+# becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
+# There's no way to get a relative path directly out of here::here(), but
+# fs::path_rel() works fine with it (see
+# https://github.com/r-lib/here/issues/36#issuecomment-530894167)
+here_rel <- function(...) {fs::path_rel(here::here(...))}
+
+
+# Actual pipeline ---------------------------------------------------------
+list(
+  tar_target(data, data.frame(x = sample.int(100), y = sample.int(100)))
+)

### 2023-05-07 manuscript/manuscript.qmd
Use separate profiles + word count

@@
 title: "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
+short-title: "Amicable Contempt"
 author:
@@
 bibliography: references.bib
-link-citations: true
-format: 
-  html:
-    toc: true
-  pdf: default
-  docx: default
-language: 
-  title-block-published: "Latest version"
 ---
@@
 
-## References
+# References

### 2023-05-07 _targets.R
Build dual manuscript outputs with targets

@@ -29,5 +29,6 @@ here_rel <- function(...) {fs::path_rel(here::here(...))}
 
 # Actual pipeline ---------------------------------------------------------
 list(
-  tar_target(data, data.frame(x = sample.int(100), y = sample.int(100)))
+  tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
+  tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms")
 )

### 2023-05-07 manuscript/appendix.qmd
Add appendix placeholder

---
title: 'Online appendix for "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"'
short-title: 'Online appendix for "Amicable Contempt"'
author:
- name: Andrew Heiss
  affiliation: Georgia State University
  email: aheiss@gsu.edu
  orcid: 0000-0002-3948-3914
bibliography: references.bib
crossref: 
  tbl-title: Appendix Table
  fig-title: Appendix Figure
---

Here's the appendix

```{r warning=FALSE, message=FALSE}
library(gt)

mtcars |>
  gt()
```

### 2023-05-07 notebook/paper.qmd
Rename to "paper"

---
title: Paper
toc: false
page-layout: full
---

<p class="text-center"><a class="btn btn-success" href="/manuscript/output/manuscript.html" target="manuscript">{{< fa file-lines >}} &ensp;HTML</a> <a class="btn btn-success" href="/manuscript/output/manuscript.html" target="_blank">{{< fa arrow-up-right-from-square >}} &ensp;HTML (new window)</a> <a class="btn btn-success" href="/manuscript/output/manuscript.pdf" target="manuscript">{{< fa file-pdf >}} &ensp;PDF</a> <a class="btn btn-success" target="_blank" href="/manuscript/output/manuscript.pdf">{{< fa file-arrow-down >}} &ensp;PDF (download)</a></p>

<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:150%;width:100%;border:2px solid #ccc;" height="100%" width="100%" name="manuscript"></iframe>

### 2023-05-07 notebook/paper.qmd
Generate paper links automatically

@@
 
-<p class="text-center"><a class="btn btn-success" href="/manuscript/output/manuscript.html" target="manuscript">{{< fa file-lines >}} &ensp;HTML</a> <a class="btn btn-success" href="/manuscript/output/manuscript.html" target="_blank">{{< fa arrow-up-right-from-square >}} &ensp;HTML (new window)</a> <a class="btn btn-success" href="/manuscript/output/manuscript.pdf" target="manuscript">{{< fa file-pdf >}} &ensp;PDF</a> <a class="btn btn-success" target="_blank" href="/manuscript/output/manuscript.pdf">{{< fa file-arrow-down >}} &ensp;PDF (download)</a></p>
+```{r include=FALSE}
+library(dplyr)
+library(glue)
 
-<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:150%;width:100%;border:2px solid #ccc;" height="100%" width="100%" name="manuscript"></iframe>
+links_to_include <- tribble(
+  ~title, ~path, 
+    ~icon, ~btn_class, ~target,
+  "HTML", "/manuscript/output/manuscript.html", 
+    '<i class="fa-solid fa-file-lines"></i>', "btn-success", "manuscript",
+  "HTML <small>(new window)</small>", "/manuscript/output/manuscript.html", 
+    '<i class="fa-solid fa-arrow-up-right-from-square"></i>', "btn-success", "_blank",
+  "PDF", "/manuscript/output/manuscript.pdf", 
+    '<i class="fa-solid fa-file-pdf"></i>', "btn-danger", "manuscript",
+  "PDF <small>(new window)</small>", "/manuscript/output/manuscript.pdf", 
+    '<i class="fa-solid fa-file-arrow-down"></i>', "btn-danger", "_blank",
+  "Manuscripty PDF", "/manuscript/output-ms/manuscript.pdf", 
+    '<i class="fa-solid fa-file-pdf"></i>', "btn-warning", "manuscript",
+  "Manuscript PDF <small>(new window)</small>", "/manuscript/output-ms/manuscript.pdf", 
+    '<i class="fa-solid fa-file-arrow-down"></i>', "btn-warning", "_blank"
+) %>% 
+  mutate(nice_link = glue(
+    '<a class="btn [btn_class] btn-sm mb-1" href="[path]" target="[target]">',
+    '[icon] &ensp;[title]',
+    '</a>', .open = "[", .close = "]"
+  ))
+
+links <- paste(links_to_include$nice_link, collapse = "\n")
+```
+
+```{=html}
+<p class="text-center">
+  `r links`
+</p>
+
+<iframe src="/manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="manuscript"></iframe>
+```

### 2023-05-07 notebook/appendix.qmd
Add appendix page

---
title: Appendix
toc: false
page-layout: full
---

```{r include=FALSE}
library(dplyr)
library(glue)

links_to_include <- tribble(
  ~title, ~path, 
    ~icon, ~btn_class, ~target,
  "HTML", "/manuscript/output/appendix.html", 
    '<i class="fa-solid fa-file-lines"></i>', "btn-success", "appendix",
  "HTML <small>(new window)</small>", "/manuscript/output/appendix.html", 
    '<i class="fa-solid fa-arrow-up-right-from-square"></i>', "btn-success", "_blank",
  "PDF", "/manuscript/output/appendix.pdf", 
    '<i class="fa-solid fa-file-pdf"></i>', "btn-danger", "appendix",
  "PDF <small>(new window)</small>", "/manuscript/output/appendix.pdf", 
    '<i class="fa-solid fa-file-arrow-down"></i>', "btn-danger", "_blank",
  "Manuscripty PDF", "/manuscript/output-ms/appendix.pdf", 
    '<i class="fa-solid fa-file-pdf"></i>', "btn-warning", "appendix",
  "Manuscript PDF <small>(new window)</small>", "/manuscript/output-ms/appendix.pdf", 
    '<i class="fa-solid fa-file-arrow-down"></i>', "btn-warning", "_blank"
) %>% 
  mutate(nice_link = glue(
    '<a class="btn [btn_class] btn-sm mb-1" href="[path]" target="[target]">',
    '[icon] &ensp;[title]',
    '</a>', .open = "[", .close = "]"
  ))

links <- paste(links_to_include$nice_link, collapse = "\n")
```

```{=html}
<p class="text-center">
  `r links`
</p>

<iframe src="/manuscript/output/appendix.html" frameborder="0" style="overflow:hidden;height:90%;width:100%;border:2px solid #ccc;" height="90%" width="100%" name="appendix"></iframe>
```

### 2023-05-07 _targets.R
Add target for building and deploying site

@@ -29,6 +29,16 @@ here_rel <- function(...) {fs::path_rel(here::here(...))}
 
 # Actual pipeline ---------------------------------------------------------
 list(
+  ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
-  tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms")
+  tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),
+  
+  tar_quarto(website, path = ".", quiet = FALSE),
+  tar_target(deploy_script, here_rel("deploy.sh"), format = "file"),
+  tar_target(deploy, {
+    # Force a dependency
+    website
+    # Run the deploy script
+    if (Sys.getenv("UPLOAD_WEBSITES") == "TRUE") processx::run(paste0("./", deploy_script))
+  })
 )

### 2023-05-07 deploy.sh

@@ -1,0 +1,7 @@
+REMOTE_HOST="cloud"
+REMOTE_DIR="~/sites/stats/public_html/truthful-tuna"
+REMOTE_DEST=$REMOTE_HOST:$REMOTE_DIR
+
+echo "Uploading new changes to remote server..."
+echo
+rsync -crvP --exclude '*_cache' --delete _site/ $REMOTE_DEST

### 2023-05-09 R/funs_data.R
Target-ify data cleaning and processing

@@ -1,0 +1,59 @@
+clean_survey_orgs <- function(path) {
+  x <- readRDS(path)
+  
+  return(x)
+}
+
+clean_survey_countries <- function(path) {
+  x <- readRDS(path) %>% 
+    mutate(Q4.4_collapsed =
+             fct_recode(Q4.4, Registered = "Yes", `Not registered` = "No", 
+                        NULL = "Don't know"),
+           Q4.4_collapsed = ordered(Q4.4_collapsed)) %>%
+    mutate(Q4.11_collapsed = 
+             fct_collapse(Q4.11,
+                          Negative = c("Extremely negative", "Somewhat negative"),
+                          Neither = c("Neither positive nor negative"),
+                          Positive = c("Somewhat positive", "Extremely positive"),
+                          NULL = c("Don't know", "Prefer not to answer")),
+           Q4.11_collapsed = ordered(fct_na_level_to_value(
+             Q4.11_collapsed, 
+             extra_levels = c("Don't know", "Prefer not to answer")))) %>%
+    mutate(Q4.13_collapsed = 
+             fct_collapse(Q4.13,
+                          "Very familiar" = c("Extremely familiar", "Very familiar"),
+                          "Somewhat familiar" = c("Moderately familiar", "Slightly familiar"),
+                          "Not familiar at all" = c("Not familiar at all")),
+           Q4.13_collapsed = ordered(fct_na_level_to_value(
+             Q4.13_collapsed, 
+             extra_levels = c("Don't know")))) %>%
+    mutate(Q4.14_collapsed = 
+             fct_collapse(Q4.14,
+                          "At least once a year" = c("Once a month", "Once a year"),
+                          "Once every few years" = c("Once every few years"),
+                          "Rarely or never" = c("Rarely", "Never"),
+                          NULL = c("Don't know")),
+           Q4.14_collapsed = ordered(fct_na_level_to_value(
+             Q4.14_collapsed, 
+             extra_levels = c("Don't know")))) %>%
+    mutate(Q4.17_collapsed = 
+             fct_collapse(Q4.17,
+                          "Not restricted" = c("Not restricted at all"),
+                          "Very restricted" = c("Very restricted",
+                                                "Extremely restricted"),
+                          NULL = c("Don’t know")),
+           Q4.17_collapsed = ordered(fct_na_level_to_value(
+             Q4.17_collapsed, 
[…]

### 2023-05-09 _targets.R

@@ -26,9 +26,28 @@ tar_option_set(packages = c("tidyverse"),
 # https://github.com/r-lib/here/issues/36#issuecomment-530894167)
 here_rel <- function(...) {fs::path_rel(here::here(...))}
 
+# Load R scripts with functions to use in the pipeline
+lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
 
 # Actual pipeline ---------------------------------------------------------
 list(
+  ## Raw data files ----
+  tar_target(survey_orgs_file, 
+             here_rel("data", "raw-data", "survey_orgs_clean.rds"), 
+             format = "file"),
+  tar_target(survey_countries_file, 
+             here_rel("data", "raw-data", "survey_countries_clean.rds"), 
+             format = "file"),
+  tar_target(naturalearth_raw_file,
+             here_rel("data", "raw-data", "ne_110m_admin_0_countries",
+                      "ne_110m_admin_0_countries.shp"),
+             format = "file"),
+  
+  ## Process and clean data ----
+  tar_target(survey_orgs, clean_survey_orgs(survey_orgs_file)),
+  tar_target(survey_countries, clean_survey_countries(survey_countries_file)),
+  tar_target(world_map, load_world_map(naturalearth_raw_file)),
+  
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
   tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),

### 2023-05-09 R/funs_graphics.R
Target-ify graphics stuff

@@ -1,0 +1,52 @@
+# https://carto.com/carto-colors/
+clrs <- list(Prism = rcartocolor::carto_pal(n = 12, "Prism"),
+             PurpOr = rcartocolor::carto_pal(7, "PurpOr"),
+             Emrld = rcartocolor::carto_pal(7, "Emrld"),
+             Teal = rcartocolor::carto_pal(7, "Teal"),
+             Peach = rcartocolor::carto_pal(7, "Peach"),
+             Sunset = rcartocolor::carto_pal(7, "Sunset"))
+
+set_annotation_fonts <- function() {
+  ggplot2::update_geom_defaults("label", list(family = "Fira Sans", face = "plain"))
+  ggplot2::update_geom_defaults("text", list(family = "Fira Sans", face = "plain"))
+}
+
+theme_ingo <- function(base_size = 11, base_family = "Fira Sans") {
+  ret <- theme_bw(base_size, base_family) +
+    theme(panel.background = element_rect(fill = "#ffffff", colour = NA),
+          title = element_text(size = rel(1), family = "Fira Sans", face = "bold"),
+          plot.subtitle = element_text(size = rel(0.8),
+                                       family = "Fira Sans", face = "plain"),
+          plot.caption = element_text(margin = margin(t = 10), size = rel(0.6),
+                                      family = "Fira Sans", face = "plain"),
+          panel.border = element_rect(color = "grey50", fill = NA, linewidth = 0.15),
+          panel.spacing = unit(1, "lines"),
+          panel.grid.minor = element_blank(),
+          panel.grid.major = element_line(linewidth = 0.25, colour = "grey90"),
+          axis.line = element_blank(),
+          axis.ticks = element_blank(),
+          axis.title = element_text(size = rel(0.8),
+                                    family = "Fira Sans", face = "bold"),
+          axis.title.x = element_text(hjust = 0, margin = margin(t = 10)),
+          axis.title.y = element_text(hjust = 1, margin = margin(r = 10)),
+          legend.position = "bottom",
+          legend.title = element_text(size = rel(0.7), vjust = 0.5,
+                                      family = "Fira Sans", face = "plain"),
+          legend.key.size = unit(0.7, "line"),
+          legend.key = element_blank(),
+          legend.spacing = unit(0.1, "lines"),
+          legend.justification = "left",
+          legend.margin = margin(t = -5, b = 0, l = 0, r = 0),
+          strip.text = element_text(size = rel(0.9), hjust = 0,
[…]

### 2023-05-09 _targets.R

@@ -48,6 +48,9 @@ list(
   tar_target(survey_countries, clean_survey_countries(survey_countries_file)),
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
   
+  ## Graphics ----
+  tar_target(graphic_functions, lst(theme_ingo, theme_ingo_map, set_annotation_fonts, clrs)),
+  
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
   tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),

### 2023-05-09 notebook/descriptive.qmd
Start descriptive stuff

---
title: "Descriptive stuff"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE,
                      dev = "ragg_png")

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(sf)
library(scales)
library(gt)
library(here)

tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(survey_orgs, survey_countries))
tar_load(c(world_map))

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
```

# General respondent details

## How many NGOs responded?

```{r summary-n-respondents}
#| code-fold: show
nrow(survey_orgs)
```

## How many respondents answered questions for more than one country?

```{r summary-n-multiple-countries}
#| code-fold: show
survey_countries %>% 
  summarize(more_than_1 = sum(loop.number > 1),
            prop = more_than_1 / nrow(survey_orgs))
```

## Who in the organization responded to the survey?

```{r plot-respondents-who, fig.width=6, fig.height=3}
df_plot_respondents <- survey_orgs %>%
  group_by(Q2.3) %>%
  summarise(num = n()) %>%
  arrange(num) %>% 
  mutate(question = fct_inorder(Q2.3))

df_plot_respondents %>% 
  ggplot(aes(x = num, y = question)) +
  geom_col() +
  scale_x_continuous(expand = c(0, 0),
                     sec.axis = sec_axis(~ . / sum(df_plot_respondents$num),
                                         labels = label_percent())) +
  labs(x = "Respondents", y = NULL,
       title = "Who filled out the survey?",
       subtitle = "Q2.3: What is your position in your organization?") +
  theme_ingo()
```

Lots of others. Who are the others?

```{r tb-who-responded-others}
survey_orgs %>%
  filter(!is.na(Q2.3_TEXT)) %>%
  mutate(`Position in organization` = str_to_title(Q2.3_TEXT)) %>%
  group_by(`Position in organization`) %>%
  summarise(Count = n()) %>%
  mutate(Proportion = Count / sum(Count)) %>%
  arrange(desc(Count)) %>% 
  gt() %>% 
  fmt_percent(columns = Proportion, decimals = 1) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
  opt_table_font(font = "Fira Sans")
```

# Where are NGOs based?

```{r process-map}
df_hq_countries <- survey_orgs %>% 
  group_by(Q2.2_iso3) %>% 
  summarize(num_ngos = n()) %>% 
  mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA))

map_hq <- world_map %>% 
  left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3))
```

```{r plot-map-respondents-gradient}
ggplot() +
  geom_sf(data = map_hq, aes(fill = num_ngos_ceiling),
          linewidth = 0.1, color = "grey30") +
  scale_fill_binned(low = clrs$Peach[1], high = clrs$Peach[7], na.value = "grey95",
                    labels = c(1, 10, 20, "30+"), breaks = c(1, 10, 20, 30),
                    name = "Number of NGOs: ",
                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
                                             title.vjust = 1)) +
  coord_sf(crs = "+proj=robin") +
  theme_ingo_map()
```

```{r plot-map-respondents-binary}
ggplot() +
  geom_sf(data = map_hq, aes(fill = ngo_presence),
          linewidth = 0.1, color = "grey30") +
  scale_fill_manual(values = c(clrs$Peach[7], "grey95"), 
                    na.value = "grey95", na.translate = FALSE,
                    name = NULL) +
  coord_sf(crs = "+proj=robin") +
  theme_ingo_map()
```

# Where do NGOs work?

# What do these NGOs do?

### 2023-05-09 notebook/descriptive.qmd
Finish "Where are NGOs based" section

@@
 library(sf)
+library(countrycode)
 library(scales)
@@
 
-```{r tb-who-responded-others}
+```{r tab-who-responded-others}
 survey_orgs %>%
@@
 
-```{r process-map}
+## How are these NGOs distributed by HQ?
+
+```{r tab-hq-countries}
 df_hq_countries <- survey_orgs %>% 
@@
   mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
-         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA))
+         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA),
+         prop = num_ngos / sum(num_ngos)) %>% 
+  mutate(country_name = countrycode(Q2.2_iso3, "iso3c", "country.name")) %>%
+  arrange(desc(num_ngos))
 
+df_hq_countries %>% 
+  select(country_name, Q2.2_iso3, num_ngos, prop) %>%
+  gt() %>% 
+  cols_label(
+    country_name = "Country name",
+    Q2.2_iso3 = "ISO3",
+    num_ngos = "NGOs",
+    prop = "Proportion"
+  ) %>% 
+  fmt_percent(columns = prop, decimals = 1) %>% 
+  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
+  opt_table_font(font = "Fira Sans")
+```
+
+## Number of unique HQ countries
+
+```{r}
+#| code-fold: show
+df_hq_countries %>% 
+  summarize(total = sum(num_ngos >= 1))
+```
+
+## Regional distribution of HQ countries
+
+```{r tab-hq-regions}
+df_hq_regions <- df_hq_countries %>%
+  mutate(region = countrycode(Q2.2_iso3, "iso3c", "continent"),
+         region = ifelse(Q2.2_iso3 == "TWN", "Asia", region)) %>%
+  mutate(region = recode(region, Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania")) %>%
+  group_by(region) %>%
+  summarise(num = sum(num_ngos)) %>% ungroup() %>%
+  mutate(prop = num / sum(num)) %>%
+  arrange(desc(num)) %>%
+  mutate(region = fct_rev(fct_inorder(region)))
+
+df_hq_regions %>% 
+  gt() %>% 
+  cols_label(
+    region = "Region",
+    num = "NGOs",
+    prop = "Proportion"
+  ) %>% 
+  fmt_percent(columns = prop, decimals = 1) %>% 
+  cols_align(align = "left", columns = region) %>% 
+  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, 
+                  use_pagination = FALSE, use_pagination_info = FALSE) %>% 
+  opt_table_font(font = "Fira Sans")
+```
+
+```{r plot-hq-regions, fig.width=6, fig.height=3}
+ggplot(df_hq_regions, aes(x = num, y = region)) +
+  geom_pointrange(aes(xmin = 0, xmax = num)) +
+  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_hq_regions$num),
+                                         labels = label_percent())) +
+  labs(x = "Respondents based in region", y = NULL,
+       title = "Region of headquarters",
+       subtitle = "Q2.2: Where is your organization's headquarters? (summarized by region)") +
+  theme_ingo() + 
+  theme(panel.grid.major.y = element_blank())
+```
+
+## Responses per country (30 NGO ceiling)
+
+```{r plot-map-respondents-gradient}
 map_hq <- world_map %>% 
   left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3))
-```
 
-```{r plot-map-respondents-gradient}
 ggplot() +
@@
 ```
+
+## Countries with at least one response
 

### 2023-05-09 R/funs_data.R
Add full data as target

@@ -1,9 +1,26 @@
-clean_survey_orgs <- function(path) {
-  x <- readRDS(path)
+# Country-based data (*with* the Q4 loop)
+clean_survey_all <- function(path) {
+  x <- readRDS(path) %>% 
+    mutate(small_org = Q3.4.num <= 50,
+           small_org = factor(small_org, levels = c(TRUE, FALSE),
+                              labels = c("0–50 employees", "51+ employees"),
+                              ordered = TRUE)) 
   
   return(x)
 }
 
+# Organization-based data (without the Q4 loop)
+clean_survey_orgs <- function(path) {
+  x <- readRDS(path) %>% 
+    mutate(small_org = Q3.4.num <= 50,
+           small_org = factor(small_org, levels = c(TRUE, FALSE),
+                              labels = c("0–50 employees", "51+ employees"),
+                              ordered = TRUE)) 
+  
+  return(x)
+}
+
+# Country-based data (only the Q4 loop)
 clean_survey_countries <- function(path) {
   x <- readRDS(path) %>% 
     mutate(Q4.4_collapsed =

### 2023-05-09 _targets.R

@@ -38,6 +38,9 @@ list(
   tar_target(survey_countries_file, 
              here_rel("data", "raw-data", "survey_countries_clean.rds"), 
              format = "file"),
+  tar_target(survey_all_file, 
+             here_rel("data", "raw-data", "survey_clean_all.rds"), 
+             format = "file"),
   tar_target(naturalearth_raw_file,
              here_rel("data", "raw-data", "ne_110m_admin_0_countries",
                       "ne_110m_admin_0_countries.shp"),
@@ -46,6 +49,7 @@ list(
   ## Process and clean data ----
   tar_target(survey_orgs, clean_survey_orgs(survey_orgs_file)),
   tar_target(survey_countries, clean_survey_countries(survey_countries_file)),
+  tar_target(survey_all, clean_survey_all(survey_all_file)),
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
   
   ## Graphics ----

### 2023-05-09 notebook/descriptive.qmd
Add where NGOs work section

@@
 library(gt)
+library(skimr)
+library(ggalluvial)
 library(here)
@@
 
-tar_load(c(survey_orgs, survey_countries))
+tar_load(c(survey_orgs, survey_countries, survey_all))
 tar_load(c(world_map))
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+set_annotation_fonts()
+
+opts_int <- function(x, ...) {
+  x %>% 
+    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
+}
+
+opts_theme <- function(x) {
+  x %>% 
+    opt_table_font(font = "Fira Sans")
+}
 ```
@@
   fmt_percent(columns = Proportion, decimals = 1) %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
-  opt_table_font(font = "Fira Sans")
+  opts_int() %>% opts_theme()
 ```
@@
   summarize(num_ngos = n()) %>% 
+  ungroup() %>% 
   mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
          ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA),
-         prop = num_ngos / sum(num_ngos)) %>% 
+         prop = num_ngos / sum(num_ngos, na.rm = TRUE)) %>% 
   mutate(country_name = countrycode(Q2.2_iso3, "iso3c", "country.name")) %>%
@@
   fmt_percent(columns = prop, decimals = 1) %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE) %>% 
-  opt_table_font(font = "Fira Sans")
+  opts_int() %>% opts_theme()
 ```
@@
 
-```{r}
+```{r summary-num-hq-countries}
 #| code-fold: show
 df_hq_countries %>% 
-  summarize(total = sum(num_ngos >= 1))
+  summarize(total = sum(num_ngos >= 1, na.rm = TRUE))
 ```
@@
   cols_align(align = "left", columns = region) %>% 
-  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, 
-                  use_pagination = FALSE, use_pagination_info = FALSE) %>% 
-  opt_table_font(font = "Fira Sans")
+  opts_theme() %>% 
+  opts_int(use_pagination = FALSE, use_pagination_info = FALSE)
 ```
@@
 
+## How are these NGOs distributed by target country?
+
+```{r tab-target-countries}
+possible_countries <- tibble(ISO3 = unique(as.character(world_map$ISO_A3))) %>% 
+  filter(ISO3 != "-99")
+
+df_work_countries_all <- survey_orgs %>%
+  unnest(Q2.5_iso3) %>%
+  group_by(Q2.5_iso3) %>%
+  summarise(num_ngos = n()) %>%
+  right_join(possible_countries, by = join_by(Q2.5_iso3 == ISO3)) %>% 
+  mutate(prop = num_ngos / sum(num_ngos, na.rm = TRUE),
+         country_name = countrycode(Q2.5_iso3, "iso3c", "country.name",
+                                    custom_match = c("XKX" = "Kosovo")),
+         presence = num_ngos >= 1) %>%
+  arrange(desc(num_ngos))
+
+df_work_countries_answered <- survey_all %>%
+  group_by(Q4.1_iso3) %>%
+  summarise(num = n())
+
+df_work_countries_all %>% 
+  select(country_name, Q2.5_iso3, num_ngos, prop) %>%
+  gt() %>% 
+  cols_label(
+    country_name = "Country name",
+    Q2.5_iso3 = "ISO3",
+    num_ngos = "NGOs",
+    prop = "Proportion"
+  ) %>% 
+  fmt_percent(columns = prop, decimals = 1) %>% 
+  opts_int() %>% opts_theme()
+```
+
+## Number of unique target countries
+
+Respondents indicated working in this many unique countries:
+
+```{r summary-num-target-countries}
+#| code-fold: show
+df_work_countries_all %>% 
+  summarize(total = sum(num_ngos >= 1, na.rm = TRUE))
+```
+
+```{r summary-num-countries-answered}
+df_work_countries_answered %>% 
+  nrow()
+```
+
+## Countries per response
+
+```{r tab-countries-per-response}
+countries_per_response <- survey_orgs %>%
+  unnest(Q2.5_iso3) %>%
+  group_by(clean.id) %>%
+  summarise(num = n())
+
+skim_without_charts(countries_per_response$num) %>% 
+  select(-c(skim_type, skim_variable, complete_rate)) %>% 
+  rename_with(~str_remove(., "numeric\\.")) %>% 
+  gt() %>% 
+  opts_theme() %>% 
+  opt_horizontal_padding(scale = 2)
+```
+
+```{r plot-countries-per-response, fig.width=6, fig.height=3}
+ggplot(countries_per_response, aes(x = num)) +
+  geom_histogram(binwidth = 2, color = "white", linewidth = 0.1) + 
+  labs(x = "Number of countries selected", y = "Frequency") +
+  theme_ingo()
+```
+
+## Flows between countries selected
+
+```{r plot-continents-marked}
+continents_marked <- survey_orgs %>%
+  select(home = Q2.2_iso3, target = Q2.5_iso3) %>%
+  unnest(target) %>% 
+  mutate(across(c(home, target), 
+                list(continent = ~countrycode(., "iso3c", "continent",
+                                              custom_match = c("XKX" = "Europe"))))) %>% 
+  mutate(across(ends_with("_continent"),
+                ~recode(., Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania"))) %>% 
+  group_by(home_continent, target_continent) %>%
+  summarize(times_marked = n()) %>% 
+  ungroup() %>% 
+  mutate(id = 1:n()) %>% 
+  pivot_longer(ends_with("continent"), names_to = "x", values_to = "continent")
+
+ggplot(continents_marked,
+       aes(x = x, y = times_marked, stratum = continent, alluvium = id, fill = continent)) +
+  geom_flow() +
+  geom_stratum(color = "grey30", alpha = 0.5, linewidth = 0.2) +
+  geom_text(stat = "stratum", aes(label = continent, color = continent), lineheight = 0.9,
+            family = "Fira Sans Semibold") +
+  scale_x_discrete(labels = c("Home region", "Target region"),
+                   expand = c(0, 0)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_fill_manual(values = c(clrs$Prism[6], clrs$Prism[8], clrs$Prism[11], clrs$Prism[2]),
+                    guide = "none") +
+  scale_color_manual(values = colorspace::darken(c(clrs$Prism[6], clrs$Prism[8], 
+                                                   clrs$Prism[11], clrs$Prism[2]), 0.5),
+                    guide = "none") +
+  labs(x = NULL, y = NULL,
+       title = "Flows between INGO home and target regions",
+       subtitle = "European NGOs tend to work in Europe; American NGOs go all over the place") +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        axis.text.x = element_text(family = "Fira Sans Semibold", size = rel(1.3)),
+        axis.text.y = element_blank())
+```
+
+## Regions worked in
+
+```{r tab-work-regions}
+df_target_regions <- survey_orgs %>%
+  select(target = Q2.5_iso3) %>%
+  unnest(target) %>% 
+  mutate(target = countrycode(target, "iso3c", "continent",
+                              custom_match = c("XKX" = "Europe"))) %>% 
+  mutate(target = recode(target, Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania")) %>% 
+  group_by(target) %>% 
+  summarize(times_marked = n()) %>% 
+  mutate(prop = times_marked / sum(times_marked)) %>% 
+  arrange(times_marked) %>% 
+  mutate(target = fct_inorder(target))
+
+df_target_regions %>% 
+  gt() %>% 
+  cols_label(
+    target = "Region",
+    times_marked = "Times marked",
+    prop = "Proportion"
+  ) %>% 
+  fmt_percent(columns = prop, decimals = 1) %>% 
+  fmt_number(columns = times_marked, decimals = 0) %>% 
+  cols_align(align = "left", columns = target) %>% 
+  opts_theme() %>% 
+  opts_int(use_pagination = FALSE, use_pagination_info = FALSE)
+```
+
+```{r plot-work-regions, fig.width=6, fig.height=3}
+ggplot(df_target_regions, aes(x = times_marked, y = target)) +
+  geom_pointrange(aes(xmin = 0, xmax = times_marked)) +
+  scale_x_continuous(labels = label_comma(),
+                     sec.axis = sec_axis(~ . / sum(df_target_regions$times_marked),
+                                         labels = label_percent())) +
+  labs(x = "Times country in region selected", y = NULL,
+       title = "Region of target countries",
+       subtitle = "Q2.5: Where does your organization work? (summarized by region)") +
+  theme_ingo() + 
+  theme(panel.grid.major.y = element_blank())
+```
+
 # What do these NGOs do?

### 2023-05-10 notebook/descriptive.qmd
Add activities models + general framework for brms targets

@@
 tar_load(c(world_map))
+tar_load(c(summary_activities, models_activities))
 
@@
 # What do these NGOs do?
+
+## Which issues do these NGOs work on?
+
+```{r plot-issues-worked-on, fig.width=6, fig.height=4}
+df_issues_most <- survey_orgs %>%
+  group_by(Q3.2.clean, potential.contentiousness) %>%
+  summarise(num = n()) %>%
+  ungroup() %>%
+  arrange(desc(num)) %>%
+  mutate(issue = factor(Q3.2.clean, levels = rev(unique(Q3.2.clean)), ordered = TRUE)) %>%
+  mutate(prop = num / sum(num), cum.prop = cumsum(prop))
+
+ggplot(df_issues_most, aes(x = num, y = issue, color = potential.contentiousness)) +
+  geom_pointrange(aes(xmin = 0, xmax = num)) +
+  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_issues_most$num),
+                                         labels = label_percent())) +
+  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8]), name = NULL) +
+  labs(x = "Organizations", y = NULL) +
+  theme_ingo() + 
+  theme(legend.position = c(1, 0), legend.justification = c(1, 0),
+        legend.direction = "horizontal", panel.grid.major.y = element_blank())
+```
+
+### What kinds of activities do these NGOs engage in?
+
+```{r plot-activities, fig.width=7, fig.height=4.5}
+ggplot(summary_activities$df_activities_collapsed, 
+       aes(x = prop, y = fct_rev(response), color = potential.contentiousness)) +
+  geom_pointrange(aes(xmin = 0, xmax = prop), position = position_dodge(width = 0.75),
+                   size = 0.5) +
+  labs(x = "Proportion selected", y = "How often INGO does work") +
+  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8]), name = NULL,
+                     guide = guide_legend(reverse = TRUE)) +
+  scale_x_continuous(labels = label_percent()) +
+  facet_wrap(~ question, ncol = 2) +
+  theme_ingo() + 
+  theme(legend.position = c(1, 0), legend.justification = c(1, 0),
+        legend.direction = "vertical", strip.text = element_text(size = rel(0.75)),
+        panel.grid.major.y = element_blank())
+```
+
+```{r tab-activities-contentiousness-diffs}
+#| tbl-cap: Median differences in proportion of high and low contention INGOs selecting frequency of type of work. Probability that the proportion is greater than 0 given in parentheses.
+models_activities %>% 
+  unnest(diffs_summary) %>% 
+  mutate(nice_value = glue::glue(
+    "{diff}<br>({p})",
+    diff = label_number(style_negative = "minus", accuracy = 0.01)(y),
+    p = label_number(accuracy = 0.01)(p_greater_0))
+  ) %>% 
+  ungroup() %>% 
+  select(question, response, nice_value) %>% 
+  pivot_wider(names_from = "response", values_from = "nice_value") %>% 
+  gt() %>%
+  fmt_markdown(columns = 2:4) %>%
+  cols_align(align = "left", columns = question) %>%
+  cols_label(question = "") %>% 
+  opts_theme()
+```
+
+### Challenges and obstacles to mission
+
+```{r analyze-obstacles}
+# df.plot.obstacles.raw <- survey.orgs.clean %>%
+#   filter(!is.na(Q3.12_obstacle)) %>%
+#   mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
+#   unnest(obstacle) %>%
+#   mutate(obstacle = recode(obstacle,
+#     `access to country` = "bureaucratic, legal, and political",
+#     `political context` = "bureaucratic, legal, and political",
+#     `bureaucratic and legal` = "bureaucratic, legal, and political"
+#   )) %>%
+#   group_by(obstacle) %>%
+#   summarise(num = n()) %>%
+#   arrange(desc(num))
+# 
+# df.plot.obstacles.denom <- survey.orgs.clean %>%
+#   filter(!is.na(Q3.12_obstacle)) %>%
+#   nrow()
+# 
+# df.plot.obstacles <- df.plot.obstacles.raw %>%
+#   mutate(prop = num / df.plot.obstacles.denom) %>%
+#   mutate(obstacle = capitalize(obstacle)) %>%
+#   filter(num > 20, obstacle != "Other") %>%
+#   mutate(obstacle = fct_inorder(obstacle))
+# 
+# plot.obstacles <- ggplot(df.plot.obstacles, aes(x=prop, y=fct_rev(obstacle))) +
+#   geom_pointrangeh(aes(xmin=0, xmax=prop)) +
+#   scale_x_continuous(labels=scales::percent) +
+#   labs(x="Proportion of respondents", y=NULL) +
+#   theme_ath() + theme(panel.grid.major.y=element_blank())
+# 
+# plot.obstacles
+# 
+# fig.save.cairo(plot.obstacles,
+#                filename="3-obstacles",
+#                width=4.5, height=2)
+```

### 2023-05-10 R/funs_analysis.R

@@ -1,0 +1,106 @@
+library(marginaleffects)
+suppressPackageStartupMessages(library(tidybayes))
+
+# brms cleans up names for Stan with base::make.names() + removing .s and _s
+# https://github.com/paul-buerkner/brms/issues/442#issuecomment-392520245
+brms_names <- function(x) {
+  gsub("\\.|\\_", "", make.names(x))
+}
+
+extract_clean_draws <- function(model) {
+  var_name <- labels(terms(as.formula(model$formula)))
+  
+  group_names <- tibble(nice_name = levels(model$data[[var_name]])) %>% 
+    mutate(.variable = paste0("b_", var_name, brms_names(nice_name)))
+  
+  model %>% 
+    gather_draws(`^b_.*`, regex = TRUE) %>% 
+    ungroup() %>% 
+    left_join(group_names, by = join_by(.variable))
+}
+
+extract_diffs <- function(model) {
+  var_name <- labels(terms(as.formula(model$formula)))
+  var_list <- setNames(list("pairwise"), var_name)
+  
+  model %>% 
+    avg_comparisons(variables = var_list, type = "link") %>% 
+    posterior_draws()
+}
+
+extract_diffs_summary <- function(diffs) {
+  diffs %>% 
+    summarize(post_median = median_qi(draw, .width = 0.95),
+              p_greater_0 = sum(draw > 0) / n()) %>% 
+    unnest(post_median)
+}
+
+make_activities_summary <- function(x) {
+  labels_activities <- tribble(
+    ~levels, ~labels, 
+    "aid", "Providing direct aid and services",
+    "education", "Engaging in research and public education",
+    "mobilize", "Mobilizing people",
+    "advocacy", "Engaging in advocacy",
+    "monitor", "Monitoring and assessing the effects of policies"
+  )
+  
+  df_activities <- x %>%
+    select(potential.contentiousness, contains("Q3.3"), -contains("TEXT")) %>%
+    gather(question, response, -potential.contentiousness) %>%
+    mutate(question = str_replace(question, "Q3\\.3_", ""),
+           question = factor(question, levels = labels_activities$levels,
+                             labels = labels_activities$labels, ordered = TRUE)) %>%
+    filter(!(response %in% c("Don't know", "Not applicable"))) %>%
+    group_by(question, response, potential.contentiousness) %>%
+    summarise(num = n()) %>%
+    ungroup() %>%
+    mutate(response = factor(response, levels = levels(x$Q3.3_aid), ordered = TRUE))
+  
[…]

### 2023-05-10 _targets.R

@@ -16,6 +16,16 @@ options(tidyverse.quiet = TRUE,
 
 set.seed(71215)  # From random.org
 
+# Bayesian stuff
+suppressPackageStartupMessages(library(brms))
+options(mc.cores = 4,
+        brms.backend = "cmdstanr")
+
+BAYES_SEED <- 907680  # From random.org
+CHAINS <- 4
+ITER <- 2000
+WARMUP <- 1000
+
 tar_option_set(packages = c("tidyverse"),
                format = "qs")
 
@@ -54,6 +64,10 @@ list(
   
   ## Graphics ----
   tar_target(graphic_functions, lst(theme_ingo, theme_ingo_map, set_annotation_fonts, clrs)),
+  
+  ## Analysis ----
+  tar_target(summary_activities, make_activities_summary(survey_orgs)),
+  tar_target(models_activities, make_activities_models(summary_activities)),
   
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-05-10 R/funs_analysis.R
Get rid of useless grouping/mutating

@@ -83,14 +83,11 @@ make_activities_models <- function(x) {
     bf(num | trials(total) ~ 0 + Intercept), 
     data = list(num = 5, total = 5),
     family = binomial(link = "identity"),
-    prior = c(prior(beta(5, 5), class = b, ub = 1, lb = 0)),
+    prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
     chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED
   )
   
   df_with_models <- x$df_activities_collapsed %>%
-    select(-total, -prop) %>%
-    group_by(question, potential.contentiousness) %>%
-    mutate(total = sum(num)) %>%
     group_by(question, response) %>% 
     nest() %>% 
     mutate(model = map(data, ~{

### 2023-05-10 notebook/desc-work.qmd
Add obstacles + rename

--- 2023-05-10 notebook/descriptive.qmd
@@
 ---
-title: "Descriptive stuff"
+title: "INGOs and instrumental factors"
 format:
@@
   cols_label(question = "") %>% 
+  tab_footnote(footnote = "Values show the differences in proportion of high and low contention INGOs providing each response (high contention proportion − low contention proportion)") %>% 
   opts_theme()
@@
 
-```{r analyze-obstacles}
-# df.plot.obstacles.raw <- survey.orgs.clean %>%
-#   filter(!is.na(Q3.12_obstacle)) %>%
-#   mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
-#   unnest(obstacle) %>%
-#   mutate(obstacle = recode(obstacle,
-#     `access to country` = "bureaucratic, legal, and political",
-#     `political context` = "bureaucratic, legal, and political",
-#     `bureaucratic and legal` = "bureaucratic, legal, and political"
-#   )) %>%
-#   group_by(obstacle) %>%
-#   summarise(num = n()) %>%
-#   arrange(desc(num))
-# 
-# df.plot.obstacles.denom <- survey.orgs.clean %>%
-#   filter(!is.na(Q3.12_obstacle)) %>%
-#   nrow()
-# 
-# df.plot.obstacles <- df.plot.obstacles.raw %>%
-#   mutate(prop = num / df.plot.obstacles.denom) %>%
-#   mutate(obstacle = capitalize(obstacle)) %>%
-#   filter(num > 20, obstacle != "Other") %>%
-#   mutate(obstacle = fct_inorder(obstacle))
-# 
-# plot.obstacles <- ggplot(df.plot.obstacles, aes(x=prop, y=fct_rev(obstacle))) +
-#   geom_pointrangeh(aes(xmin=0, xmax=prop)) +
-#   scale_x_continuous(labels=scales::percent) +
-#   labs(x="Proportion of respondents", y=NULL) +
-#   theme_ath() + theme(panel.grid.major.y=element_blank())
-# 
-# plot.obstacles
-# 
-# fig.save.cairo(plot.obstacles,
-#                filename="3-obstacles",
-#                width=4.5, height=2)
+```{r plot-obstacles, fig.width=6, fig.height=2}
+df_obstacles_raw <- survey_orgs %>% 
+  filter(!is.na(Q3.12_obstacle)) %>%
+  mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
+  unnest(obstacle) %>%
+  mutate(obstacle = recode(obstacle,
+                           `access to country` = "bureaucratic, legal, and political",
+                           `political context` = "bureaucratic, legal, and political",
+                           `bureaucratic and legal` = "bureaucratic, legal, and political"
+  )) %>%
+  group_by(obstacle) %>%
+  summarise(num = n()) %>%
+  arrange(desc(num))
+
+df_obstacles_denom <- survey_orgs %>%
+  filter(!is.na(Q3.12_obstacle)) %>%
+  nrow()
+
+df_obstacles <- df_obstacles_raw %>% 
+  mutate(prop = num / df_obstacles_denom) %>% 
+  mutate(obstacle = str_to_sentence(obstacle)) %>% 
+  filter(num > 20, obstacle != "Other") %>%
+  mutate(obstacle = fct_inorder(obstacle))
+
+ggplot(df_obstacles, aes(x = prop, y = fct_rev(obstacle))) +
+  geom_pointrange(aes(xmin = 0, xmax = prop)) +
+  scale_x_continuous(labels = label_percent()) +
+  labs(x = "Proportion of respondents", y = NULL) +
+  theme_ingo() + 
+  theme(panel.grid.major.y = element_blank())
 ```

### 2023-05-10 R/funs_analysis.R
Turn off chain details

@@ -84,7 +84,7 @@ make_activities_models <- function(x) {
     data = list(num = 5, total = 5),
     family = binomial(link = "identity"),
     prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
-    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
   )
   
   df_with_models <- x$df_activities_collapsed %>%

### 2023-05-10 notebook/desc-details.qmd
Split descriptive stuff across multiple qmd files

--- 2023-05-09 notebook/descriptive.qmd
@@
 ---
-title: "Descriptive stuff"
+title: "General respondent details"
 format:
@@
 library(targets)
-library(sf)
-library(countrycode)
 library(scales)
 library(gt)
-library(skimr)
-library(ggalluvial)
 library(here)
@@
 
-tar_load(c(survey_orgs, survey_countries, survey_all))
-tar_load(c(world_map))
+tar_load(c(survey_orgs, survey_countries))
 
@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
-set_annotation_fonts()
-
-opts_int <- function(x, ...) {
-  x %>% 
-    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
-}
-
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Fira Sans")
-}
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 ```
 
-# General respondent details
-
-## How many NGOs responded?
+# How many NGOs responded?
 
@@
 
-## How many respondents answered questions for more than one country?
+# How many respondents answered questions for more than one country?
 
@@
 
-## Who in the organization responded to the survey?
+# Who in the organization responded to the survey?
 
@@
 ```
-
-# Where are NGOs based?
-
-## How are these NGOs distributed by HQ?
-
-```{r tab-hq-countries}
-df_hq_countries <- survey_orgs %>% 
-  group_by(Q2.2_iso3) %>% 
-  summarize(num_ngos = n()) %>% 
-  ungroup() %>% 
-  mutate(num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
-         ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA),
-         prop = num_ngos / sum(num_ngos, na.rm = TRUE)) %>% 
-  mutate(country_name = countrycode(Q2.2_iso3, "iso3c", "country.name")) %>%
-  arrange(desc(num_ngos))
-
-df_hq_countries %>% 
-  select(country_name, Q2.2_iso3, num_ngos, prop) %>%
-  gt() %>% 
-  cols_label(
-    country_name = "Country name",
-    Q2.2_iso3 = "ISO3",
-    num_ngos = "NGOs",
-    prop = "Proportion"
-  ) %>% 
-  fmt_percent(columns = prop, decimals = 1) %>% 
-  opts_int() %>% opts_theme()
-```
-
-## Number of unique HQ countries
-
-```{r summary-num-hq-countries}
-#| code-fold: show
-df_hq_countries %>% 
-  summarize(total = sum(num_ngos >= 1, na.rm = TRUE))
-```
-
-## Regional distribution of HQ countries
-
-```{r tab-hq-regions}
-df_hq_regions <- df_hq_countries %>%
-  mutate(region = countrycode(Q2.2_iso3, "iso3c", "continent"),
-         region = ifelse(Q2.2_iso3 == "TWN", "Asia", region)) %>%
-  mutate(region = recode(region, Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania")) %>%
-  group_by(region) %>%
-  summarise(num = sum(num_ngos)) %>% ungroup() %>%
-  mutate(prop = num / sum(num)) %>%
-  arrange(desc(num)) %>%
-  mutate(region = fct_rev(fct_inorder(region)))
-
-df_hq_regions %>% 
-  gt() %>% 
-  cols_label(
-    region = "Region",
-    num = "NGOs",
-    prop = "Proportion"
-  ) %>% 
-  fmt_percent(columns = prop, decimals = 1) %>% 
-  cols_align(align = "left", columns = region) %>% 
-  opts_theme() %>% 
-  opts_int(use_pagination = FALSE, use_pagination_info = FALSE)
-```
-
-```{r plot-hq-regions, fig.width=6, fig.height=3}
-ggplot(df_hq_regions, aes(x = num, y = region)) +
-  geom_pointrange(aes(xmin = 0, xmax = num)) +
-  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_hq_regions$num),
-                                         labels = label_percent())) +
-  labs(x = "Respondents based in region", y = NULL,
-       title = "Region of headquarters",
-       subtitle = "Q2.2: Where is your organization's headquarters? (summarized by region)") +
-  theme_ingo() + 
-  theme(panel.grid.major.y = element_blank())
-```
-
-## Responses per country (30 NGO ceiling)
-
-```{r plot-map-respondents-gradient}
-map_hq <- world_map %>% 
-  left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3))
-
-ggplot() +
-  geom_sf(data = map_hq, aes(fill = num_ngos_ceiling),
-          linewidth = 0.1, color = "grey30") +
-  scale_fill_binned(low = clrs$Peach[1], high = clrs$Peach[7], na.value = "grey95",
-                    labels = c(1, 10, 20, "30+"), breaks = c(1, 10, 20, 30),
-                    name = "Number of NGOs: ",
-                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
-                                             title.vjust = 1)) +
-  coord_sf(crs = "+proj=robin") +
-  theme_ingo_map()
-```
-
-## Countries with at least one response
-
-```{r plot-map-respondents-binary}
-ggplot() +
-  geom_sf(data = map_hq, aes(fill = ngo_presence),
-          linewidth = 0.1, color = "grey30") +
-  scale_fill_manual(values = c(clrs$Peach[7], "grey95"), 
-                    na.value = "grey95", na.translate = FALSE,
-                    name = NULL) +
-  coord_sf(crs = "+proj=robin") +
-  theme_ingo_map()
-```
-
-# Where do NGOs work?
-
-## How are these NGOs distributed by target country?
-
-```{r tab-target-countries}
-possible_countries <- tibble(ISO3 = unique(as.character(world_map$ISO_A3))) %>% 
-  filter(ISO3 != "-99")
-
-df_work_countries_all <- survey_orgs %>%
-  unnest(Q2.5_iso3) %>%
-  group_by(Q2.5_iso3) %>%
-  summarise(num_ngos = n()) %>%
-  right_join(possible_countries, by = join_by(Q2.5_iso3 == ISO3)) %>% 
-  mutate(prop = num_ngos / sum(num_ngos, na.rm = TRUE),
-         country_name = countrycode(Q2.5_iso3, "iso3c", "country.name",
-                                    custom_match = c("XKX" = "Kosovo")),
-         presence = num_ngos >= 1) %>%
-  arrange(desc(num_ngos))
-
-df_work_countries_answered <- survey_all %>%
-  group_by(Q4.1_iso3) %>%
-  summarise(num = n())
-
-df_work_countries_all %>% 
-  select(country_name, Q2.5_iso3, num_ngos, prop) %>%
-  gt() %>% 
-  cols_label(
-    country_name = "Country name",
-    Q2.5_iso3 = "ISO3",
-    num_ngos = "NGOs",
-    prop = "Proportion"
-  ) %>% 
-  fmt_percent(columns = prop, decimals = 1) %>% 
-  opts_int() %>% opts_theme()
-```
-
-## Number of unique target countries
-
-Respondents indicated working in this many unique countries:
-
-```{r summary-num-target-countries}
-#| code-fold: show
-df_work_countries_all %>% 
-  summarize(total = sum(num_ngos >= 1, na.rm = TRUE))
-```
-
-```{r summary-num-countries-answered}
-df_work_countries_answered %>% 
-  nrow()
-```
-
-## Countries per response
-
-```{r tab-countries-per-response}
-countries_per_response <- survey_orgs %>%
-  unnest(Q2.5_iso3) %>%
-  group_by(clean.id) %>%
-  summarise(num = n())
-
-skim_without_charts(countries_per_response$num) %>% 
-  select(-c(skim_type, skim_variable, complete_rate)) %>% 
-  rename_with(~str_remove(., "numeric\\.")) %>% 
-  gt() %>% 
-  opts_theme() %>% 
-  opt_horizontal_padding(scale = 2)
-```
-
-```{r plot-countries-per-response, fig.width=6, fig.height=3}
-ggplot(countries_per_response, aes(x = num)) +
-  geom_histogram(binwidth = 2, color = "white", linewidth = 0.1) + 
-  labs(x = "Number of countries selected", y = "Frequency") +
-  theme_ingo()
-```
-
-## Flows between countries selected
-
-```{r plot-continents-marked}
-continents_marked <- survey_orgs %>%
-  select(home = Q2.2_iso3, target = Q2.5_iso3) %>%
-  unnest(target) %>% 
-  mutate(across(c(home, target), 
-                list(continent = ~countrycode(., "iso3c", "continent",
-                                              custom_match = c("XKX" = "Europe"))))) %>% 
-  mutate(across(ends_with("_continent"),
-                ~recode(., Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania"))) %>% 
-  group_by(home_continent, target_continent) %>%
-  summarize(times_marked = n()) %>% 
-  ungroup() %>% 
-  mutate(id = 1:n()) %>% 
-  pivot_longer(ends_with("continent"), names_to = "x", values_to = "continent")
-
-ggplot(continents_marked,
-       aes(x = x, y = times_marked, stratum = continent, alluvium = id, fill = continent)) +
-  geom_flow() +
-  geom_stratum(color = "grey30", alpha = 0.5, linewidth = 0.2) +
-  geom_text(stat = "stratum", aes(label = continent, color = continent), lineheight = 0.9,
-            family = "Fira Sans Semibold") +
-  scale_x_discrete(labels = c("Home region", "Target region"),
-                   expand = c(0, 0)) +
-  scale_y_continuous(expand = c(0, 0)) +
-  scale_fill_manual(values = c(clrs$Prism[6], clrs$Prism[8], clrs$Prism[11], clrs$Prism[2]),
-                    guide = "none") +
-  scale_color_manual(values = colorspace::darken(c(clrs$Prism[6], clrs$Prism[8], 
-                                                   clrs$Prism[11], clrs$Prism[2]), 0.5),
-                    guide = "none") +
-  labs(x = NULL, y = NULL,
-       title = "Flows between INGO home and target regions",
-       subtitle = "European NGOs tend to work in Europe; American NGOs go all over the place") +
-  theme_ingo() +
-  theme(panel.grid.major.x = element_blank(),
-        panel.grid.major.y = element_blank(),
-        axis.text.x = element_text(family = "Fira Sans Semibold", size = rel(1.3)),
-        axis.text.y = element_blank())
-```
-
-## Regions worked in
-
-```{r tab-work-regions}
-df_target_regions <- survey_orgs %>%
-  select(target = Q2.5_iso3) %>%
-  unnest(target) %>% 
-  mutate(target = countrycode(target, "iso3c", "continent",
-                              custom_match = c("XKX" = "Europe"))) %>% 
-  mutate(target = recode(target, Oceania = "Asia &\nOceania", Asia = "Asia &\nOceania")) %>% 
-  group_by(target) %>% 
-  summarize(times_marked = n()) %>% 
-  mutate(prop = times_marked / sum(times_marked)) %>% 
-  arrange(times_marked) %>% 
-  mutate(target = fct_inorder(target))
-
-df_target_regions %>% 
-  gt() %>% 
-  cols_label(
-    target = "Region",
-    times_marked = "Times marked",
-    prop = "Proportion"
-  ) %>% 
-  fmt_percent(columns = prop, decimals = 1) %>% 
-  fmt_number(columns = times_marked, decimals = 0) %>% 
-  cols_align(align = "left", columns = target) %>% 
-  opts_theme() %>% 
-  opts_int(use_pagination = FALSE, use_pagination_info = FALSE)
-```
-
-```{r plot-work-regions, fig.width=6, fig.height=3}
-ggplot(df_target_regions, aes(x = times_marked, y = target)) +
-  geom_pointrange(aes(xmin = 0, xmax = times_marked)) +
-  scale_x_continuous(labels = label_comma(),
-                     sec.axis = sec_axis(~ . / sum(df_target_regions$times_marked),
-                                         labels = label_percent())) +
-  labs(x = "Times country in region selected", y = NULL,
-       title = "Region of target countries",
-       subtitle = "Q2.5: Where does your organization work? (summarized by region)") +
-  theme_ingo() + 
-  theme(panel.grid.major.y = element_blank())
-```
-
-# What do these NGOs do?

### 2023-05-10 notebook/desc-governments.qmd
Split descriptive stuff across multiple qmd files

--- 2023-05-10 notebook/desc-details.qmd
@@
 ---
-title: "General respondent details"
+title: "INGOs and governments"
 format:
@@
 ```
-
-```{r load-libraries-data, warning=FALSE, message=FALSE}
-library(tidyverse)
-library(targets)
-library(scales)
-library(gt)
-library(here)
-
-tar_config_set(store = here('_targets'),
-               script = here('_targets.R'))
-
-tar_load(c(survey_orgs, survey_countries))
-
-# Plotting functions
-invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
-invisible(list2env(tar_read(table_functions), .GlobalEnv))
-```
-
-# How many NGOs responded?
-
-```{r summary-n-respondents}
-#| code-fold: show
-nrow(survey_orgs)
-```
-
-# How many respondents answered questions for more than one country?
-
-```{r summary-n-multiple-countries}
-#| code-fold: show
-survey_countries %>% 
-  summarize(more_than_1 = sum(loop.number > 1),
-            prop = more_than_1 / nrow(survey_orgs))
-```
-
-# Who in the organization responded to the survey?
-
-```{r plot-respondents-who, fig.width=6, fig.height=3}
-df_plot_respondents <- survey_orgs %>%
-  group_by(Q2.3) %>%
-  summarise(num = n()) %>%
-  arrange(num) %>% 
-  mutate(question = fct_inorder(Q2.3))
-
-df_plot_respondents %>% 
-  ggplot(aes(x = num, y = question)) +
-  geom_col() +
-  scale_x_continuous(expand = c(0, 0),
-                     sec.axis = sec_axis(~ . / sum(df_plot_respondents$num),
-                                         labels = label_percent())) +
-  labs(x = "Respondents", y = NULL,
-       title = "Who filled out the survey?",
-       subtitle = "Q2.3: What is your position in your organization?") +
-  theme_ingo()
-```
-
-Lots of others. Who are the others?
-
-```{r tab-who-responded-others}
-survey_orgs %>%
-  filter(!is.na(Q2.3_TEXT)) %>%
-  mutate(`Position in organization` = str_to_title(Q2.3_TEXT)) %>%
-  group_by(`Position in organization`) %>%
-  summarise(Count = n()) %>%
-  mutate(Proportion = Count / sum(Count)) %>%
-  arrange(desc(Count)) %>% 
-  gt() %>% 
-  fmt_percent(columns = Proportion, decimals = 1) %>% 
-  opts_int() %>% opts_theme()
-```

### 2023-05-10 notebook/desc-work.qmd
Split descriptive stuff across multiple qmd files

@@
 invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
 set_annotation_fonts()
-
-opts_int <- function(x, ...) {
-  x %>% 
-    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
-}
-
-opts_theme <- function(x) {
-  x %>% 
-    opt_table_font(font = "Fira Sans")
-}
-```
-
-# General respondent details
-
-## How many NGOs responded?
-
-```{r summary-n-respondents}
-#| code-fold: show
-nrow(survey_orgs)
-```
-
-## How many respondents answered questions for more than one country?
-
-```{r summary-n-multiple-countries}
-#| code-fold: show
-survey_countries %>% 
-  summarize(more_than_1 = sum(loop.number > 1),
-            prop = more_than_1 / nrow(survey_orgs))
-```
-
-## Who in the organization responded to the survey?
-
-```{r plot-respondents-who, fig.width=6, fig.height=3}
-df_plot_respondents <- survey_orgs %>%
-  group_by(Q2.3) %>%
-  summarise(num = n()) %>%
-  arrange(num) %>% 
-  mutate(question = fct_inorder(Q2.3))
-
-df_plot_respondents %>% 
-  ggplot(aes(x = num, y = question)) +
-  geom_col() +
-  scale_x_continuous(expand = c(0, 0),
-                     sec.axis = sec_axis(~ . / sum(df_plot_respondents$num),
-                                         labels = label_percent())) +
-  labs(x = "Respondents", y = NULL,
-       title = "Who filled out the survey?",
-       subtitle = "Q2.3: What is your position in your organization?") +
-  theme_ingo()
-```
-
-Lots of others. Who are the others?
-
-```{r tab-who-responded-others}
-survey_orgs %>%
-  filter(!is.na(Q2.3_TEXT)) %>%
-  mutate(`Position in organization` = str_to_title(Q2.3_TEXT)) %>%
-  group_by(`Position in organization`) %>%
-  summarise(Count = n()) %>%
-  mutate(Proportion = Count / sum(Count)) %>%
-  arrange(desc(Count)) %>% 
-  gt() %>% 
-  fmt_percent(columns = Proportion, decimals = 1) %>% 
-  opts_int() %>% opts_theme()
 ```
@@
 
-### What kinds of activities do these NGOs engage in?
+## What kinds of activities do these NGOs engage in?
 
@@
 
-### Challenges and obstacles to mission
+## Challenges and obstacles to mission
 

### 2023-05-10 R/funs_tables.R

@@ -1,0 +1,9 @@
+opts_int <- function(x, ...) {
+  x %>% 
+    opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, ...)
+}
+
+opts_theme <- function(x) {
+  x %>% 
+    opt_table_font(font = "Fira Sans")
+}

### 2023-05-10 _targets.R

@@ -64,6 +64,7 @@ list(
   
   ## Graphics ----
   tar_target(graphic_functions, lst(theme_ingo, theme_ingo_map, set_annotation_fonts, clrs)),
+  tar_target(table_functions, lst(opts_int, opts_theme)),
   
   ## Analysis ----
   tar_target(summary_activities, make_activities_summary(survey_orgs)),

### 2023-05-11 R/funs_analysis.R
Simplify and generalize pairwise calculations
tidybayes only; no more marginaleffects::comparisons

@@ -1,40 +1,38 @@
-library(marginaleffects)
 suppressPackageStartupMessages(library(tidybayes))
 
-# brms cleans up names for Stan with base::make.names() + removing .s and _s
-# https://github.com/paul-buerkner/brms/issues/442#issuecomment-392520245
-brms_names <- function(x) {
-  gsub("\\.|\\_", "", make.names(x))
+# Functions for extracting draws and calculating pairwise differences ----
+extract_posterior_draws <- function(model, prop = FALSE) {
+  post <- model %>% 
+    epred_draws(newdata = model$data)
+  
+  if (prop) {
+    post <- post %>% 
+      mutate(.epred_count = .epred,
+             .epred = .epred_count / total)
+  }
+  
+  return(post)
 }
 
-extract_clean_draws <- function(model) {
+extract_diffs <- function(model, prop = FALSE) {
+  post <- extract_posterior_draws(model, prop = prop)
+  
   var_name <- labels(terms(as.formula(model$formula)))
-  
-  group_names <- tibble(nice_name = levels(model$data[[var_name]])) %>% 
-    mutate(.variable = paste0("b_", var_name, brms_names(nice_name)))
-  
-  model %>% 
-    gather_draws(`^b_.*`, regex = TRUE) %>% 
+
+  post %>% 
     ungroup() %>% 
-    left_join(group_names, by = join_by(.variable))
-}
-
-extract_diffs <- function(model) {
-  var_name <- labels(terms(as.formula(model$formula)))
-  var_list <- setNames(list("pairwise"), var_name)
-  
-  model %>% 
-    avg_comparisons(variables = var_list, type = "link") %>% 
-    posterior_draws()
+    compare_levels(.epred, by = var_name)
 }
 
 extract_diffs_summary <- function(diffs) {
   diffs %>% 
-    summarize(post_median = median_qi(draw, .width = 0.95),
-              p_greater_0 = sum(draw > 0) / n()) %>% 
+    summarize(post_median = median_qi(.epred, .width = 0.95),
+              p_greater_0 = sum(.epred > 0) / n()) %>% 
     unnest(post_median)
 }
 
+
+# Functions for specific questions ----
 make_activities_summary <- function(x) {
   labels_activities <- tribble(
     ~levels, ~labels, 
@@ -95,8 +93,8 @@ make_activities_models <- function(x) {
              formula = bf(num | trials(total) ~ 0 + potential.contentiousness),
[…]

### 2023-05-11 _targets.R
Treat ordered factors as treatments in models

@@ -12,7 +12,9 @@ tar_config_set(store = here::here('_targets'),
                script = here::here('_targets.R'))
 
 options(tidyverse.quiet = TRUE,
-        dplyr.summarise.inform = FALSE)
+        dplyr.summarise.inform = FALSE,
+        # Treat ordered factors as treatments in models
+        contrasts = rep("contr.treatment", 2))
 
 set.seed(71215)  # From random.org
 

### 2023-05-11 R/funs_tables.R
Bold column headings

@@ -5,5 +5,6 @@ opts_int <- function(x, ...) {
 
 opts_theme <- function(x) {
   x %>% 
-    opt_table_font(font = "Fira Sans")
+    opt_table_font(font = "Fira Sans") %>% 
+    tab_options(column_labels.font.weight = "bold")
 }

### 2023-05-11 R/funs_tables.R
Also make row groups bold

@@ -6,5 +6,6 @@ opts_int <- function(x, ...) {
 opts_theme <- function(x) {
   x %>% 
     opt_table_font(font = "Fira Sans") %>% 
-    tab_options(column_labels.font.weight = "bold")
+    tab_options(column_labels.font.weight = "bold",
+                row_group.font.weight = "bold")
 }

### 2023-05-11 R/funs_analysis.R
Support general non-proportional models too

@@ -2,13 +2,18 @@ suppressPackageStartupMessages(library(tidybayes))
 
 # Functions for extracting draws and calculating pairwise differences ----
 extract_posterior_draws <- function(model, prop = FALSE) {
-  post <- model %>% 
-    epred_draws(newdata = model$data)
-  
   if (prop) {
-    post <- post %>% 
+    post <- model %>% 
+      epred_draws(newdata = model$data) %>% 
       mutate(.epred_count = .epred,
              .epred = .epred_count / total)
+  } else {
+    var_name <- labels(terms(as.formula(model$formula)))
+    
+    # Create a tibble with a column that has the value of a variable with
+    # `"{blah}" := x`, or walrus operator + glue syntax
+    post <- model %>% 
+      epred_draws(newdata = tibble("{var_name}" := unique(model$data[[var_name]])))
   }
   
   return(post)
@@ -28,7 +33,8 @@ extract_diffs_summary <- function(diffs) {
   diffs %>% 
     summarize(post_median = median_qi(.epred, .width = 0.95),
               p_greater_0 = sum(.epred > 0) / n()) %>% 
-    unnest(post_median)
+    unnest(post_median) %>% 
+    mutate(type = "Differences")
 }
 
 

### 2023-05-11 notebook/desc-instrumental.qmd
Add instrumental concerns section

---
title: "INGOs and instrumental factors"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", fig.retina = 3,
                      fig.width = 6, fig.height = (6 * 0.618),
                      out.width = "80%", collapse = TRUE,
                      dev = "ragg_png")

options(digits = 3, width = 120,
        dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(scales)
library(glue)
library(gt)
library(patchwork)
library(tidybayes)
library(here)

tar_config_set(store = here('_targets'),
               script = here('_targets.R'))

tar_load(c(survey_orgs, survey_countries, survey_all))
tar_load(c(strategies_size_models))

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(table_functions), .GlobalEnv))
set_annotation_fonts()
```

# Staffing

```{r tab-volunteers}
df_staff <- survey_orgs %>%
  select(employees = Q3.4.num, volunteers = Q3.5.num) %>%
  filter(employees < 10000, volunteers < 10000) %>%
  mutate(no_emps = employees == 0,
         no_vols = volunteers == 0)

df_staff %>% 
  count(no_vols) %>% 
  mutate(prop = n / sum(n)) %>% 
  gt() %>% 
  cols_label(
    no_vols = "No volunteers",
    n = "N",
    prop = "Proportion"
  ) %>% 
  cols_align(align = "left", columns = no_vols) %>% 
  fmt_percent(columns = prop, decimals = 1) %>% 
  opts_theme()
```

```{r tab-staff-volunteers}
df_staff %>% 
  group_by(no_emps, no_vols) %>% 
  summarize(across(c(employees, volunteers), 
                   list(n = ~n(), median = median, mean = mean))) %>% 
  ungroup() %>%
  mutate(prop = employees_n / sum(employees_n))

df_staff %>% 
  pivot_longer(c(employees, volunteers)) %>% 
  mutate(name = str_to_title(name)) %>% 
  ggplot(aes(x = value, fill = name)) +
  geom_histogram(binwidth = 0.5, color = "white", linewidth = 0.25) +
  scale_x_continuous(trans = "log1p", breaks = c(0, 10^(0:5)), labels = label_comma()) +
  scale_fill_manual(values = c(clrs$Prism[3], clrs$Prism[6]), name = NULL) +
  labs(x = NULL, y = "Number of staff") +
  facet_wrap(vars(name), nrow = 2) +
  theme_ingo()
```

# Funding

```{r tab-funding}
df_funding <- survey_orgs %>%
  filter(!is.na(small_org)) %>%
  select(clean.id, small_org, Q3.8.num, Q3.8) %>%
  filter(!is.na(Q3.8.num))

df_funding %>%
  group_by(small_org) %>%
  summarize(across(Q3.8.num, list(mean = mean, median = median))) %>% 
  gt() %>% 
  cols_label(
    small_org = "Organization size",
    Q3.8.num_mean = "Sources (mean)",
    Q3.8.num_median = "Sources (median)"
  ) %>% 
  cols_align(align = "left", columns = small_org) %>% 
  opts_theme()
```

```{r calc-funding-org-size}
df_funding_unnested_org_size <- df_funding %>% 
  unnest(Q3.8) %>% 
  filter(key != "None") %>%
  group_by(key, value, small_org) %>%
  summarise(num = n()) %>%
  ungroup() %>%
  mutate(value = factor(value,
                        levels = levels(survey_orgs$Q3.8_individual),
                        ordered = TRUE)) %>% 
  mutate(answer = fct_collapse(value,
    "A lot" = c("A great deal", "A lot"),
    "Some" = c("A moderate amount", "A little"),
    "None" = "None at all"
  )) %>%
  filter(key != "Other") %>%
  mutate(source = fct_collapse(key,
    "NGOs and foundations" = c("Donations from other NGOs", "Foundation donations"),
    "Governments and IGOs" = c("Grants from home country", "Grants from host country", "Grants from other governments", "Grants from IGOs")
  ))
```

```{r plot-funding-org-size, fig.width=7, fig.height=5}
df_funding_plot <- df_funding_unnested_org_size %>%
  group_by(answer, source, small_org) %>% 
  summarise(num = sum(num)) %>%
  group_by(small_org, source) %>% 
  mutate(total = sum(num)) %>% 
  ungroup() %>%
  mutate(prop = num / total) %>%
  arrange(answer, desc(small_org), desc(prop)) %>%
  mutate(source = fct_inorder(source))

df_funding_totals <- df_funding_plot %>%
  group_by(source) %>%
  summarise(total = sum(num)) %>%
  ungroup() %>%
  arrange(total) %>%
  mutate(source = fct_inorder(source))

p1 <- ggplot(df_funding_totals, aes(x = total, y = source)) +
  geom_pointrange(aes(xmin = 0, xmax = after_stat(x))) +
  scale_x_continuous(breaks = c(0, 500, 1000),
                     labels = label_comma()) +
  labs(x = "Times answer selected", y = NULL,
       title = "INGO funding sources") +
  theme_ingo() +
  theme(panel.grid.major.y = element_blank())

p2 <- ggplot(df_funding_plot, aes(x = prop, y = fct_rev(answer),
                            color = fct_rev(small_org))) +
  geom_pointrange(aes(xmin = 0, xmax = after_stat(x)),
                  position = position_dodge(width = 0.75), size = 0.5) + 
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[5]), name = NULL,
                     guide = guide_legend(reverse = TRUE)) +
  scale_x_continuous(labels = label_percent()) +
  labs(x = "Proportion selected", y = NULL, 
       title = "How much funding INGO relies on") +
  facet_wrap(vars(source)) +
  theme_ingo() +
  theme(strip.text = element_text(size = rel(0.75)),
        panel.grid.major.y = element_blank(),
        legend.position = c(1, 0), legend.justification = c(1, 0),
        legend.direction = "vertical")

(p1 / plot_spacer() / p2) +
  plot_layout(heights = c(0.325, 0.025, 0.65))
```

# Time in country

```{r plot-time-in-country, fig.width=6, fig.height=3}
df_time_country <- survey_all %>%
  filter(!is.na(Q4.2), Q4.2 != "Don't know") %>%
  group_by(Q4.2, target.regime.type) %>%
  summarise(num = n()) %>%
  ungroup() %>%
  mutate(Q4.2 = factor(Q4.2, levels = rev(levels(Q4.2)), ordered = TRUE))

ggplot(df_time_country, aes(x = num, y = Q4.2, color = target.regime.type)) +
  geom_pointrange(aes(xmin = 0, xmax = after_stat(x)), 
                  position = position_dodge(width = 0.5), size = 0.5) + 
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_time_country$num),
                                         labels = label_percent())) +
  scale_color_manual(values = c(clrs$Prism[4], clrs$Prism[6]), name = NULL,
                     guide = guide_legend(reverse = TRUE)) +
  labs(x = "Number of responses", y = NULL) +
  theme_ingo() + 
  theme(panel.grid.major.y = element_blank())
```

# Collaboration

```{r tab-collaboration}
df_collaboration_raw <- survey_orgs %>%
  filter(!is.na(small_org)) %>%
  select(clean.id, small_org, Q3.6_clean) %>%
  unnest(Q3.6_clean)

df_collaboration_raw %>%
  group_by(Q3.6_clean) %>%
  summarise(num = n()) %>%
  arrange(desc(num)) %>% 
  gt() %>% 
  cols_label(
    Q3.6_clean = "Partner",
    num = "N"
  ) %>% 
  opts_theme()
```

```{r plot-collaboration-size, fig.width=6, fig.height=3.5}
df_collaboration_plot <- df_collaboration_raw %>%
  filter(!(Q3.6_clean %in% c("Other", "Individuals", "Don't know", 
                             "We do not collaborate with other organizations or institutions"))) %>%
  mutate(Q3.6_clean = fct_collapse(Q3.6_clean,
    "NGOs" = 
      c("Other nongovernmental organizations (NGOs)",
        "Academic organizations",
        "Faith-based organizations"),
    "Corporations" = 
      c("Corporations or businesses", "Media"),
    "IGOs" = "International organizations (IGOs)"
  )) %>%
  group_by(small_org, Q3.6_clean) %>%
  summarise(num = n()) %>%
  group_by(small_org) %>%
  mutate(total = sum(num)) %>%
  ungroup() %>%
  mutate(prop = num / total) %>%
  arrange(small_org, prop) %>%
  mutate(Q3.6_clean = fct_inorder(Q3.6_clean))

ggplot(df_collaboration_plot, aes(x = prop, y = Q3.6_clean, 
                                  color = fct_rev(small_org))) + 
  geom_pointrange(aes(xmin = 0, xmax = after_stat(x)), 
                  position = position_dodge(width = 0.5), size = 0.5) + 
  labs(x = "Proportion selected", y = NULL) +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[5]), name = NULL,
                     guide = guide_legend(reverse = TRUE)) +
  scale_x_continuous(labels = label_percent()) +
  theme_ingo() + 
  theme(panel.grid.major.y = element_blank())
```

# Flexibility and practical strategies

## Size and number of changes

```{r plot-strategies-size}
p1 <- strategies_size_models$draws %>% 
  ggplot(aes(x = .epred, y = fct_rev(small_org), fill = small_org)) +
  stat_halfeye() +
  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[5]),
                    guide = "none") +
  labs(x = "Average number of strategies", y = NULL) +
  theme_ingo()

p2 <- strategies_size_models$diffs %>% 
  ggplot(aes(x = .epred)) +
  stat_halfeye(fill = clrs$Prism[11]) +
  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
  scale_x_continuous(labels = label_number(style_negative = "minus")) +
  labs(x = "Average # of strategies for 51+ employees − average for 0–50 employees",
       y = NULL) +
  theme_ingo() +
  theme(axis.text.y = element_blank(),
        panel.grid.major.y = element_blank())

(p1 / p2) +
  plot_layout(heights = c(0.75, 0.25))

df_strategies_size <- survey_all %>%
  mutate(num_strategies = Q4.3_value %>% map_int(length)) %>%
  filter(!is.na(Q4.3_value), !is.na(small_org))
```

```{r tab-strategies-size}
strategies_size_models$draws %>% 
  median_qi(.epred) %>% 
  mutate(small_org = as.character(small_org),
         type = "Group medians") %>%
  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
  bind_rows(strategies_size_models$diffs_summary) %>% 
  mutate(across(c(y, ymin, ymax, p_greater_0), 
                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
  mutate(nice_value = glue("{y_nice}<br>({ymin_nice}–{ymax_nice})")) %>% 
  mutate(small_org = str_replace(small_org, " - ", " − ")) %>% 
  select(type, small_org, nice_value, p_greater_0_nice) %>% 
  group_by(type) %>% 
  gt() %>% 
  cols_label(
    small_org = "",
    nice_value = "Posterior median",
    p_greater_0_nice = "p > 0"
  ) %>% 
  fmt_markdown(nice_value) %>% 
  sub_missing(p_greater_0_nice) %>% 
  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
  opts_theme()
```

## Collaborations, funding sources, and number of strategies

```{r plot-strategies-funding-collaboration, fig.width=6, fig.height=4}
df_strategies_funding <- survey_all %>%
  mutate(num_strategies = Q4.3_value %>% map_int(length)) %>%
  filter(!is.na(Q4.3_value), Q3.8.num < 7) %>%
  select(num_strategies, Q3.8.num)

p1 <- ggplot(df_strategies_funding, 
             aes(x = Q3.8.num, y = num_strategies, group = Q3.8.num)) +
  geom_point(position = position_jitter(seed = 1234), size = 0.5) + 
  geom_violin() +
  labs(x = "Number of funding sources", y = "Number of\noperational strategies") +
  theme_ingo()

df_strategies_collaboration <- survey_all %>%
  mutate(num_strategies = Q4.3_value %>% map_int(length),
         num_collaborations = Q3.6_num) %>%
  filter(!is.na(Q4.3_value), !is.na(Q3.6_num)) %>%
  select(num_strategies, num_collaborations)

p2 <- ggplot(df_strategies_collaboration, 
             aes(x = num_collaborations, y = num_strategies, group = num_collaborations)) +
  geom_point(position = position_jitter(seed = 1234), size = 0.5) + 
  geom_violin() +
  labs(x = "Number of collaborative partners", y = "Number of\noperational strategies") +
  theme_ingo()

p1 / p2
```

### 2023-05-11 R/funs_analysis.R

@@ -105,3 +105,23 @@ make_activities_models <- function(x) {
   
   return(df_with_models)
 }
+
+make_strategies_size_models <- function(survey_all) {
+  df_strategies_size <- survey_all %>%
+    mutate(num_strategies = Q4.3_value %>% map_int(length)) %>%
+    filter(!is.na(Q4.3_value), !is.na(small_org))
+  
+  model <- brm(
+    bf(num_strategies ~ 0 + small_org),
+    data = df_strategies_size,
+    family = gaussian(),
+    prior = c(prior(normal(1, 3), class = b, lb = 0)),
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
+  )
+  
+  draws <- extract_posterior_draws(model)
+  diffs <- extract_diffs(model)
+  diffs_summary <- extract_diffs_summary(diffs)
+  
+  return(lst(data = df_strategies_size, model, draws, diffs, diffs_summary))
+}

### 2023-05-11 _targets.R

@@ -71,7 +71,8 @@ list(
   ## Analysis ----
   tar_target(summary_activities, make_activities_summary(survey_orgs)),
   tar_target(models_activities, make_activities_models(summary_activities)),
-  
+  tar_target(strategies_size_models, make_strategies_size_models(survey_all)),
+    
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),
   tar_quarto(output_ms, path = "manuscript", quiet = FALSE, profile = "ms"),

### 2023-05-12 notebook/desc-instrumental.qmd
Rename target for consistency

@@
 tar_load(c(survey_orgs, survey_countries, survey_all))
-tar_load(c(strategies_size_models))
+tar_load(c(models_strategies_size))
 
@@
 ```{r plot-strategies-size}
-p1 <- strategies_size_models$draws %>% 
+p1 <- models_strategies_size$draws %>% 
   ggplot(aes(x = .epred, y = fct_rev(small_org), fill = small_org)) +
@@
 
-p2 <- strategies_size_models$diffs %>% 
+p2 <- models_strategies_size$diffs %>% 
   ggplot(aes(x = .epred)) +
@@
 ```{r tab-strategies-size}
-strategies_size_models$draws %>% 
+models_strategies_size$draws %>% 
   median_qi(.epred) %>% 
@@
   rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
-  bind_rows(strategies_size_models$diffs_summary) %>% 
+  bind_rows(models_strategies_size$diffs_summary) %>% 
   mutate(across(c(y, ymin, ymax, p_greater_0), 

### 2023-05-12 _targets.R

@@ -71,7 +71,7 @@ list(
   ## Analysis ----
   tar_target(summary_activities, make_activities_summary(survey_orgs)),
   tar_target(models_activities, make_activities_models(summary_activities)),
-  tar_target(strategies_size_models, make_strategies_size_models(survey_all)),
+  tar_target(models_strategies_size, make_strategies_size_models(survey_all)),
     
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-05-12 R/funs_graphics.R
Helper function for ggtext spans

@@ -50,3 +50,9 @@ theme_ingo_map <- function(base_size = 11, base_family = "Fira Sans") {
           panel.border = element_blank(),
           axis.text = element_blank())
 }
+
+build_span <- function(text, style_params) {
+  params <- paste0(names(style_params), ": ", style_params, collapse = "; ")
+  
+  glue::glue('<span style="{params}">{text}</span>')
+}

### 2023-05-12 _targets.R

@@ -65,7 +65,8 @@ list(
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
   
   ## Graphics ----
-  tar_target(graphic_functions, lst(theme_ingo, theme_ingo_map, set_annotation_fonts, clrs)),
+  tar_target(graphic_functions, lst(theme_ingo, theme_ingo_map, 
+                                    set_annotation_fonts, clrs, build_span)),
   tar_target(table_functions, lst(opts_int, opts_theme)),
   
   ## Analysis ----

### 2023-05-12 R/funs_analysis.R
Specify pairwise comparisons so that ordered factors loop back

@@ -26,7 +26,8 @@ extract_diffs <- function(model, prop = FALSE) {
 
   post %>% 
     ungroup() %>% 
-    compare_levels(.epred, by = var_name)
+    compare_levels(.epred, by = var_name,
+                   comparison = "pairwise")
 }
 
 extract_diffs_summary <- function(diffs) {

### 2023-05-12 notebook/desc-governments.qmd
Pattern-filled distributions

@@
 ```
+
+```{r load-libraries-data, warning=FALSE, message=FALSE}
+library(tidyverse)
+library(targets)
+library(scales)
+library(glue)
+library(gt)
+library(ggmosaic)
+library(ggtext)
+library(patchwork)
+library(tidybayes)
+library(here)
+library(ggpattern)
+
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
+
+tar_load(c(survey_orgs, survey_countries, survey_all))
+tar_load(c(df_govt_positivity_regime, models_govt_positivity_regime))
+
+# Plotting functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+```
+
+# Relationship with host governments
+
+```{r plot-govt-positivity-regime}
+ggplot(data = df_govt_positivity_regime) +
+  geom_mosaic(aes(x = product(target.regime.type, Q4.11_collapsed), 
+                  fill = target.regime.type),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[4], clrs$Prism[6]),
+                    guide = "none") +
+  labs(x = "Target country regime type",
+       y = "Relationship with target country",
+       title = glue("How would you characterize your organization’s<br>",
+                    "relationship with the government of {country}?",
+                    country = build_span("target_country",
+                                         c("font-family" = "Consolas", 
+                                           "color" = clrs$Prism[1])))) +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-govt-positivity-regime-bayes, fig.height=4}
+p1 <- models_govt_positivity_regime$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.11_collapsed, fill = Q4.11_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Relationship with target country") +
+  theme_ingo()
+
+p2 <- models_govt_positivity_regime$diffs %>% 
+  mutate(diffs = factor(Q4.11_collapsed, 
+                        levels = c("Positive - Neither", "Neither - Negative", "Positive - Negative"))) %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0.25
+  ) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp.")) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+## Regime type
+
+## Issue contentiousness
+
+# Experiences with regulations
+
+## Familiarity with regulations
+
+## Frequency of changes
+
+## How NGOs find out about changes
+
+## Are NGOs registered?
+
+# Government involvement in INGO activity
+
+## Contact and reporting frequency

### 2023-05-12 R/funs_analysis.R

@@ -126,3 +126,36 @@ make_strategies_size_models <- function(survey_all) {
   
   return(lst(data = df_strategies_size, model, draws, diffs, diffs_summary))
 }
+
+make_govt_positivity_regime <- function(x) {
+  df_govt_positivity_regime <- x %>%
+    select(Q4.11_collapsed, target.regime.type) %>%
+    filter(!is.na(Q4.11_collapsed), Q4.11_collapsed != "NULL") %>% 
+    mutate(Q4.11_collapsed = fct_drop(Q4.11_collapsed))
+
+  return(df_govt_positivity_regime)
+}
+
+make_govt_positivity_regime_models <- function(x) {
+  df_govt_positivity_regime_collapsed <- x %>% 
+    group_by(Q4.11_collapsed, target.regime.type) %>%
+    summarize(num = n()) %>% 
+    group_by(Q4.11_collapsed) %>%
+    mutate(total = sum(num)) %>% 
+    filter(target.regime.type == "Autocracy")
+  
+  model <- brm(
+    bf(num | trials(total) ~ 0 + Q4.11_collapsed),
+    data = df_govt_positivity_regime_collapsed,
+    family = binomial(link = "identity"),
+    prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
+  )
+  
+  draws <- extract_posterior_draws(model, prop = TRUE)
+  diffs <- extract_diffs(model, prop = TRUE)
+  diffs_summary <- extract_diffs_summary(diffs)
+  
+  return(lst(data = df_govt_positivity_regime_collapsed, 
+             model, draws, diffs, diffs_summary))
+}

### 2023-05-12 _targets.R

@@ -73,6 +73,9 @@ list(
   tar_target(summary_activities, make_activities_summary(survey_orgs)),
   tar_target(models_activities, make_activities_models(summary_activities)),
   tar_target(models_strategies_size, make_strategies_size_models(survey_all)),
+  tar_target(df_govt_positivity_regime, make_govt_positivity_regime(survey_countries)),
+  tar_target(models_govt_positivity_regime, 
+             make_govt_positivity_regime_models(df_govt_positivity_regime)),
     
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-05-12 notebook/desc-governments.qmd
Add relationship with government + issue area

--- 2023-05-10 notebook/desc-governments.qmd
@@
 ```
+
+```{r load-libraries-data, warning=FALSE, message=FALSE}
+library(tidyverse)
+library(targets)
+library(scales)
+library(glue)
+library(gt)
+library(ggmosaic)
+library(ggtext)
+library(patchwork)
+library(tidybayes)
+library(here)
+library(ggpattern)
+
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
+
+tar_load(c(survey_orgs, survey_countries, survey_all))
+tar_load(c(df_govt_positivity_regime, models_govt_positivity_regime,
+           df_govt_positivity_issue, models_govt_positivity_issue))
+
+# Plotting functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+```
+
+# Relationship with host governments
+
+## Regime type
+
+```{r plot-govt-positivity-regime, warning=FALSE}
+ggplot(data = df_govt_positivity_regime) +
+  geom_mosaic(aes(x = product(target.regime.type, Q4.11_collapsed), 
+                  fill = target.regime.type),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[4], clrs$Prism[6]),
+                    guide = "none") +
+  labs(x = "Target country regime type",
+       y = "Relationship with target country",
+       title = glue("How would you characterize your organization’s<br>",
+                    "relationship with the government of {country}?",
+                    country = build_span("target_country",
+                                         c("font-family" = "Consolas", 
+                                           "color" = clrs$Prism[1])))) +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-govt-positivity-regime-bayes, fig.height=4}
+p1 <- models_govt_positivity_regime$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.11_collapsed, fill = Q4.11_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Relationship with target country") +
+  theme_ingo()
+
+plot_data <- models_govt_positivity_regime$diffs %>% 
+  mutate(diffs = factor(Q4.11_collapsed, 
+                        levels = c("Positive - Neither", "Neither - Negative", "Positive - Negative")))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- models_govt_positivity_regime$diffs %>% 
+  mutate(diffs = factor(Q4.11_collapsed, 
+                        levels = c("Positive - Neither", "Neither - Negative", "Positive - Negative"))) %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp."),
+                     breaks = seq(-0.6, 0.2, by = 0.2)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-govt-positivity-regime-bayes}
+models_govt_positivity_regime$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.11_collapsed = as.character(Q4.11_collapsed),
+         type = "Median proportions for NGOs working in autocracies") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_govt_positivity_regime$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.11_collapsed = str_replace(Q4.11_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.11_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.11_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+## Issue contentiousness
+
+```{r plot-govt-positivity-issue, warning=FALSE}
+ggplot(data = df_govt_positivity_issue) +
+  geom_mosaic(aes(x = product(potential.contentiousness, Q4.11_collapsed), 
+                  fill = potential.contentiousness),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]),
+                    guide = "none") +
+  labs(x = "Contentiousness of INGO work",
+       y = "Relationship with target country",
+       title = glue("How would you characterize your organization’s<br>",
+                    "relationship with the government of {country}?",
+                    country = build_span("target_country",
+                                         c("font-family" = "Consolas", 
+                                           "color" = clrs$Prism[1])))) +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-govt-positivity-issue-bayes, fig.height=4}
+p1 <- models_govt_positivity_issue$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.11_collapsed, fill = Q4.11_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Relationship with target country") +
+  theme_ingo()
+
+plot_data <- models_govt_positivity_issue$diffs %>% 
+  mutate(diffs = factor(Q4.11_collapsed, 
+                        levels = c("Positive - Neither", "Neither - Negative", "Positive - Negative")))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- plot_data %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    # aes(y = after_stat(density * 1e5)),
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = "\n pp."),
+                     breaks = seq(-0.4, 0.1, by = 0.1)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-govt-positivity-issue-bayes}
+models_govt_positivity_issue$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.11_collapsed = as.character(Q4.11_collapsed),
+         type = "Median proportions for NGOs working on contentious issues") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_govt_positivity_issue$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.11_collapsed = str_replace(Q4.11_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.11_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.11_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+# Experiences with regulations
+
+## Familiarity with regulations
+
+## Frequency of changes
+
+## How NGOs find out about changes
+
+## Are NGOs registered?
+
+# Government involvement in INGO activity
+
+## Contact and reporting frequency

### 2023-05-12 R/funs_analysis.R

@@ -159,3 +159,36 @@ make_govt_positivity_regime_models <- function(x) {
   return(lst(data = df_govt_positivity_regime_collapsed, 
              model, draws, diffs, diffs_summary))
 }
+
+make_govt_positivity_issue <- function(x) {
+  df_govt_positivity_issue <- x %>%
+    select(Q4.11_collapsed, potential.contentiousness) %>%
+    filter(!is.na(Q4.11_collapsed), Q4.11_collapsed != "NULL") %>% 
+    mutate(Q4.11_collapsed = fct_drop(Q4.11_collapsed))
+  
+  return(df_govt_positivity_issue)
+}
+
+make_govt_positivity_issue_models <- function(x) {
+  df_govt_positivity_issue_collapsed <- x %>% 
+    group_by(Q4.11_collapsed, potential.contentiousness) %>%
+    summarize(num = n()) %>% 
+    group_by(Q4.11_collapsed) %>%
+    mutate(total = sum(num)) %>% 
+    filter(potential.contentiousness == "High contention")
+  
+  model <- brm(
+    bf(num | trials(total) ~ 0 + Q4.11_collapsed),
+    data = df_govt_positivity_issue_collapsed,
+    family = binomial(link = "identity"),
+    prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
+  )
+  
+  draws <- extract_posterior_draws(model, prop = TRUE)
+  diffs <- extract_diffs(model, prop = TRUE)
+  diffs_summary <- extract_diffs_summary(diffs)
+  
+  return(lst(data = df_govt_positivity_issue_collapsed, 
+             model, draws, diffs, diffs_summary))
+}

### 2023-05-12 _targets.R

@@ -76,6 +76,9 @@ list(
   tar_target(df_govt_positivity_regime, make_govt_positivity_regime(survey_countries)),
   tar_target(models_govt_positivity_regime, 
              make_govt_positivity_regime_models(df_govt_positivity_regime)),
+  tar_target(df_govt_positivity_issue, make_govt_positivity_issue(survey_countries)),
+  tar_target(models_govt_positivity_issue, 
+             make_govt_positivity_issue_models(df_govt_positivity_issue)),
     
   ## Manuscript and analysis notebook ----
   tar_quarto(output_nice, path = "manuscript", quiet = FALSE, profile = "nice"),

### 2023-05-16 notebook/survey-questions.qmd
Add original survey (and rename)

---
title: "Survey questions"
---

# Consent

*Q1.1*: You have been invited to participate in a research survey about the relationship between international nongovernmental organizations (INGOs) and the governments of their host countries. This survey is part of a study by Andrew Heiss from Duke University in the United States, with oversight by his adviser, Dr. Judith Kelley.

Your participation is entirely voluntary and you are free to skip any question or withdraw from the survey at any time. The survey should take about **15 minutes** to complete. ***Please answer in whatever language you feel most comfortable using***.

Results from the survey will be used in aggregate so that it will not be possible to identify any individual organization. You can also explicitly choose to remain anonymous. Your responses will be securely transmitted to Qualtrics.com and stored in a password protected electronic format. The information you provide will be analyzed with statistical software and used in academic research.

You will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights in how INGOs relate to their host governments, which can benefit other similar organizations.

If you have any questions at any time about the study or the procedures, you can contact Andrew Heiss at andrew.heiss@duke.edu or +1 801-734-9327. You can also contact Dr. Judith Kelley at judith.kelley@duke.edu or +1 919-613-7343.

**I have read the above information, and I consent to take part in the study.**

:    Single answer

    - Yes
    - No

    If the respondent doesn't consent, skip to Q6.1 and end the survey

---

# Introductory questions

*Q2.1*: What is the name of your organization?

:   Text field

*Q2.2*: Where is your organization's headquarters?

:   Dropdown menu with [country names from the World Bank](/project/diss-ingos-in-autocracies/survey-countries/).

    Though dropdown menus are poor UI, [adding an autocomplete field to Qualtrics is doable](/project/diss-ingos-in-autocracies/survey-notes/), but tricky and won't always work consistently (e.g. if a respondent disables JavaScript, validating their response nearly impossible since they'll have to type the name of the country in blindly—and perfectly—to make it match the validating regex).

*Q2.3*: What is your position in your organization?

:    Single answer

    - Executive director
    - Program officer
    - Public relations officer
    - Staff member
    - Receptionist
    - Other:

---

*Q2.4*: Does your organization work in a country other than `home_country`?

:   If the respondent answers no, skip to Q7.1 and end the survey early since they're not an INGO

    Single answer

    - Yes
    - No

*Q2.5*: Besides `home_country`, where does your organization work?

:   Checkboxes with multiple answers allowed; each country is an option

    Horrible nasty UX here, but ¯\\\_(ツ)\_/¯. There's no good way to do this in Qualtrics

---

# Organizational questions

*Q3.1*: Which issues does your organization focus on? (select all that apply)

:   Multiple answers allowed

    - Development
    - Human rights
    - Environment
    - Education
    - Disaster relief
    - Freedom of expression
    - Democracy assistance
    - Human trafficking
    - Other:

*Q3.2*: Which issue does your organization focus on *the most*? (select one)

:   Single answer

    - Development
    - Human rights
    - Environment
    - Education
    - Disaster relief
    - Freedom of expression
    - Democracy assistance
    - Human trafficking
    - Other:

---

*Q3.3*: Please indicate how often your organization engages in each of these types of activities:

:   Qualtrics side-by-side table

    |                                                                                             | Always | Most of the time | About half the time | Sometimes | Never | Don't know | Not applicable | Please explain briefly |
    |---------------------------------------------------------------------------------------------|:------:|:----------------:|:-------------------:|:---------:|:-----:|:----------:|:--------------:|:----------------------:|
    | Providing direct aid and services                                                           |    •   |         •        |          •          |     •     |   •   |      •     |        •       |       Text field       |
    | Engaging in research and public education                                                   |    •   |         •        |          •          |     •     |   •   |      •     |        •       |       Text field       |
    | Mobilizing people (e.g. campaigns, public protests)                                         |    •   |         •        |          •          |     •     |   •   |      •     |        •       |       Text field       |
    | Engaging in advocacy                                                                        |    •   |         •        |          •          |     •     |   •   |      •     |        •       |       Text field       |
    | Monitoring and assessing the effects of policies, international agreements, and commitments |    •   |         •        |          •          |     •     |   •   |      •     |        •       |       Text field       |

---

*Q3.4*: Approximately how many full-time employees does your organization have?

:   Numeric text field

*Q3.5*: Approximately how many volunteers does your organization have?

:   Numeric text field

*Q3.6*: Does your organization collaborate with any of these organizations or institutions? (select all that apply)

:   Multiple answers allowed

    - Other nongovernmental organizations (NGOs)
    - International organizations (IGOs)
    - Governments
    - Corporations or businesses
    - Other:
    - Don't know
    - We do not collaborate with other organizations or institutions

*Q3.7*: Please list a few of the organizations or institutions you partner with most often:

:   Text field

*Q3.8*: How much of your organization's funding comes from each of these sources?

:   Qualtrics side-by-side table

    |                                                                                       | A great deal | A lot | A moderate amount | A little | None at all | Don't know | Not applicable |
    | ------------------------------------------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :---------: | :--------: | :------------: |
    | Individual donations                                                                  |      •       |   •   |         •         |    •     |      •      |     •      |       •        |
    | Corporate donations                                                                   |      •       |   •   |         •         |    •     |      •      |     •      |       •        |
    | Foundation donations                                                                  |      •       |   •   |         •         |    •     |      •      |     •      |       •        |
    | Grants from the government of the country in which your organization is headquartered |      •       |   •   |         •         |    •     |      •      |     •      |       •        |
    | Grants from the government of the country in which your organization works            |      •       |   •   |         •         |    •     |      •      |     •      |       •        |
    | Other                                                                                 |      •       |   •   |         •         |    •     |      •      |     •      |       •        |

---

*Q3.9*: In general, what would you say your organization is trying to accomplish?

:   Multiline text field

*Q3.10*: How is your organization's mission, vision, and values reflected in these objectives?

:   Multiline text field

*Q3.11*: Have these objectives changed at all in the last 10 years? If so, how?

:   Multiline text field

*Q3.12*: What are the major obstacles, if any, to reaching your organization's objectives?

:   Multiline text field

*Q3.13*: Are there any changes that you would like to see in your organization's goals and strategies, now or in the future?

:   Multiline text field

---

# Government relations

Enable "Loop and merge" for this block. Respondents can fill out this section as many times as they want for each of the countries they work in.

[Qualtrics' solution for complicated looping and merging is pretty kludgy](https://support.qualtrics.com/survey-platform/edit-survey/block-options/loop-and-merge#LoopingBasedOnAYesNo). Respondents can repeat this block up to 5 times (regardless of how many countries they work in). The final question of this block, Q4.24, lets respondents either restart the block or continue to the next block.

In order to end the cycle of loops early, **each question in this block** needs to have display logic hiding itself if the respondent chooses to end the loop:

![Display logic for every question in the looped block](/files/images/survey-loop-display-logic.png){.pure-img-responsive}

It's a mess, but it works.

## General questions

*Q4.1*: I will now ask a series of questions about your organization's relationship to the government of one of the countries you work in. Please select a country you would like to discuss:

:   Single answer

    Options populated from the countries selected in Q2.5

*Q4.2*: How long has your organization worked in `target_country`?

:   Single answer

    - Less than 1 year
    - 1–4 years
    - 5–9 years
    - 10 years or more
    - Don't know

*Q4.3*: What does your organization do in `target_country`? (select all that apply)

:   Multiple answers allowed

    - Maintain a physical office staffed primarily by foreigners
    - Maintain a physical office staffed primarily by people from `target_country`
    - Provide funding to domestic NGOs
    - Partner with domestic NGOs
    - Don't know

*Q4.4*: Is your organization registered with the national government in `target_country`?

:   Single answer

    - Yes
    - No
    - Don't know

---

## Contact with government

*Q4.5*: About how often does your organization have contact with government or party officials in `target_country`?

:   Single answer

    - Once a week
    - Once a month
    - Once a year
    - Once every 2+ years
    - Never
    - Don't know
    - Other:

*Q4.6*: What kind of government officials does your organization have contact with? (select all that apply)

:   Multiple answers allowed

    - President or prime minister
    - Member of parliament
    - Head of a ministry
    - Ministry staff
    - Military
    - Police or internal security
    - Other:
    - We have no contact with government officials
    - Don't know

*Q4.7*: What kind of government officials does your organization have contact with *most often*? (select one)

:   Single answer

    - President or prime minister
    - Member of parliament
    - Head of a ministry
    - Ministry staff
    - Military
    - Police or internal security
    - Other:
    - We have no contact with government officials
    - Don't know

*Q4.8*: How often is your organization required to report to the government of `target_country`?

:   Single answer

    - Once a week
    - Once a month
    - Once a year
    - Once every few years
    - Never
    - Don't know
    - Other:

*Q4.9*: Are members of the government or ruling party of `target_country` involved in your work?

:   Single answer

    - Yes
    - No
    - Don't know

*Q4.10*: How is the government of `target_country` involved in your work?

:   Multiline text field

---

## Relationship with government

*Q4.11*: How would you characterize your organization's relationship with the government of `target_country`? *Please note all survey responses will be kept strictly confidential*.

:   Single answer

    - Extremely negative
    - Somewhat negative
    - Neither positive nor negative
    - Somewhat positive
    - Extremely positive
    - Don't know
    - Prefer not to answer

*Q4.12*: Briefly describe your organization's relationship with the government of `target_country`:

:   Multiline text field

---

## NGO regulations and restrictions

*Q4.13*: How familiar is your organization with regulations for international nongovernmental organizations (NGOs) in `target_country`?

:   Single answer

    - Extremely familiar
    - Very familiar
    - Moderately familiar
    - Slightly familiar
    - Not familiar at all
    - Don't know

*Q4.14*: How often do regulations for international NGOs in `target_country` change?

:   Single answer

    - Once a month
    - Once a year
    - Once every few years
    - Rarely
    - Never
    - Don't know

*Q4.15*: How does your organization find out about changes to NGO regulations in `target_country`? (select all that apply)

:   Multiple answers allowed

    - Government officials
    - Other NGOs
    - Newspapers, television, and other media
    - The internet
    - Other:
    - Don't know

---

*Q4.16*: How is your organization affected by the following types of legal regulations for international NGOs in `target_country`?

:   Matrix table

    Types of legal barriers adapted from the [2012 Defending Civil Society Report](http://www.defendingcivilsociety.org/dl/reports/DCS_Report_Second_Edition_English.pdf)

    |                                                     | A great deal | A lot | A moderate amount | A little | Not at all | Don't know | Not applicable |
    | --------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :--------: | :--------: | :------------: |
    | Regulations regarding registration                  |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding operations                    |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding speech and advocacy           |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding communication and cooperation |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding assembly                      |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
    | Regulations regarding resources                     |      •       |   •   |         •         |    •     |     •      |     •      |       •        |

---

*Q4.16a*: Please describe how your organization is affected by regulations regarding registration.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16b*: Please describe how your organization is affected by regulations regarding operations.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16c*: Please describe how your organization is affected by regulations regarding speech and advocacy.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16d*: Please describe how your organization is affected by regulations regarding communication and cooperation.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16e*: Please describe how your organization is affected by regulations regarding assembly.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

*Q4.16f*: Please describe how your organization is affected by regulations regarding resources.

:   Multiline text field

    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"

---

*Q4.17*: Overall, how is your organization's work affected by government regulations in `target_country`?

:   Single answer

    - Not restricted at all
    - Slightly restricted
    - Moderately restricted
    - Very restricted
    - Extremely restricted
    - Don't know

*Q4.18*: How do the local laws and regulations in `target_country` affect your organization's ability to pursue its mission?

:   Multiline text field

---

## Responses to regulations

*Q4.19*: Over the last 10 years, has your organization changed its mix of programming in `target_country`?

:   Single answer

    - Yes
    - No
    - Don't know

*Q4.20*: How has your organization's mix of programming changed in `target_country`?

:   Multiline text field

    Display if Q4.19 is "Yes"

*Q4.21*: Has your organization done any of the following in response to changes in government regulations in `target_country`?

:   Matrix table

    |                                                   | Yes |  No | Don’t know | Not applicable |
    | ------------------------------------------------- | :-: | :-: | :--------: | :------------: |
    | We changed the sources of our funding             |  •  |  •  |     •      |       •        |
    | We changed which issues we work on                |  •  |  •  |     •      |       •        |
    | We changed how we communicate with the government |  •  |  •  |     •      |       •        |
    | We changed how we communicate with our donors     |  •  |  •  |     •      |       •        |
    | We changed which locations we work in             |  •  |  •  |     •      |       •        |
    | We changed the location of our country office     |  •  |  •  |     •      |       •        |
    | We used more local staff and/or volunteers        |  •  |  •  |     •      |       •        |
    | We used more foreign staff and/or volunteers      |  •  |  •  |     •      |       •        |

---

*Q4.21a*: Please describe how your organization changed its funding sources. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21b*: Please describe how your organization changed which issues it works on. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21c*: Please describe how your organization changed how it communicates with the government. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21d*: Please describe how your organization changed how it communicates with donors. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21e*: Please describe how your organization changed the locations it works in. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21f*: Please describe how your organization changed the location of its country office. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21g*: Please describe how your organization used more local staff or volunteers. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

*Q4.21h*: Please describe how your organization used more foreign staff or volunteers. What regulation were you responding to?

:   Multiline text field

    Display if corresponding answer in Q4.21 is "Yes"

---

*Q4.22*: Has your organization discussed NGO regulations with government officials in `target_country`?

:   Single answer

    - Yes
    - No
    - Don't know

*Q4.23*: Has your organization tried to change NGO regulations in `target_country`?

:   Single answer

    - Yes
    - No
    - Don't know

---

*Q4.24*: That's all I need to know about your organization's work in `target_country`.<br><br>You can either answer the same set of questions for another country your organization works in (this would be helpful) or move on to the survey's final questions.

:   Single answer

    - Answer questions about another country
    - Continue with survey's final questions

---

# Final questions

*Q5.1*: Do you have any additional comments?

:   Multiline text field

---

*Q5.2*: May I contact you for any follow up questions?

:   Single answer

    - Yes
    - No

*Q5.3*: Would you like to be notified of the results of this survey once it is completed?

:   Single answer

    - Yes
    - No

*Q5.4*: Please provide an e-mail address I can use to contact you:

:   Text field

---

Thank you for participating in this research.

If you have any questions or concerns about this survey, please feel free to contact Andrew Heiss by e-mail at andrew.heiss@duke.edu or by phone at +1 801-734-9327

---

# Optional blocks

## No consent

*Q6.1*: I'm sorry you did not consent to participate in this research. Could you briefly explain why?

:   Multiline text field

## Not INGO

*Q7.1*: This survey is only concerned with international NGOs, or NGOs that work in countries other than the ones they are based in. Based on your responses, your organization only works in `home_country`, indicating that you are not an international NGO.<br><br>If this is a mistake and your organization does work abroad, click here to restart the survey. Otherwise, click on the forward arrow below to end the survey.<br><br>Thanks for your time!

:   Descriptive text

### 2023-05-16 notebook/survey-completion-rates.qmd
Add all files related to original survey

---
title: "Survey completion rates"
resources: 
  - files/*
format:
  html:
    include-in-header:
      - text: |
          <script src="files/htmlwidgets-0.6/htmlwidgets.js"></script>
          <link href="files/plotlyjs-1.10.1/plotly-htmlwidgets.css" rel="stylesheet" />
          <script src="files/plotlyjs-1.10.1/plotly-latest.min.js"></script>
          <script src="files/plotly-binding-3.6.0/plotly.js"></script>
---

::: {.callout-important}
# Important!

None of this code is generated automatically—it's all [static R output from my old notebook](https://notebook.andrewheiss.com/project/diss-ingos-in-autocracies/survey-completion-rates/). None of the file paths are accurate here. The code and output here are included for historical purposes.
:::

# Load and process all data

```r
library(dplyr)
library(tidyr)
library(stringr)
library(yaml)
library(purrr)
library(pander)
library(ggplot2)
library(ggrepel)
library(scales)
library(lubridate)
library(plotly)

panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('keep.line.breaks', TRUE)
panderOptions('table.style', 'multiline')
panderOptions('table.alignment.default', 'left')
```

## Dead addresses, domains, and bounces

```r
# Load data from tracking database
db.email <- src_sqlite(path=file.path(PROJHOME, "Data", "Survey", "list", 
                                      "final_list.db"))
email.full <- tbl(db.email, "full_list") %>% collect() %>%
  separate(id_org, c("db", "id.in.db"))
removed <- tbl(db.email, "remove") %>% collect()
bounced.raw <- tbl(db.email, "bounces") %>% collect()
completed <- tbl(db.email, "survey_completed") %>% collect()
sending.groups <- tbl(db.email, "groups") %>% collect()

email.by.db <- email.full %>%
  group_by(db) %>%
  summarise(num.apparently.valid = n())

dead.searches <- paste(c("Hippo", "Invalid", "Dead", "weird opt"), collapse="|")
dead <- removed %>%
  filter(str_detect(remove_notes, regex(dead.searches, ignore_case=TRUE))) %>%
  select(fk_org, notes = remove_notes)

bounced <- bounced.raw %>%
  gather(notes, value, hard_bounce, email_dead, email_bounce) %>%
  filter(value != 0) %>%
  select(fk_org, notes)

dead.and.bounced <- bind_rows(dead, bounced) %>%
  group_by(fk_org) %>%
  slice(1) %>%  # Get rid of duplicate removal entries
  ungroup() %>%
  left_join(select(email.full, fk_org = index_org, db), by="fk_org")

dead.and.bounced.by.db <- dead.and.bounced %>%
  group_by(db) %>%
  summarise(num.dead.bounced = n())

# Load full survey data (minus the Q4\* loop for simplicity)
survey.orgs.all <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                     "survey_orgs_all.rds"))

# Load cleaned, country-based survey data (*with* the Q4\* loop)
survey.clean.all <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                      "survey_clean_all.rds"))

# Load cleaned, organization-based data (without the Q4 loop)
survey.orgs.clean <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                       "survey_orgs_clean.rds"))

# Load cleaned, country-based data (only the Q4 loop)
survey.countries.clean <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                            "survey_countries_clean.rds"))

# Load valid partial responses
survey.partials <- readRDS(file.path(PROJHOME, "Data", "data_processed", 
                                     "survey_partials.rds"))
```

## Summarize response rates from each database

```r
# Load YAML metadata for survey lists
raw.lists <- yaml.load_file(file.path(PROJHOME, "data", "data_raw",
                                      "NGO lists", "ngo_lists.yml"),
                            as.named.list=TRUE)

# Convert to nice dataframe with purrr::map_df()
list.details <- seq(1:length(raw.lists$lists)) %>%
  map_df(function(x) raw.lists$lists[[x]][c("title", 'name',
                                            "num_rows_raw", "description")]) %>%
  arrange(desc(num_rows_raw))

response.summary <- list.details %>%
  left_join(email.by.db, by=c("name" = "db")) %>%
  left_join(dead.and.bounced.by.db, by=c("name" = "db")) %>%
  mutate(num.invited = num.apparently.valid - num.dead.bounced) %>%
  select(-c(description))

response.summary.total <- response.summary %>%
  summarise_each(funs(sum), -title, -name) %>%
  mutate(title = "**Total**")

response.summary.with.total <- bind_rows(response.summary,
                                         response.summary.total) %>%
  select(-name) %>%
  mutate(perc.valid = num.apparently.valid / num_rows_raw,
         perc.bounced.from.valid = num.dead.bounced / num.apparently.valid,
         perc.invited.from.raw = num.invited / num_rows_raw,
         perc.invited.from.valid = num.invited / num.apparently.valid)

response.summary.display <- response.summary.with.total %>%
  mutate_each(funs(comma), starts_with("num")) %>%
  mutate_each(funs(percent), starts_with("perc"))
```

Full technical details of how I ran the survey are available at my [research
notebook](https://notebook.andrewheiss.com/project/diss-ingos-in-autocracies/survey-technical-details/).

The complete database of NGOs to receive a survey invitation came from 
5 different sources. After collecting the details
of each organization listed at each source, I cleaned the raw lists by 
removing all organizations without valid e-mail addresses and by attempting 
to filter out obviously domestic NGOs. I filtered out domestic NGOs either 
by not collecting them in the first place (in the case of the Yearbook of
International Organizations), or using information from the database to
identify them. For example, the UN iCSCO database includes a field for an
organization's geographic scope: local, national, regional, and
international. I omitted local and national.

I filtered out invalid e-mail addresses using Email Hippo, which pings each
address to verify (1) that the domain exists, and (2) that the address
exists at the domain.

```r
pandoc.table(response.summary.display)
```

:::{.column-screen-inset-right}

-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
title                                                   num_rows_raw   num.apparently.valid   num.dead.bounced   num.invited   perc.valid   perc.bounced.from.valid   perc.invited.from.raw   perc.invited.from.valid  
------------------------------------------------------- -------------- ---------------------- ------------------ ------------- ------------ ------------------------- ----------------------- -------------------------
UN Integrated Civil Society Organizations System (iCSO) 27,028         7,498                  1,101              6,397         27.7%        14.7%                     23.7%                   85.3%

Directory of Development Organizations                  14,834         14,540                 7,457              7,083         98.0%        51.3%                     47.7%                   48.7%

Yearbook of International Organizations (YBIO)          9,325          3,065                  322                2,743         32.9%        10.5%                     29.4%                   89.5%

Global Anti-Human Trafficking (TIP) NGOs                1,421          1,063                  93                 970           74.8%        8.7%                      68.3%                   91.3%

Arab Institute of Human Rights NGO directory            761            606                    209                397           79.6%        34.5%                     52.2%                   65.5%

**Total**                                               53,369         26,772                 9,182              17,590        50.2%        34.3%                     33.0%                   65.7%                    
-----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------

:::

Some databases were more responsive than others (though this is hardly
accurate; half of the responses aren't linked to specific databases):

```r
survey.dbs <- survey.orgs.clean %>%
  group_by(database) %>%
  summarise(num.responses = n()) %>% 
  ungroup()

response.summary.actual <- survey.dbs %>%
  left_join(response.summary, by=c("database"="name")) %>%
  mutate(pct.responded.from.invited = num.responses / num.invited,
         pct.responded.clean = percent(pct.responded.from.invited)) %>%
  mutate(database = ifelse(database == "unknown", "zzzunknown", database),
         title = ifelse(is.na(title), "Unknown", title)) %>%
  arrange(database) %>%
  select(title, num.responses, num.invited, pct.responded.clean)
```

```r
pandoc.table(response.summary.actual)
```

-----------------------------------------------------------------------------------------------------------
title                                                   num.responses   num.invited   pct.responded.clean  
------------------------------------------------------- --------------- ------------- ---------------------
Arab Institute of Human Rights NGO directory            4               397           1.01%

Directory of Development Organizations                  59              7083          0.83%

UN Integrated Civil Society Organizations System (iCSO) 321             6397          5.02%

Global Anti-Human Trafficking (TIP) NGOs                30              970           3.09%

Yearbook of International Organizations (YBIO)          80              2743          2.92%

Unknown                                                 349             NA            NA%                  
-----------------------------------------------------------------------------------------------------------

## Figure out partials, incompletes, completes

Determine the best cutoff point for partially answered questions based on
the number of questions answered.

What was the minimum number of questions answered by an INGO that finished
the survey?

```r
complete.ingos <- survey.orgs.all %>%
  filter(Finished == 1, Q2.4 == "Yes") %>%
  # Count of Q* questions answered
  mutate(num.answered = rowSums(!is.na(select(., starts_with("Q")))))

min(complete.ingos$num.answered)
```

```
## [1] 17
```

Thus, my rough cut-off point for partials = 20.

However, some respondents quit before answering any questions about the 
countries they work in. I count any respondent that answered more than six 
questions in the loop of country questions. I use six because of how the Q4
variables are generated and cleaned. If an organization answered Q4.1 (the
country name), the script converted it to COW and ISO codes, resulting in 3
valid Q4.1 questions. Additionally, the script converts text-based Q4
questions into characters and will sometimes yield NULL instead of NA, which
then gets counted in the number of questions (so it's possible for a
respondent to answer just the country name and have that count as 6
questions). More than six quesion.

So, I use a combination of factors to determine partiality. A respondent has
to answer at least 20 questions, and at least 6 have to come from the Q4
loop. This is a better, more robust cutoff than simply using a 20-question
minimum arbitrarily.

Thus, there are this many valid partial responses:

```r
nrow(survey.orgs.clean)
```

```
## [1] 843
```

```r
table(survey.orgs.clean$complete)
```

```
## 
## FALSE  TRUE 
##   307   536
```

# Survey meta-metrics

## Absorption rate

> The absorption rate [measures] the ability of the survey company to manage
and keep up-to-date their database of email addresses and communications
with panel members [@CallegaroDiSogra:2008, 1026].

$$
\frac{EI - BB - NET}{EI}
$$

```r
EI <- response.summary.total$num.apparently.valid
BB.NET <- response.summary.total$num.dead.bounced

absorption.rate <- (EI - BB.NET) / EI
```

- EI = e-mail invitations sent: 26,772
- BB = bounced: 9,182
- NET = network undeliverable: included in `BB`
- **Absorption rate:** 65.7%

## Break-off rate

> The break-off rate is a possible indicator of problems in the design of
the questionnaire (e.g., too long, boring…) or struggle with technical
problems during the survey administration (e.g., streaming media or
animations that may “break” a survey at some point) 
[@CallegaroDiSogra:2008, 1026].

$$
\frac{BO}{I + P + BO}
$$

```r
# Only consider the organizations that were not screened out
survey.orgs.ingos <- survey.orgs.all %>%
  filter(Q2.4 == "Yes")

BO <- survey.orgs.ingos %>%
  filter(!(ResponseID %in% unique(c(survey.partials$ResponseID,
                                    survey.clean.all$ResponseID)))) %>%
  select(ResponseID) %>% unique() %>% nrow() %>% unlist()

I.survey <- survey.clean.all %>%
  filter(Finished == 1) %>% select(ResponseID) %>% 
  unique() %>% nrow() %>% unlist()

P.survey <- length(unique(survey.partials$ResponseID))

break.off.rate <- BO / (I.survey + P.survey + BO)
```

- BO = number of surveys broken off (i.e. incomplete and 
  not partial): 102
- I = complete: 536
- P = partial: 307
- **Break-off rate:** 10.8%

## Completion rate (participation rate)

> The most intuitive response metric is the survey's completion rate. It is
also the one metric most often mislabeled as a response rate. The completion
rate is the proportion of those who completed the Web survey among all the
eligible panel members who were invited to take the survey
[@CallegaroDiSogra:2008, 1021-22].

> Using such a rate as an indicator of possible nonresponse error makes
little sense; however, the participation rate may serve as a useful
indicator of panel efficiency [@AAPOR:2016, 49].

$$
\frac{I + P}{(I + P) + (R + NC + O)}
$$

```r
# Number who refused (i.e. explicitly did not give consent)
R.survey <- survey.orgs.all %>%
  select(Q6.1) %>%
  filter(!is.na(Q6.1)) %>%
  nrow() %>% unlist()
```

Non-contact is impossible to determine, since I don't know how many
organizations self-screened without taking the survey or e-mailing me. So,
this participation rate is not accurate, but no participation rate ever is.

```r
NC <- response.summary.total$num.invited - nrow(survey.orgs.all)

participation.rate <- (I.survey + P.survey) / 
  (I.survey + P.survey + BO + R.survey + NC)
```

- I = complete: 536
- P = partial: 307
- R = refusal and break-off: 102 (break-off) and 
  2 (refusal)
- NC = non-contact: 15,772
- O = other: None
- **Participation rate**: 5.04%

## Study-specific screening completion rates

> Study-specific screening completion rates and eligibility rates measure
the incidence of a particular phenomenon among panel members. When these
rates are significantly different from an external "gold standard," they may
indicate issues of question wording in the screener module or respondents
purposively self-selecting themselves for a particular study (e.g., to gain
rewards) even if they do not really qualify.… These rates may also reveal a
skew in the panel membership along a particular dimension that may raise
concerns regarding bias [@CallegaroDiSogra:2008, 1026].

$$
\frac{SCQ + SCNQ}{INV}
$$

```r
SCQ <- survey.orgs.all %>%
  filter(Q2.4 == "Yes") %>%
  select(ResponseID) %>%
  unique() %>% nrow() %>% unlist()

SCNQ <- survey.orgs.all %>%
  filter(Q2.4 == "No") %>%
  select(ResponseID) %>%
  unique() %>% nrow() %>% unlist()

INV <- response.summary.total$num.invited

screening.completion.rate <- (SCQ + SCNQ) / INV
```

- SCQ = screening completed and qualified: 945
- SCNQ = screening completed and not qualified (i.e. screened out): 478
- INV = survey invitations sent out: 17,590
- **Study-specific screening completion rate**: 8.09%

## Study-specific eligibility rate

> The problem with a screening rate is that nonresponse is confounded with
the screening. In fact, we do not know if a person qualifies unless they
provide that information by answering the screening questions. For this
reason, we talk about screening completion rate and not screening rate
[@CallegaroDiSogra:2008, 1023].

$$
\frac{SCQ}{SCQ + SCNQ}
$$

```r
study.eligibility.rate <- SCQ / (SCQ + SCNQ)
```

- SCQ = screening completed and qualified: 945
- SCNQ = screening completed and not qualified (i.e. screened out): 478
- **Study-specific eligibility rate**: 66.4%

# Other details

> In addition to these rates, we also believe that it is the best practice
to report the length of the field period with its start and close dates, the
number of reminders sent and their form (email, letter, IVR call, or
personal call), and the use of any incentive [@CallegaroDiSogra:2008, 1026].

## Timeline of e-mail invitations

```r
invited.groups.summary <- email.full %>%
  filter(!(index_org %in% dead.and.bounced$fk_org)) %>%
  mutate(id_group = as.integer(group)) %>%
  group_by(id_group) %>%
  summarise(num.in.group = n())

sending.groups.summary <- sending.groups %>%
  left_join(invited.groups.summary, by="id_group") %>%
  # Because I stupidly didn't include a final reminder column, I put the
  # timestamp of the final reminder in the notes column. This extracts the
  # timestamp with a regex.
  mutate(email_final_reminder = 
           str_extract(notes, "\\d{4}-\\d{2}-\\d{2} \\d{2}:\\d{2}:\\d{2}")) %>%
  mutate_each(funs(ymd_hms), starts_with("email")) %>%
  gather(email_type, email_date, starts_with("email")) %>%
  # Make Group 9's reminder be the final reminder
  mutate(email_type = ifelse(email_type == "email_reminder" & id_group == 9,
                             "email_final_reminder", email_type))

make_range <- function(x) {
  if (length(x) == 1) {
    return(paste("Group", as.character(x)))
  } else {
    return(paste0("Groups ", min(x), "-", max(x)))
  }
}

sending.groups.plot <- sending.groups.summary %>%
  mutate(email_day = ceiling_date(email_date, unit="day")) %>%
  filter(!is.na(email_day)) %>%
  group_by(email_day, email_type) %>%
  summarise(emails_sent = sum(num.in.group),
            group_names = make_range(id_group)) %>%
  ungroup() %>%
  mutate(total = cumsum(emails_sent),
         email_type = factor(email_type, 
                             levels=c("email_invitation", "email_reminder", 
                                      "email_final_reminder"),
                             label=c("Invitation  ", "Reminder  ", "Final reminder"),
                             ordered=TRUE))

plot.timeline <- ggplot(sending.groups.plot, aes(x=email_day, y=total)) +
  geom_step(size=0.5, colour="grey50") + 
  scale_y_continuous(labels=comma) +
  scale_x_datetime(date_labels="%B %e", date_breaks="1 week") +
  guides(fill=FALSE, colour=guide_legend(title=NULL)) +
  labs(x=NULL, y="Approximate total number of emails") +
  theme_light()

plot.timeline.static <- plot.timeline + 
  geom_point(aes(color=email_type)) + 
  geom_label_repel(aes(label=group_names, fill=email_type),
                   size=2.5, colour="white") +
  theme(legend.position="bottom", 
        legend.key.size=unit(0.65, "lines"),
        legend.key=element_blank(),
        panel.grid.minor=element_blank())

plot.timeline.interactive <- plot.timeline +
  geom_point(aes(color=email_type, text=group_names))

ggplotly(plot.timeline.interactive)
```

```{=html}
<div id="htmlwidget-5736" style="width:672px;height:480px;" class="plotly html-widget"></div>
<script type="application/json" data-for="htmlwidget-5736">{"x":{"data":[{"x":[1461196800,1461283200,1461369600,1461888000,1461974400,1462233600,1462320000,1462924800,1465257600,1465344000,1465344000,1467158400],"y":[1293,3003,4223,6725,8093,16955,21178,33910,46642,50865,51500,52135],"text":["email_day: 2016-04-20 20:00:00<br>total: 1293","email_day: 2016-04-21 20:00:00<br>total: 3003","email_day: 2016-04-22 20:00:00<br>total: 4223","email_day: 2016-04-28 20:00:00<br>total: 6725","email_day: 2016-04-29 20:00:00<br>total: 8093","email_day: 2016-05-02 20:00:00<br>total: 16955","email_day: 2016-05-03 20:00:00<br>total: 21178","email_day: 2016-05-10 20:00:00<br>total: 33910","email_day: 2016-06-06 20:00:00<br>total: 46642","email_day: 2016-06-07 20:00:00<br>total: 50865","email_day: 2016-06-07 20:00:00<br>total: 51500","email_day: 2016-06-28 20:00:00<br>total: 52135"],"key":null,"type":"scatter","mode":"lines","name":"","line":{"width":1.88976377952756,"color":"rgba(127,127,127,1)","dash":"solid","shape":"hv"},"showlegend":false,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1461196800,1461283200,1461369600,1461888000,1461974400,1462233600,1465344000],"y":[1293,3003,4223,6725,8093,16955,51500],"text":["email_day: 2016-04-20 20:00:00<br>total: 1293<br>email_type: Invitation  <br>Groups 1-3","email_day: 2016-04-21 20:00:00<br>total: 3003<br>email_type: Invitation  <br>Groups 4-6","email_day: 2016-04-22 20:00:00<br>total: 4223<br>email_type: Invitation  <br>Groups 7-8","email_day: 2016-04-28 20:00:00<br>total: 6725<br>email_type: Invitation  <br>Groups 10-13","email_day: 2016-04-29 20:00:00<br>total: 8093<br>email_type: Invitation  <br>Groups 14-15","email_day: 2016-05-02 20:00:00<br>total: 16955<br>email_type: Invitation  <br>Groups 16-28","email_day: 2016-06-07 20:00:00<br>total: 51500<br>email_type: Invitation  <br>Group 9"],"key":null,"type":"scatter","mode":"markers","marker":{"autocolorscale":false,"color":"rgba(248,118,109,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)"}},"name":"Invitation  ","legendgroup":"Invitation  ","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1462320000,1462924800],"y":[21178,33910],"text":["email_day: 2016-05-03 20:00:00<br>total: 21178<br>email_type: Reminder  <br>Groups 1-8","email_day: 2016-05-10 20:00:00<br>total: 33910<br>email_type: Reminder  <br>Groups 10-28"],"key":null,"type":"scatter","mode":"markers","marker":{"autocolorscale":false,"color":"rgba(0,186,56,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,186,56,1)"}},"name":"Reminder  ","legendgroup":"Reminder  ","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1465257600,1465344000,1467158400],"y":[46642,50865,52135],"text":["email_day: 2016-06-06 20:00:00<br>total: 46642<br>email_type: Final reminder<br>Groups 10-28","email_day: 2016-06-07 20:00:00<br>total: 50865<br>email_type: Final reminder<br>Groups 1-8","email_day: 2016-06-28 20:00:00<br>total: 52135<br>email_type: Final reminder<br>Group 9"],"key":null,"type":"scatter","mode":"markers","marker":{"autocolorscale":false,"color":"rgba(97,156,255,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(97,156,255,1)"}},"name":"Final reminder","legendgroup":"Final reminder","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"}],"layout":{"margin":{"b":27.8953922789539,"l":66.1519302615193,"t":27.1581569115816,"r":7.97011207970112},"plot_bgcolor":"rgba(255,255,255,1)","paper_bgcolor":"rgba(255,255,255,1)","font":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"xaxis":{"type":"linear","autorange":false,"tickmode":"array","range":[1460898720,1467456480],"ticktext":["April 18","April 25","May  2","May  9","May 16","May 23","May 30","June  6","June 13","June 20","June 27"],"tickvals":[1460937600,1461542400,1462147200,1462752000,1463356800,1463961600,1464566400,1465171200,1465776000,1466380800,1466985600],"ticks":"outside","tickcolor":"rgba(179,179,179,1)","ticklen":3.98505603985056,"tickwidth":0.33208800332088,"showticklabels":true,"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":12.7521793275218},"tickangle":-0,"showline":false,"linecolor":null,"linewidth":0,"showgrid":true,"domain":[0,1],"gridcolor":"rgba(217,217,217,1)","gridwidth":0.33208800332088,"zeroline":false,"anchor":"y","title":"","titlefont":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"hoverformat":".2f"},"yaxis":{"type":"linear","autorange":false,"tickmode":"array","range":[-1249.1,54677.1],"ticktext":["0","10,000","20,000","30,000","40,000","50,000"],"tickvals":[0,10000,20000,30000,40000,50000],"ticks":"outside","tickcolor":"rgba(179,179,179,1)","ticklen":3.98505603985056,"tickwidth":0.33208800332088,"showticklabels":true,"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":12.7521793275218},"tickangle":-0,"showline":false,"linecolor":null,"linewidth":0,"showgrid":true,"domain":[0,1],"gridcolor":"rgba(217,217,217,1)","gridwidth":0.33208800332088,"zeroline":false,"anchor":"x","title":"Approximate total number of emails","titlefont":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"hoverformat":".2f"},"shapes":[{"type":"rect","fillcolor":"transparent","line":{"color":"rgba(179,179,179,1)","width":0.66417600664176,"linetype":"solid"},"yref":"paper","xref":"paper","x0":0,"x1":1,"y0":0,"y1":1}],"showlegend":true,"legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":12.7521793275218},"y":1},"hovermode":"closest"},"source":"A","config":{"modeBarButtonsToRemove":["sendDataToCloud"]},"base_url":"https://plot.ly"},"evals":[],"jsHooks":[]}</script>
```

## Timeline of survey responses

```r
survey.time.plot <- survey.orgs.clean %>%
  select(EndDate) %>%
  arrange(EndDate) %>%
  mutate(done = 1,
         num.completed.cum = cumsum(done))

plot.responses.timeline <- ggplot() + 
  geom_step(data=survey.time.plot,
            aes(x=EndDate, y=num.completed.cum),
            size=0.5, colour="grey50") + 
  scale_y_continuous(labels=comma) +
  scale_x_datetime(date_labels="%B %e", date_breaks="1 week") +
  guides(fill=FALSE, colour=guide_legend(title=NULL)) +
  labs(x=NULL, y="Cumulative number of responses") +
  theme_light()

plot.responses.timeline.static <- plot.responses.timeline +
  geom_vline(data=sending.groups.plot, 
             aes(xintercept=as.numeric(email_day), 
                 colour=email_type),
             size=0.5) + 
  geom_label_repel(data=sending.groups.plot,
                   aes(x=email_day, y=400, 
                       label=group_names, fill=email_type),
                   size=2.5, colour="white") +
  theme(legend.position="bottom", 
        legend.key.size=unit(0.65, "lines"),
        legend.key=element_blank(),
        panel.grid.minor=element_blank())

plot.responses.timeline.interactive <- plot.responses.timeline +
  geom_vline(data=sending.groups.plot, 
             aes(xintercept=as.numeric(email_day), 
                 colour=email_type, text=group_names),
             size=0.5)

ggplotly(plot.responses.timeline.interactive)
```

```{=html}
<div id="htmlwidget-1194" style="width:672px;height:480px;" class="plotly html-widget"></div>
<script type="application/json" data-for="htmlwidget-1194">{"x":{"data":[{"x":[1461172871,1461175205,1461178013,1461178218,1461179934,1461188367,1461191621,1461193969,1461198809,1461199308,1461208238,1461208973,1461210053,1461216330,1461220382,1461222746,1461232926,1461235755,1461238929,1461240578,1461241221,1461249469,1461251376,1461252980,1461253467,1461256412,1461257446,1461259492,1461259825,1461261365,1461263247,1461263702,1461266777,1461267859,1461272024,1461277983,1461285841,1461288655,1461292369,1461294450,1461296570,1461297974,1461299294,1461299539,1461300020,1461301925,1461302433,1461305921,1461306744,1461308434,1461309322,1461313975,1461314995,1461316204,1461319559,1461320094,1461323255,1461325215,1461326441,1461329400,1461329790,1461335646,1461337055,1461337092,1461337270,1461337925,1461340114,1461344149,1461356158,1461362601,1461364525,1461366567,1461370255,1461376829,1461379596,1461403519,1461403583,1461414458,1461420578,1461420669,1461423681,1461424860,1461429365,1461437253,1461487964,1461532853,1461536263,1461553728,1461559483,1461559577,1461560532,1461566049,1461566552,1461585671,1461586581,1461587349,1461589707,1461594094,1461597189,1461602309,1461603614,1461604125,1461604500,1461604834,1461641026,1461642570,1461646792,1461651023,1461652953,1461657730,1461659552,1461662133,1461665652,1461667994,1461671605,1461679331,1461679386,1461682953,1461685982,1461705046,1461724505,1461734541,1461746925,1461749295,1461756690,1461761978,1461781438,1461797893,1461798488,1461831800,1461837659,1461840757,1461841224,1461843604,1461848617,1461849280,1461849375,1461850206,1461850734,1461851198,1461851524,1461851532,1461852730,1461852948,1461854870,1461856691,1461857189,1461859929,1461860786,1461865098,1461866342,1461869824,1461877983,1461881438,1461883030,1461885288,1461886318,1461889850,1461892140,1461894372,1461901329,1461906610,1461912420,1461918711,1461919553,1461924939,1461929598,1461932909,1461933163,1461935224,1461935437,1461936032,1461937829,1461938423,1461939772,1461945035,1461965136,1461969284,1461987537,1461994578,1461996857,1461997522,1461998286,1462003949,1462004313,1462006093,1462017314,1462017429,1462018299,1462054141,1462087016,1462089015,1462094253,1462095244,1462105848,1462112661,1462149451,1462160340,1462161318,1462166046,1462174836,1462183302,1462185559,1462186933,1462187000,1462187077,1462187092,1462187101,1462187370,1462187680,1462187868,1462189004,1462189331,1462189479,1462189781,1462189806,1462190302,1462190370,1462190640,1462190861,1462191238,1462191503,1462191702,1462191818,1462192090,1462192356,1462192421,1462192542,1462192542,1462192564,1462192769,1462192777,1462193008,1462193047,1462193206,1462193753,1462193876,1462194291,1462194292,1462194436,1462194445,1462194754,1462194836,1462195237,1462195420,1462195776,1462195825,1462195829,1462196354,1462196511,1462197483,1462197984,1462199014,1462199064,1462199389,1462199457,1462199634,1462199731,1462199746,1462199797,1462200040,1462200178,1462201239,1462201716,1462201868,1462202203,1462202402,1462203158,1462205310,1462205493,1462205919,1462205956,1462206186,1462206374,1462206916,1462207112,1462207934,1462208100,1462212142,1462214042,1462214059,1462216349,1462218086,1462222440,1462224019,1462224880,1462225139,1462228153,1462232027,1462232525,1462234505,1462234517,1462238513,1462239764,1462242891,1462244072,1462245292,1462248226,1462249277,1462249493,1462250969,1462251267,1462252448,1462253452,1462255556,1462257460,1462258808,1462258901,1462259084,1462259502,1462259773,1462261448,1462262087,1462262139,1462265300,1462266009,1462267305,1462267388,1462268152,1462269286,1462270030,1462270337,1462270605,1462270770,1462271175,1462271354,1462271536,1462271863,1462271959,1462272050,1462272810,1462273395,1462275552,1462275810,1462276153,1462276446,1462277854,1462278232,1462280208,1462280857,1462285365,1462287776,1462289645,1462289897,1462290008,1462290665,1462290865,1462291184,1462291299,1462291519,1462291847,1462291976,1462292417,1462292544,1462293577,1462294608,1462296206,1462296248,1462297322,1462299519,1462301526,1462304126,1462306004,1462309545,1462311571,1462320300,1462322313,1462322585,1462324224,1462324689,1462326620,1462328748,1462329636,1462332386,1462334691,1462335556,1462337178,1462339644,1462342492,1462342964,1462346319,1462347187,1462352677,1462353203,1462353843,1462358716,1462359772,1462360028,1462360576,1462361236,1462363467,1462363752,1462364851,1462368992,1462371890,1462372219,1462378099,1462378281,1462382079,1462384728,1462387322,1462399606,1462401821,1462410599,1462426318,1462433000,1462434744,1462436425,1462440282,1462447626,1462451394,1462451875,1462454654,1462455824,1462457718,1462458480,1462458621,1462462280,1462476076,1462478558,1462479040,1462480532,1462501959,1462507235,1462518083,1462524245,1462524983,1462527906,1462528064,1462532840,1462563850,1462573492,1462623357,1462627518,1462636046,1462659219,1462672167,1462704573,1462709259,1462742474,1462764494,1462768309,1462780559,1462784134,1462788870,1462789253,1462813022,1462819446,1462827787,1462846821,1462848818,1462855470,1462857011,1462857441,1462860821,1462870299,1462870698,1462873399,1462873862,1462874191,1462874366,1462875176,1462875631,1462876109,1462876436,1462877268,1462879201,1462879207,1462879245,1462879494,1462880571,1462880868,1462881255,1462881284,1462881736,1462881739,1462881885,1462882166,1462882460,1462882736,1462883241,1462883646,1462883903,1462883968,1462884809,1462885506,1462885512,1462885553,1462885852,1462885876,1462885954,1462886064,1462887051,1462887284,1462887775,1462888643,1462889019,1462893083,1462893110,1462893685,1462894319,1462894704,1462894869,1462896034,1462896285,1462897066,1462897444,1462897783,1462898098,1462898448,1462899163,1462899470,1462901306,1462901826,1462902323,1462904543,1462905196,1462905666,1462906217,1462907181,1462907438,1462910615,1462915755,1462917076,1462917272,1462917375,1462919382,1462921682,1462923425,1462928684,1462932169,1462932673,1462933247,1462934774,1462935183,1462936758,1462938948,1462939296,1462940055,1462940480,1462940547,1462940957,1462941614,1462942162,1462942180,1462943634,1462943897,1462944030,1462945035,1462947284,1462948216,1462949290,1462950096,1462951353,1462951405,1462953620,1462953886,1462954070,1462954116,1462954945,1462957800,1462958633,1462960778,1462960780,1462962211,1462962298,1462964780,1462965404,1462965964,1462967697,1462967819,1462968464,1462969197,1462971455,1462971485,1462972002,1462973323,1462975667,1462979602,1462981708,1462983063,1462984912,1462986151,1462989722,1462992881,1462996533,1463004659,1463006258,1463020211,1463025183,1463025883,1463027015,1463036492,1463036625,1463037955,1463040956,1463052112,1463057064,1463057252,1463058089,1463060739,1463062632,1463063099,1463064000,1463068090,1463082896,1463088922,1463089208,1463089804,1463109184,1463110292,1463113405,1463120075,1463121737,1463123177,1463123212,1463128443,1463128965,1463130908,1463130942,1463136335,1463138693,1463147273,1463148876,1463151417,1463153312,1463153986,1463224906,1463287280,1463297327,1463297704,1463300250,1463306845,1463314559,1463330241,1463359043,1463372267,1463373528,1463375800,1463384611,1463399021,1463399950,1463407396,1463452053,1463465392,1463468270,1463468771,1463471066,1463475144,1463475311,1463475334,1463480195,1463487531,1463489100,1463499915,1463513442,1463533054,1463542712,1463549827,1463558017,1463564666,1463573721,1463583833,1463599008,1463611621,1463631857,1463674077,1463688301,1463750047,1463773002,1464003232,1464021607,1464133638,1464239046,1464430228,1464648100,1464753080,1464890805,1465186169,1465226948,1465227071,1465227961,1465228627,1465230055,1465230067,1465230488,1465230875,1465230887,1465231150,1465232657,1465233911,1465233970,1465233993,1465235635,1465236134,1465238142,1465238411,1465238499,1465240190,1465241740,1465244792,1465246849,1465247321,1465247401,1465248196,1465250987,1465253084,1465253465,1465254542,1465255497,1465256239,1465261980,1465268764,1465269517,1465269742,1465270586,1465270624,1465271144,1465272333,1465272420,1465274543,1465274860,1465275734,1465276336,1465276540,1465278025,1465278443,1465278569,1465278940,1465279627,1465279774,1465280339,1465280840,1465281898,1465282582,1465282789,1465284405,1465284675,1465285269,1465285457,1465286202,1465286818,1465291095,1465294293,1465294999,1465300941,1465301729,1465303710,1465304394,1465305147,1465305827,1465308962,1465310007,1465321276,1465326792,1465332195,1465335829,1465337737,1465338551,1465339924,1465341696,1465344172,1465351918,1465355666,1465359115,1465359234,1465363714,1465367306,1465370816,1465375441,1465377781,1465381370,1465381678,1465384850,1465388290,1465392701,1465393703,1465395611,1465397836,1465404367,1465404978,1465408539,1465420769,1465444629,1465448021,1465449529,1465457474,1465467094,1465467587,1465472203,1465485659,1465486198,1465495512,1465497925,1465504982,1465506748,1465517651,1465526809,1465553691,1465553949,1465555016,1465560139,1465562234,1465563200,1465577109,1465579763,1465591944,1465593820,1465622106,1465648297,1465654313,1465658843,1465713957,1465730322,1465806746,1465808465,1465910089,1465912205,1465966112,1465980745,1465983324,1465986936,1465988925,1466000156,1466082588,1466120510,1466167639,1466213412,1466219588,1466318864,1466398212,1466445010,1466449732,1466516527,1466546160,1467163964,1467166334,1467186490,1467189650,1467197229,1467222135,1467388733,1467693554],"y":[1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54,55,56,57,58,59,60,61,62,63,64,65,66,67,68,69,70,71,72,73,74,75,76,77,78,79,80,81,82,83,84,85,86,87,88,89,90,91,92,93,94,95,96,97,98,99,100,101,102,103,104,105,106,107,108,109,110,111,112,113,114,115,116,117,118,119,120,121,122,123,124,125,126,127,128,129,130,131,132,133,134,135,136,137,138,139,140,141,142,143,144,145,146,147,148,149,150,151,152,153,154,155,156,157,158,159,160,161,162,163,164,165,166,167,168,169,170,171,172,173,174,175,176,177,178,179,180,181,182,183,184,185,186,187,188,189,190,191,192,193,194,195,196,197,198,199,200,201,202,203,204,205,206,207,208,209,210,211,212,213,214,215,216,217,218,219,220,221,222,223,224,225,226,227,228,229,230,231,232,233,234,235,236,237,238,239,240,241,242,243,244,245,246,247,248,249,250,251,252,253,254,255,256,257,258,259,260,261,262,263,264,265,266,267,268,269,270,271,272,273,274,275,276,277,278,279,280,281,282,283,284,285,286,287,288,289,290,291,292,293,294,295,296,297,298,299,300,301,302,303,304,305,306,307,308,309,310,311,312,313,314,315,316,317,318,319,320,321,322,323,324,325,326,327,328,329,330,331,332,333,334,335,336,337,338,339,340,341,342,343,344,345,346,347,348,349,350,351,352,353,354,355,356,357,358,359,360,361,362,363,364,365,366,367,368,369,370,371,372,373,374,375,376,377,378,379,380,381,382,383,384,385,386,387,388,389,390,391,392,393,394,395,396,397,398,399,400,401,402,403,404,405,406,407,408,409,410,411,412,413,414,415,416,417,418,419,420,421,422,423,424,425,426,427,428,429,430,431,432,433,434,435,436,437,438,439,440,441,442,443,444,445,446,447,448,449,450,451,452,453,454,455,456,457,458,459,460,461,462,463,464,465,466,467,468,469,470,471,472,473,474,475,476,477,478,479,480,481,482,483,484,485,486,487,488,489,490,491,492,493,494,495,496,497,498,499,500,501,502,503,504,505,506,507,508,509,510,511,512,513,514,515,516,517,518,519,520,521,522,523,524,525,526,527,528,529,530,531,532,533,534,535,536,537,538,539,540,541,542,543,544,545,546,547,548,549,550,551,552,553,554,555,556,557,558,559,560,561,562,563,564,565,566,567,568,569,570,571,572,573,574,575,576,577,578,579,580,581,582,583,584,585,586,587,588,589,590,591,592,593,594,595,596,597,598,599,600,601,602,603,604,605,606,607,608,609,610,611,612,613,614,615,616,617,618,619,620,621,622,623,624,625,626,627,628,629,630,631,632,633,634,635,636,637,638,639,640,641,642,643,644,645,646,647,648,649,650,651,652,653,654,655,656,657,658,659,660,661,662,663,664,665,666,667,668,669,670,671,672,673,674,675,676,677,678,679,680,681,682,683,684,685,686,687,688,689,690,691,692,693,694,695,696,697,698,699,700,701,702,703,704,705,706,707,708,709,710,711,712,713,714,715,716,717,718,719,720,721,722,723,724,725,726,727,728,729,730,731,732,733,734,735,736,737,738,739,740,741,742,743,744,745,746,747,748,749,750,751,752,753,754,755,756,757,758,759,760,761,762,763,764,765,766,767,768,769,770,771,772,773,774,775,776,777,778,779,780,781,782,783,784,785,786,787,788,789,790,791,792,793,794,795,796,797,798,799,800,801,802,803,804,805,806,807,808,809,810,811,812,813,814,815,816,817,818,819,820,821,822,823,824,825,826,827,828,829,830,831,832,833,834,835,836,837,838,839,840,841,842,843],"text":["EndDate: 2016-04-20 13:21:11<br>num.completed.cum: 1","EndDate: 2016-04-20 14:00:05<br>num.completed.cum: 2","EndDate: 2016-04-20 14:46:53<br>num.completed.cum: 3","EndDate: 2016-04-20 14:50:18<br>num.completed.cum: 4","EndDate: 2016-04-20 15:18:54<br>num.completed.cum: 5","EndDate: 2016-04-20 17:39:27<br>num.completed.cum: 6","EndDate: 2016-04-20 18:33:41<br>num.completed.cum: 7","EndDate: 2016-04-20 19:12:49<br>num.completed.cum: 8","EndDate: 2016-04-20 20:33:29<br>num.completed.cum: 9","EndDate: 2016-04-20 20:41:48<br>num.completed.cum: 10","EndDate: 2016-04-20 23:10:38<br>num.completed.cum: 11","EndDate: 2016-04-20 23:22:53<br>num.completed.cum: 12","EndDate: 2016-04-20 23:40:53<br>num.completed.cum: 13","EndDate: 2016-04-21 01:25:30<br>num.completed.cum: 14","EndDate: 2016-04-21 02:33:02<br>num.completed.cum: 15","EndDate: 2016-04-21 03:12:26<br>num.completed.cum: 16","EndDate: 2016-04-21 06:02:06<br>num.completed.cum: 17","EndDate: 2016-04-21 06:49:15<br>num.completed.cum: 18","EndDate: 2016-04-21 07:42:09<br>num.completed.cum: 19","EndDate: 2016-04-21 08:09:38<br>num.completed.cum: 20","EndDate: 2016-04-21 08:20:21<br>num.completed.cum: 21","EndDate: 2016-04-21 10:37:49<br>num.completed.cum: 22","EndDate: 2016-04-21 11:09:36<br>num.completed.cum: 23","EndDate: 2016-04-21 11:36:20<br>num.completed.cum: 24","EndDate: 2016-04-21 11:44:27<br>num.completed.cum: 25","EndDate: 2016-04-21 12:33:32<br>num.completed.cum: 26","EndDate: 2016-04-21 12:50:46<br>num.completed.cum: 27","EndDate: 2016-04-21 13:24:52<br>num.completed.cum: 28","EndDate: 2016-04-21 13:30:25<br>num.completed.cum: 29","EndDate: 2016-04-21 13:56:05<br>num.completed.cum: 30","EndDate: 2016-04-21 14:27:27<br>num.completed.cum: 31","EndDate: 2016-04-21 14:35:02<br>num.completed.cum: 32","EndDate: 2016-04-21 15:26:17<br>num.completed.cum: 33","EndDate: 2016-04-21 15:44:19<br>num.completed.cum: 34","EndDate: 2016-04-21 16:53:44<br>num.completed.cum: 35","EndDate: 2016-04-21 18:33:03<br>num.completed.cum: 36","EndDate: 2016-04-21 20:44:01<br>num.completed.cum: 37","EndDate: 2016-04-21 21:30:55<br>num.completed.cum: 38","EndDate: 2016-04-21 22:32:49<br>num.completed.cum: 39","EndDate: 2016-04-21 23:07:30<br>num.completed.cum: 40","EndDate: 2016-04-21 23:42:50<br>num.completed.cum: 41","EndDate: 2016-04-22 00:06:14<br>num.completed.cum: 42","EndDate: 2016-04-22 00:28:14<br>num.completed.cum: 43","EndDate: 2016-04-22 00:32:19<br>num.completed.cum: 44","EndDate: 2016-04-22 00:40:20<br>num.completed.cum: 45","EndDate: 2016-04-22 01:12:05<br>num.completed.cum: 46","EndDate: 2016-04-22 01:20:33<br>num.completed.cum: 47","EndDate: 2016-04-22 02:18:41<br>num.completed.cum: 48","EndDate: 2016-04-22 02:32:24<br>num.completed.cum: 49","EndDate: 2016-04-22 03:00:34<br>num.completed.cum: 50","EndDate: 2016-04-22 03:15:22<br>num.completed.cum: 51","EndDate: 2016-04-22 04:32:55<br>num.completed.cum: 52","EndDate: 2016-04-22 04:49:55<br>num.completed.cum: 53","EndDate: 2016-04-22 05:10:04<br>num.completed.cum: 54","EndDate: 2016-04-22 06:05:59<br>num.completed.cum: 55","EndDate: 2016-04-22 06:14:54<br>num.completed.cum: 56","EndDate: 2016-04-22 07:07:35<br>num.completed.cum: 57","EndDate: 2016-04-22 07:40:15<br>num.completed.cum: 58","EndDate: 2016-04-22 08:00:41<br>num.completed.cum: 59","EndDate: 2016-04-22 08:50:00<br>num.completed.cum: 60","EndDate: 2016-04-22 08:56:30<br>num.completed.cum: 61","EndDate: 2016-04-22 10:34:06<br>num.completed.cum: 62","EndDate: 2016-04-22 10:57:35<br>num.completed.cum: 63","EndDate: 2016-04-22 10:58:12<br>num.completed.cum: 64","EndDate: 2016-04-22 11:01:10<br>num.completed.cum: 65","EndDate: 2016-04-22 11:12:05<br>num.completed.cum: 66","EndDate: 2016-04-22 11:48:34<br>num.completed.cum: 67","EndDate: 2016-04-22 12:55:49<br>num.completed.cum: 68","EndDate: 2016-04-22 16:15:58<br>num.completed.cum: 69","EndDate: 2016-04-22 18:03:21<br>num.completed.cum: 70","EndDate: 2016-04-22 18:35:25<br>num.completed.cum: 71","EndDate: 2016-04-22 19:09:27<br>num.completed.cum: 72","EndDate: 2016-04-22 20:10:55<br>num.completed.cum: 73","EndDate: 2016-04-22 22:00:29<br>num.completed.cum: 74","EndDate: 2016-04-22 22:46:36<br>num.completed.cum: 75","EndDate: 2016-04-23 05:25:19<br>num.completed.cum: 76","EndDate: 2016-04-23 05:26:23<br>num.completed.cum: 77","EndDate: 2016-04-23 08:27:38<br>num.completed.cum: 78","EndDate: 2016-04-23 10:09:38<br>num.completed.cum: 79","EndDate: 2016-04-23 10:11:09<br>num.completed.cum: 80","EndDate: 2016-04-23 11:01:21<br>num.completed.cum: 81","EndDate: 2016-04-23 11:21:00<br>num.completed.cum: 82","EndDate: 2016-04-23 12:36:05<br>num.completed.cum: 83","EndDate: 2016-04-23 14:47:33<br>num.completed.cum: 84","EndDate: 2016-04-24 04:52:44<br>num.completed.cum: 85","EndDate: 2016-04-24 17:20:53<br>num.completed.cum: 86","EndDate: 2016-04-24 18:17:43<br>num.completed.cum: 87","EndDate: 2016-04-24 23:08:48<br>num.completed.cum: 88","EndDate: 2016-04-25 00:44:43<br>num.completed.cum: 89","EndDate: 2016-04-25 00:46:17<br>num.completed.cum: 90","EndDate: 2016-04-25 01:02:12<br>num.completed.cum: 91","EndDate: 2016-04-25 02:34:09<br>num.completed.cum: 92","EndDate: 2016-04-25 02:42:32<br>num.completed.cum: 93","EndDate: 2016-04-25 08:01:11<br>num.completed.cum: 94","EndDate: 2016-04-25 08:16:21<br>num.completed.cum: 95","EndDate: 2016-04-25 08:29:09<br>num.completed.cum: 96","EndDate: 2016-04-25 09:08:27<br>num.completed.cum: 97","EndDate: 2016-04-25 10:21:34<br>num.completed.cum: 98","EndDate: 2016-04-25 11:13:09<br>num.completed.cum: 99","EndDate: 2016-04-25 12:38:29<br>num.completed.cum: 100","EndDate: 2016-04-25 13:00:14<br>num.completed.cum: 101","EndDate: 2016-04-25 13:08:45<br>num.completed.cum: 102","EndDate: 2016-04-25 13:15:00<br>num.completed.cum: 103","EndDate: 2016-04-25 13:20:34<br>num.completed.cum: 104","EndDate: 2016-04-25 23:23:46<br>num.completed.cum: 105","EndDate: 2016-04-25 23:49:30<br>num.completed.cum: 106","EndDate: 2016-04-26 00:59:52<br>num.completed.cum: 107","EndDate: 2016-04-26 02:10:23<br>num.completed.cum: 108","EndDate: 2016-04-26 02:42:33<br>num.completed.cum: 109","EndDate: 2016-04-26 04:02:10<br>num.completed.cum: 110","EndDate: 2016-04-26 04:32:32<br>num.completed.cum: 111","EndDate: 2016-04-26 05:15:33<br>num.completed.cum: 112","EndDate: 2016-04-26 06:14:12<br>num.completed.cum: 113","EndDate: 2016-04-26 06:53:14<br>num.completed.cum: 114","EndDate: 2016-04-26 07:53:25<br>num.completed.cum: 115","EndDate: 2016-04-26 10:02:11<br>num.completed.cum: 116","EndDate: 2016-04-26 10:03:06<br>num.completed.cum: 117","EndDate: 2016-04-26 11:02:33<br>num.completed.cum: 118","EndDate: 2016-04-26 11:53:02<br>num.completed.cum: 119","EndDate: 2016-04-26 17:10:46<br>num.completed.cum: 120","EndDate: 2016-04-26 22:35:05<br>num.completed.cum: 121","EndDate: 2016-04-27 01:22:21<br>num.completed.cum: 122","EndDate: 2016-04-27 04:48:45<br>num.completed.cum: 123","EndDate: 2016-04-27 05:28:15<br>num.completed.cum: 124","EndDate: 2016-04-27 07:31:30<br>num.completed.cum: 125","EndDate: 2016-04-27 08:59:38<br>num.completed.cum: 126","EndDate: 2016-04-27 14:23:58<br>num.completed.cum: 127","EndDate: 2016-04-27 18:58:13<br>num.completed.cum: 128","EndDate: 2016-04-27 19:08:08<br>num.completed.cum: 129","EndDate: 2016-04-28 04:23:20<br>num.completed.cum: 130","EndDate: 2016-04-28 06:00:59<br>num.completed.cum: 131","EndDate: 2016-04-28 06:52:37<br>num.completed.cum: 132","EndDate: 2016-04-28 07:00:24<br>num.completed.cum: 133","EndDate: 2016-04-28 07:40:04<br>num.completed.cum: 134","EndDate: 2016-04-28 09:03:37<br>num.completed.cum: 135","EndDate: 2016-04-28 09:14:40<br>num.completed.cum: 136","EndDate: 2016-04-28 09:16:15<br>num.completed.cum: 137","EndDate: 2016-04-28 09:30:06<br>num.completed.cum: 138","EndDate: 2016-04-28 09:38:54<br>num.completed.cum: 139","EndDate: 2016-04-28 09:46:38<br>num.completed.cum: 140","EndDate: 2016-04-28 09:52:04<br>num.completed.cum: 141","EndDate: 2016-04-28 09:52:12<br>num.completed.cum: 142","EndDate: 2016-04-28 10:12:10<br>num.completed.cum: 143","EndDate: 2016-04-28 10:15:48<br>num.completed.cum: 144","EndDate: 2016-04-28 10:47:50<br>num.completed.cum: 145","EndDate: 2016-04-28 11:18:11<br>num.completed.cum: 146","EndDate: 2016-04-28 11:26:29<br>num.completed.cum: 147","EndDate: 2016-04-28 12:12:09<br>num.completed.cum: 148","EndDate: 2016-04-28 12:26:26<br>num.completed.cum: 149","EndDate: 2016-04-28 13:38:18<br>num.completed.cum: 150","EndDate: 2016-04-28 13:59:02<br>num.completed.cum: 151","EndDate: 2016-04-28 14:57:04<br>num.completed.cum: 152","EndDate: 2016-04-28 17:13:03<br>num.completed.cum: 153","EndDate: 2016-04-28 18:10:38<br>num.completed.cum: 154","EndDate: 2016-04-28 18:37:10<br>num.completed.cum: 155","EndDate: 2016-04-28 19:14:48<br>num.completed.cum: 156","EndDate: 2016-04-28 19:31:58<br>num.completed.cum: 157","EndDate: 2016-04-28 20:30:50<br>num.completed.cum: 158","EndDate: 2016-04-28 21:09:00<br>num.completed.cum: 159","EndDate: 2016-04-28 21:46:12<br>num.completed.cum: 160","EndDate: 2016-04-28 23:42:09<br>num.completed.cum: 161","EndDate: 2016-04-29 01:10:10<br>num.completed.cum: 162","EndDate: 2016-04-29 02:47:00<br>num.completed.cum: 163","EndDate: 2016-04-29 04:31:51<br>num.completed.cum: 164","EndDate: 2016-04-29 04:45:53<br>num.completed.cum: 165","EndDate: 2016-04-29 06:15:39<br>num.completed.cum: 166","EndDate: 2016-04-29 07:33:18<br>num.completed.cum: 167","EndDate: 2016-04-29 08:28:29<br>num.completed.cum: 168","EndDate: 2016-04-29 08:32:43<br>num.completed.cum: 169","EndDate: 2016-04-29 09:07:04<br>num.completed.cum: 170","EndDate: 2016-04-29 09:10:37<br>num.completed.cum: 171","EndDate: 2016-04-29 09:20:32<br>num.completed.cum: 172","EndDate: 2016-04-29 09:50:29<br>num.completed.cum: 173","EndDate: 2016-04-29 10:00:23<br>num.completed.cum: 174","EndDate: 2016-04-29 10:22:52<br>num.completed.cum: 175","EndDate: 2016-04-29 11:50:35<br>num.completed.cum: 176","EndDate: 2016-04-29 17:25:36<br>num.completed.cum: 177","EndDate: 2016-04-29 18:34:44<br>num.completed.cum: 178","EndDate: 2016-04-29 23:38:57<br>num.completed.cum: 179","EndDate: 2016-04-30 01:36:18<br>num.completed.cum: 180","EndDate: 2016-04-30 02:14:17<br>num.completed.cum: 181","EndDate: 2016-04-30 02:25:22<br>num.completed.cum: 182","EndDate: 2016-04-30 02:38:06<br>num.completed.cum: 183","EndDate: 2016-04-30 04:12:29<br>num.completed.cum: 184","EndDate: 2016-04-30 04:18:33<br>num.completed.cum: 185","EndDate: 2016-04-30 04:48:13<br>num.completed.cum: 186","EndDate: 2016-04-30 07:55:14<br>num.completed.cum: 187","EndDate: 2016-04-30 07:57:09<br>num.completed.cum: 188","EndDate: 2016-04-30 08:11:39<br>num.completed.cum: 189","EndDate: 2016-04-30 18:09:01<br>num.completed.cum: 190","EndDate: 2016-05-01 03:16:56<br>num.completed.cum: 191","EndDate: 2016-05-01 03:50:15<br>num.completed.cum: 192","EndDate: 2016-05-01 05:17:33<br>num.completed.cum: 193","EndDate: 2016-05-01 05:34:04<br>num.completed.cum: 194","EndDate: 2016-05-01 08:30:48<br>num.completed.cum: 195","EndDate: 2016-05-01 10:24:21<br>num.completed.cum: 196","EndDate: 2016-05-01 20:37:31<br>num.completed.cum: 197","EndDate: 2016-05-01 23:39:00<br>num.completed.cum: 198","EndDate: 2016-05-01 23:55:18<br>num.completed.cum: 199","EndDate: 2016-05-02 01:14:06<br>num.completed.cum: 200","EndDate: 2016-05-02 03:40:36<br>num.completed.cum: 201","EndDate: 2016-05-02 06:01:42<br>num.completed.cum: 202","EndDate: 2016-05-02 06:39:19<br>num.completed.cum: 203","EndDate: 2016-05-02 07:02:13<br>num.completed.cum: 204","EndDate: 2016-05-02 07:03:20<br>num.completed.cum: 205","EndDate: 2016-05-02 07:04:37<br>num.completed.cum: 206","EndDate: 2016-05-02 07:04:52<br>num.completed.cum: 207","EndDate: 2016-05-02 07:05:01<br>num.completed.cum: 208","EndDate: 2016-05-02 07:09:30<br>num.completed.cum: 209","EndDate: 2016-05-02 07:14:40<br>num.completed.cum: 210","EndDate: 2016-05-02 07:17:48<br>num.completed.cum: 211","EndDate: 2016-05-02 07:36:44<br>num.completed.cum: 212","EndDate: 2016-05-02 07:42:11<br>num.completed.cum: 213","EndDate: 2016-05-02 07:44:39<br>num.completed.cum: 214","EndDate: 2016-05-02 07:49:41<br>num.completed.cum: 215","EndDate: 2016-05-02 07:50:06<br>num.completed.cum: 216","EndDate: 2016-05-02 07:58:22<br>num.completed.cum: 217","EndDate: 2016-05-02 07:59:30<br>num.completed.cum: 218","EndDate: 2016-05-02 08:04:00<br>num.completed.cum: 219","EndDate: 2016-05-02 08:07:41<br>num.completed.cum: 220","EndDate: 2016-05-02 08:13:58<br>num.completed.cum: 221","EndDate: 2016-05-02 08:18:23<br>num.completed.cum: 222","EndDate: 2016-05-02 08:21:42<br>num.completed.cum: 223","EndDate: 2016-05-02 08:23:38<br>num.completed.cum: 224","EndDate: 2016-05-02 08:28:10<br>num.completed.cum: 225","EndDate: 2016-05-02 08:32:36<br>num.completed.cum: 226","EndDate: 2016-05-02 08:33:41<br>num.completed.cum: 227","EndDate: 2016-05-02 08:35:42<br>num.completed.cum: 228","EndDate: 2016-05-02 08:35:42<br>num.completed.cum: 229","EndDate: 2016-05-02 08:36:04<br>num.completed.cum: 230","EndDate: 2016-05-02 08:39:29<br>num.completed.cum: 231","EndDate: 2016-05-02 08:39:37<br>num.completed.cum: 232","EndDate: 2016-05-02 08:43:28<br>num.completed.cum: 233","EndDate: 2016-05-02 08:44:07<br>num.completed.cum: 234","EndDate: 2016-05-02 08:46:46<br>num.completed.cum: 235","EndDate: 2016-05-02 08:55:53<br>num.completed.cum: 236","EndDate: 2016-05-02 08:57:56<br>num.completed.cum: 237","EndDate: 2016-05-02 09:04:51<br>num.completed.cum: 238","EndDate: 2016-05-02 09:04:52<br>num.completed.cum: 239","EndDate: 2016-05-02 09:07:16<br>num.completed.cum: 240","EndDate: 2016-05-02 09:07:25<br>num.completed.cum: 241","EndDate: 2016-05-02 09:12:34<br>num.completed.cum: 242","EndDate: 2016-05-02 09:13:56<br>num.completed.cum: 243","EndDate: 2016-05-02 09:20:37<br>num.completed.cum: 244","EndDate: 2016-05-02 09:23:40<br>num.completed.cum: 245","EndDate: 2016-05-02 09:29:36<br>num.completed.cum: 246","EndDate: 2016-05-02 09:30:25<br>num.completed.cum: 247","EndDate: 2016-05-02 09:30:29<br>num.completed.cum: 248","EndDate: 2016-05-02 09:39:14<br>num.completed.cum: 249","EndDate: 2016-05-02 09:41:51<br>num.completed.cum: 250","EndDate: 2016-05-02 09:58:03<br>num.completed.cum: 251","EndDate: 2016-05-02 10:06:24<br>num.completed.cum: 252","EndDate: 2016-05-02 10:23:34<br>num.completed.cum: 253","EndDate: 2016-05-02 10:24:24<br>num.completed.cum: 254","EndDate: 2016-05-02 10:29:49<br>num.completed.cum: 255","EndDate: 2016-05-02 10:30:57<br>num.completed.cum: 256","EndDate: 2016-05-02 10:33:54<br>num.completed.cum: 257","EndDate: 2016-05-02 10:35:31<br>num.completed.cum: 258","EndDate: 2016-05-02 10:35:46<br>num.completed.cum: 259","EndDate: 2016-05-02 10:36:37<br>num.completed.cum: 260","EndDate: 2016-05-02 10:40:40<br>num.completed.cum: 261","EndDate: 2016-05-02 10:42:58<br>num.completed.cum: 262","EndDate: 2016-05-02 11:00:39<br>num.completed.cum: 263","EndDate: 2016-05-02 11:08:36<br>num.completed.cum: 264","EndDate: 2016-05-02 11:11:08<br>num.completed.cum: 265","EndDate: 2016-05-02 11:16:43<br>num.completed.cum: 266","EndDate: 2016-05-02 11:20:02<br>num.completed.cum: 267","EndDate: 2016-05-02 11:32:38<br>num.completed.cum: 268","EndDate: 2016-05-02 12:08:30<br>num.completed.cum: 269","EndDate: 2016-05-02 12:11:33<br>num.completed.cum: 270","EndDate: 2016-05-02 12:18:39<br>num.completed.cum: 271","EndDate: 2016-05-02 12:19:16<br>num.completed.cum: 272","EndDate: 2016-05-02 12:23:06<br>num.completed.cum: 273","EndDate: 2016-05-02 12:26:14<br>num.completed.cum: 274","EndDate: 2016-05-02 12:35:16<br>num.completed.cum: 275","EndDate: 2016-05-02 12:38:32<br>num.completed.cum: 276","EndDate: 2016-05-02 12:52:14<br>num.completed.cum: 277","EndDate: 2016-05-02 12:55:00<br>num.completed.cum: 278","EndDate: 2016-05-02 14:02:22<br>num.completed.cum: 279","EndDate: 2016-05-02 14:34:02<br>num.completed.cum: 280","EndDate: 2016-05-02 14:34:19<br>num.completed.cum: 281","EndDate: 2016-05-02 15:12:29<br>num.completed.cum: 282","EndDate: 2016-05-02 15:41:26<br>num.completed.cum: 283","EndDate: 2016-05-02 16:54:00<br>num.completed.cum: 284","EndDate: 2016-05-02 17:20:19<br>num.completed.cum: 285","EndDate: 2016-05-02 17:34:40<br>num.completed.cum: 286","EndDate: 2016-05-02 17:38:59<br>num.completed.cum: 287","EndDate: 2016-05-02 18:29:13<br>num.completed.cum: 288","EndDate: 2016-05-02 19:33:47<br>num.completed.cum: 289","EndDate: 2016-05-02 19:42:05<br>num.completed.cum: 290","EndDate: 2016-05-02 20:15:05<br>num.completed.cum: 291","EndDate: 2016-05-02 20:15:17<br>num.completed.cum: 292","EndDate: 2016-05-02 21:21:53<br>num.completed.cum: 293","EndDate: 2016-05-02 21:42:44<br>num.completed.cum: 294","EndDate: 2016-05-02 22:34:51<br>num.completed.cum: 295","EndDate: 2016-05-02 22:54:32<br>num.completed.cum: 296","EndDate: 2016-05-02 23:14:52<br>num.completed.cum: 297","EndDate: 2016-05-03 00:03:46<br>num.completed.cum: 298","EndDate: 2016-05-03 00:21:17<br>num.completed.cum: 299","EndDate: 2016-05-03 00:24:53<br>num.completed.cum: 300","EndDate: 2016-05-03 00:49:29<br>num.completed.cum: 301","EndDate: 2016-05-03 00:54:27<br>num.completed.cum: 302","EndDate: 2016-05-03 01:14:08<br>num.completed.cum: 303","EndDate: 2016-05-03 01:30:52<br>num.completed.cum: 304","EndDate: 2016-05-03 02:05:56<br>num.completed.cum: 305","EndDate: 2016-05-03 02:37:40<br>num.completed.cum: 306","EndDate: 2016-05-03 03:00:08<br>num.completed.cum: 307","EndDate: 2016-05-03 03:01:41<br>num.completed.cum: 308","EndDate: 2016-05-03 03:04:44<br>num.completed.cum: 309","EndDate: 2016-05-03 03:11:42<br>num.completed.cum: 310","EndDate: 2016-05-03 03:16:13<br>num.completed.cum: 311","EndDate: 2016-05-03 03:44:08<br>num.completed.cum: 312","EndDate: 2016-05-03 03:54:47<br>num.completed.cum: 313","EndDate: 2016-05-03 03:55:39<br>num.completed.cum: 314","EndDate: 2016-05-03 04:48:20<br>num.completed.cum: 315","EndDate: 2016-05-03 05:00:09<br>num.completed.cum: 316","EndDate: 2016-05-03 05:21:45<br>num.completed.cum: 317","EndDate: 2016-05-03 05:23:08<br>num.completed.cum: 318","EndDate: 2016-05-03 05:35:52<br>num.completed.cum: 319","EndDate: 2016-05-03 05:54:46<br>num.completed.cum: 320","EndDate: 2016-05-03 06:07:10<br>num.completed.cum: 321","EndDate: 2016-05-03 06:12:17<br>num.completed.cum: 322","EndDate: 2016-05-03 06:16:45<br>num.completed.cum: 323","EndDate: 2016-05-03 06:19:30<br>num.completed.cum: 324","EndDate: 2016-05-03 06:26:15<br>num.completed.cum: 325","EndDate: 2016-05-03 06:29:14<br>num.completed.cum: 326","EndDate: 2016-05-03 06:32:16<br>num.completed.cum: 327","EndDate: 2016-05-03 06:37:43<br>num.completed.cum: 328","EndDate: 2016-05-03 06:39:19<br>num.completed.cum: 329","EndDate: 2016-05-03 06:40:50<br>num.completed.cum: 330","EndDate: 2016-05-03 06:53:30<br>num.completed.cum: 331","EndDate: 2016-05-03 07:03:15<br>num.completed.cum: 332","EndDate: 2016-05-03 07:39:12<br>num.completed.cum: 333","EndDate: 2016-05-03 07:43:30<br>num.completed.cum: 334","EndDate: 2016-05-03 07:49:13<br>num.completed.cum: 335","EndDate: 2016-05-03 07:54:06<br>num.completed.cum: 336","EndDate: 2016-05-03 08:17:34<br>num.completed.cum: 337","EndDate: 2016-05-03 08:23:52<br>num.completed.cum: 338","EndDate: 2016-05-03 08:56:48<br>num.completed.cum: 339","EndDate: 2016-05-03 09:07:37<br>num.completed.cum: 340","EndDate: 2016-05-03 10:22:45<br>num.completed.cum: 341","EndDate: 2016-05-03 11:02:56<br>num.completed.cum: 342","EndDate: 2016-05-03 11:34:05<br>num.completed.cum: 343","EndDate: 2016-05-03 11:38:17<br>num.completed.cum: 344","EndDate: 2016-05-03 11:40:08<br>num.completed.cum: 345","EndDate: 2016-05-03 11:51:05<br>num.completed.cum: 346","EndDate: 2016-05-03 11:54:25<br>num.completed.cum: 347","EndDate: 2016-05-03 11:59:44<br>num.completed.cum: 348","EndDate: 2016-05-03 12:01:39<br>num.completed.cum: 349","EndDate: 2016-05-03 12:05:19<br>num.completed.cum: 350","EndDate: 2016-05-03 12:10:47<br>num.completed.cum: 351","EndDate: 2016-05-03 12:12:56<br>num.completed.cum: 352","EndDate: 2016-05-03 12:20:17<br>num.completed.cum: 353","EndDate: 2016-05-03 12:22:24<br>num.completed.cum: 354","EndDate: 2016-05-03 12:39:37<br>num.completed.cum: 355","EndDate: 2016-05-03 12:56:48<br>num.completed.cum: 356","EndDate: 2016-05-03 13:23:26<br>num.completed.cum: 357","EndDate: 2016-05-03 13:24:08<br>num.completed.cum: 358","EndDate: 2016-05-03 13:42:02<br>num.completed.cum: 359","EndDate: 2016-05-03 14:18:39<br>num.completed.cum: 360","EndDate: 2016-05-03 14:52:06<br>num.completed.cum: 361","EndDate: 2016-05-03 15:35:26<br>num.completed.cum: 362","EndDate: 2016-05-03 16:06:44<br>num.completed.cum: 363","EndDate: 2016-05-03 17:05:45<br>num.completed.cum: 364","EndDate: 2016-05-03 17:39:31<br>num.completed.cum: 365","EndDate: 2016-05-03 20:05:00<br>num.completed.cum: 366","EndDate: 2016-05-03 20:38:33<br>num.completed.cum: 367","EndDate: 2016-05-03 20:43:05<br>num.completed.cum: 368","EndDate: 2016-05-03 21:10:24<br>num.completed.cum: 369","EndDate: 2016-05-03 21:18:09<br>num.completed.cum: 370","EndDate: 2016-05-03 21:50:20<br>num.completed.cum: 371","EndDate: 2016-05-03 22:25:48<br>num.completed.cum: 372","EndDate: 2016-05-03 22:40:36<br>num.completed.cum: 373","EndDate: 2016-05-03 23:26:26<br>num.completed.cum: 374","EndDate: 2016-05-04 00:04:51<br>num.completed.cum: 375","EndDate: 2016-05-04 00:19:16<br>num.completed.cum: 376","EndDate: 2016-05-04 00:46:18<br>num.completed.cum: 377","EndDate: 2016-05-04 01:27:24<br>num.completed.cum: 378","EndDate: 2016-05-04 02:14:52<br>num.completed.cum: 379","EndDate: 2016-05-04 02:22:44<br>num.completed.cum: 380","EndDate: 2016-05-04 03:18:39<br>num.completed.cum: 381","EndDate: 2016-05-04 03:33:07<br>num.completed.cum: 382","EndDate: 2016-05-04 05:04:37<br>num.completed.cum: 383","EndDate: 2016-05-04 05:13:23<br>num.completed.cum: 384","EndDate: 2016-05-04 05:24:03<br>num.completed.cum: 385","EndDate: 2016-05-04 06:45:16<br>num.completed.cum: 386","EndDate: 2016-05-04 07:02:52<br>num.completed.cum: 387","EndDate: 2016-05-04 07:07:08<br>num.completed.cum: 388","EndDate: 2016-05-04 07:16:16<br>num.completed.cum: 389","EndDate: 2016-05-04 07:27:16<br>num.completed.cum: 390","EndDate: 2016-05-04 08:04:27<br>num.completed.cum: 391","EndDate: 2016-05-04 08:09:12<br>num.completed.cum: 392","EndDate: 2016-05-04 08:27:31<br>num.completed.cum: 393","EndDate: 2016-05-04 09:36:32<br>num.completed.cum: 394","EndDate: 2016-05-04 10:24:50<br>num.completed.cum: 395","EndDate: 2016-05-04 10:30:19<br>num.completed.cum: 396","EndDate: 2016-05-04 12:08:19<br>num.completed.cum: 397","EndDate: 2016-05-04 12:11:21<br>num.completed.cum: 398","EndDate: 2016-05-04 13:14:39<br>num.completed.cum: 399","EndDate: 2016-05-04 13:58:48<br>num.completed.cum: 400","EndDate: 2016-05-04 14:42:02<br>num.completed.cum: 401","EndDate: 2016-05-04 18:06:46<br>num.completed.cum: 402","EndDate: 2016-05-04 18:43:41<br>num.completed.cum: 403","EndDate: 2016-05-04 21:09:59<br>num.completed.cum: 404","EndDate: 2016-05-05 01:31:58<br>num.completed.cum: 405","EndDate: 2016-05-05 03:23:20<br>num.completed.cum: 406","EndDate: 2016-05-05 03:52:24<br>num.completed.cum: 407","EndDate: 2016-05-05 04:20:25<br>num.completed.cum: 408","EndDate: 2016-05-05 05:24:42<br>num.completed.cum: 409","EndDate: 2016-05-05 07:27:06<br>num.completed.cum: 410","EndDate: 2016-05-05 08:29:54<br>num.completed.cum: 411","EndDate: 2016-05-05 08:37:55<br>num.completed.cum: 412","EndDate: 2016-05-05 09:24:14<br>num.completed.cum: 413","EndDate: 2016-05-05 09:43:44<br>num.completed.cum: 414","EndDate: 2016-05-05 10:15:18<br>num.completed.cum: 415","EndDate: 2016-05-05 10:28:00<br>num.completed.cum: 416","EndDate: 2016-05-05 10:30:21<br>num.completed.cum: 417","EndDate: 2016-05-05 11:31:20<br>num.completed.cum: 418","EndDate: 2016-05-05 15:21:16<br>num.completed.cum: 419","EndDate: 2016-05-05 16:02:38<br>num.completed.cum: 420","EndDate: 2016-05-05 16:10:40<br>num.completed.cum: 421","EndDate: 2016-05-05 16:35:32<br>num.completed.cum: 422","EndDate: 2016-05-05 22:32:39<br>num.completed.cum: 423","EndDate: 2016-05-06 00:00:35<br>num.completed.cum: 424","EndDate: 2016-05-06 03:01:23<br>num.completed.cum: 425","EndDate: 2016-05-06 04:44:05<br>num.completed.cum: 426","EndDate: 2016-05-06 04:56:23<br>num.completed.cum: 427","EndDate: 2016-05-06 05:45:06<br>num.completed.cum: 428","EndDate: 2016-05-06 05:47:44<br>num.completed.cum: 429","EndDate: 2016-05-06 07:07:20<br>num.completed.cum: 430","EndDate: 2016-05-06 15:44:10<br>num.completed.cum: 431","EndDate: 2016-05-06 18:24:52<br>num.completed.cum: 432","EndDate: 2016-05-07 08:15:57<br>num.completed.cum: 433","EndDate: 2016-05-07 09:25:18<br>num.completed.cum: 434","EndDate: 2016-05-07 11:47:26<br>num.completed.cum: 435","EndDate: 2016-05-07 18:13:39<br>num.completed.cum: 436","EndDate: 2016-05-07 21:49:27<br>num.completed.cum: 437","EndDate: 2016-05-08 06:49:33<br>num.completed.cum: 438","EndDate: 2016-05-08 08:07:39<br>num.completed.cum: 439","EndDate: 2016-05-08 17:21:14<br>num.completed.cum: 440","EndDate: 2016-05-08 23:28:14<br>num.completed.cum: 441","EndDate: 2016-05-09 00:31:49<br>num.completed.cum: 442","EndDate: 2016-05-09 03:55:59<br>num.completed.cum: 443","EndDate: 2016-05-09 04:55:34<br>num.completed.cum: 444","EndDate: 2016-05-09 06:14:30<br>num.completed.cum: 445","EndDate: 2016-05-09 06:20:53<br>num.completed.cum: 446","EndDate: 2016-05-09 12:57:02<br>num.completed.cum: 447","EndDate: 2016-05-09 14:44:06<br>num.completed.cum: 448","EndDate: 2016-05-09 17:03:07<br>num.completed.cum: 449","EndDate: 2016-05-09 22:20:21<br>num.completed.cum: 450","EndDate: 2016-05-09 22:53:38<br>num.completed.cum: 451","EndDate: 2016-05-10 00:44:30<br>num.completed.cum: 452","EndDate: 2016-05-10 01:10:11<br>num.completed.cum: 453","EndDate: 2016-05-10 01:17:21<br>num.completed.cum: 454","EndDate: 2016-05-10 02:13:41<br>num.completed.cum: 455","EndDate: 2016-05-10 04:51:39<br>num.completed.cum: 456","EndDate: 2016-05-10 04:58:18<br>num.completed.cum: 457","EndDate: 2016-05-10 05:43:19<br>num.completed.cum: 458","EndDate: 2016-05-10 05:51:02<br>num.completed.cum: 459","EndDate: 2016-05-10 05:56:31<br>num.completed.cum: 460","EndDate: 2016-05-10 05:59:26<br>num.completed.cum: 461","EndDate: 2016-05-10 06:12:56<br>num.completed.cum: 462","EndDate: 2016-05-10 06:20:31<br>num.completed.cum: 463","EndDate: 2016-05-10 06:28:29<br>num.completed.cum: 464","EndDate: 2016-05-10 06:33:56<br>num.completed.cum: 465","EndDate: 2016-05-10 06:47:48<br>num.completed.cum: 466","EndDate: 2016-05-10 07:20:01<br>num.completed.cum: 467","EndDate: 2016-05-10 07:20:07<br>num.completed.cum: 468","EndDate: 2016-05-10 07:20:45<br>num.completed.cum: 469","EndDate: 2016-05-10 07:24:54<br>num.completed.cum: 470","EndDate: 2016-05-10 07:42:51<br>num.completed.cum: 471","EndDate: 2016-05-10 07:47:48<br>num.completed.cum: 472","EndDate: 2016-05-10 07:54:15<br>num.completed.cum: 473","EndDate: 2016-05-10 07:54:44<br>num.completed.cum: 474","EndDate: 2016-05-10 08:02:16<br>num.completed.cum: 475","EndDate: 2016-05-10 08:02:19<br>num.completed.cum: 476","EndDate: 2016-05-10 08:04:45<br>num.completed.cum: 477","EndDate: 2016-05-10 08:09:26<br>num.completed.cum: 478","EndDate: 2016-05-10 08:14:20<br>num.completed.cum: 479","EndDate: 2016-05-10 08:18:56<br>num.completed.cum: 480","EndDate: 2016-05-10 08:27:21<br>num.completed.cum: 481","EndDate: 2016-05-10 08:34:06<br>num.completed.cum: 482","EndDate: 2016-05-10 08:38:23<br>num.completed.cum: 483","EndDate: 2016-05-10 08:39:28<br>num.completed.cum: 484","EndDate: 2016-05-10 08:53:29<br>num.completed.cum: 485","EndDate: 2016-05-10 09:05:06<br>num.completed.cum: 486","EndDate: 2016-05-10 09:05:12<br>num.completed.cum: 487","EndDate: 2016-05-10 09:05:53<br>num.completed.cum: 488","EndDate: 2016-05-10 09:10:52<br>num.completed.cum: 489","EndDate: 2016-05-10 09:11:16<br>num.completed.cum: 490","EndDate: 2016-05-10 09:12:34<br>num.completed.cum: 491","EndDate: 2016-05-10 09:14:24<br>num.completed.cum: 492","EndDate: 2016-05-10 09:30:51<br>num.completed.cum: 493","EndDate: 2016-05-10 09:34:44<br>num.completed.cum: 494","EndDate: 2016-05-10 09:42:55<br>num.completed.cum: 495","EndDate: 2016-05-10 09:57:23<br>num.completed.cum: 496","EndDate: 2016-05-10 10:03:39<br>num.completed.cum: 497","EndDate: 2016-05-10 11:11:23<br>num.completed.cum: 498","EndDate: 2016-05-10 11:11:50<br>num.completed.cum: 499","EndDate: 2016-05-10 11:21:25<br>num.completed.cum: 500","EndDate: 2016-05-10 11:31:59<br>num.completed.cum: 501","EndDate: 2016-05-10 11:38:24<br>num.completed.cum: 502","EndDate: 2016-05-10 11:41:09<br>num.completed.cum: 503","EndDate: 2016-05-10 12:00:34<br>num.completed.cum: 504","EndDate: 2016-05-10 12:04:45<br>num.completed.cum: 505","EndDate: 2016-05-10 12:17:46<br>num.completed.cum: 506","EndDate: 2016-05-10 12:24:04<br>num.completed.cum: 507","EndDate: 2016-05-10 12:29:43<br>num.completed.cum: 508","EndDate: 2016-05-10 12:34:58<br>num.completed.cum: 509","EndDate: 2016-05-10 12:40:48<br>num.completed.cum: 510","EndDate: 2016-05-10 12:52:43<br>num.completed.cum: 511","EndDate: 2016-05-10 12:57:50<br>num.completed.cum: 512","EndDate: 2016-05-10 13:28:26<br>num.completed.cum: 513","EndDate: 2016-05-10 13:37:06<br>num.completed.cum: 514","EndDate: 2016-05-10 13:45:23<br>num.completed.cum: 515","EndDate: 2016-05-10 14:22:23<br>num.completed.cum: 516","EndDate: 2016-05-10 14:33:16<br>num.completed.cum: 517","EndDate: 2016-05-10 14:41:06<br>num.completed.cum: 518","EndDate: 2016-05-10 14:50:17<br>num.completed.cum: 519","EndDate: 2016-05-10 15:06:21<br>num.completed.cum: 520","EndDate: 2016-05-10 15:10:38<br>num.completed.cum: 521","EndDate: 2016-05-10 16:03:35<br>num.completed.cum: 522","EndDate: 2016-05-10 17:29:15<br>num.completed.cum: 523","EndDate: 2016-05-10 17:51:16<br>num.completed.cum: 524","EndDate: 2016-05-10 17:54:32<br>num.completed.cum: 525","EndDate: 2016-05-10 17:56:15<br>num.completed.cum: 526","EndDate: 2016-05-10 18:29:42<br>num.completed.cum: 527","EndDate: 2016-05-10 19:08:02<br>num.completed.cum: 528","EndDate: 2016-05-10 19:37:05<br>num.completed.cum: 529","EndDate: 2016-05-10 21:04:44<br>num.completed.cum: 530","EndDate: 2016-05-10 22:02:49<br>num.completed.cum: 531","EndDate: 2016-05-10 22:11:13<br>num.completed.cum: 532","EndDate: 2016-05-10 22:20:47<br>num.completed.cum: 533","EndDate: 2016-05-10 22:46:14<br>num.completed.cum: 534","EndDate: 2016-05-10 22:53:03<br>num.completed.cum: 535","EndDate: 2016-05-10 23:19:18<br>num.completed.cum: 536","EndDate: 2016-05-10 23:55:48<br>num.completed.cum: 537","EndDate: 2016-05-11 00:01:36<br>num.completed.cum: 538","EndDate: 2016-05-11 00:14:15<br>num.completed.cum: 539","EndDate: 2016-05-11 00:21:20<br>num.completed.cum: 540","EndDate: 2016-05-11 00:22:27<br>num.completed.cum: 541","EndDate: 2016-05-11 00:29:17<br>num.completed.cum: 542","EndDate: 2016-05-11 00:40:14<br>num.completed.cum: 543","EndDate: 2016-05-11 00:49:22<br>num.completed.cum: 544","EndDate: 2016-05-11 00:49:40<br>num.completed.cum: 545","EndDate: 2016-05-11 01:13:54<br>num.completed.cum: 546","EndDate: 2016-05-11 01:18:17<br>num.completed.cum: 547","EndDate: 2016-05-11 01:20:30<br>num.completed.cum: 548","EndDate: 2016-05-11 01:37:15<br>num.completed.cum: 549","EndDate: 2016-05-11 02:14:44<br>num.completed.cum: 550","EndDate: 2016-05-11 02:30:16<br>num.completed.cum: 551","EndDate: 2016-05-11 02:48:10<br>num.completed.cum: 552","EndDate: 2016-05-11 03:01:36<br>num.completed.cum: 553","EndDate: 2016-05-11 03:22:33<br>num.completed.cum: 554","EndDate: 2016-05-11 03:23:25<br>num.completed.cum: 555","EndDate: 2016-05-11 04:00:20<br>num.completed.cum: 556","EndDate: 2016-05-11 04:04:46<br>num.completed.cum: 557","EndDate: 2016-05-11 04:07:50<br>num.completed.cum: 558","EndDate: 2016-05-11 04:08:36<br>num.completed.cum: 559","EndDate: 2016-05-11 04:22:25<br>num.completed.cum: 560","EndDate: 2016-05-11 05:10:00<br>num.completed.cum: 561","EndDate: 2016-05-11 05:23:53<br>num.completed.cum: 562","EndDate: 2016-05-11 05:59:38<br>num.completed.cum: 563","EndDate: 2016-05-11 05:59:40<br>num.completed.cum: 564","EndDate: 2016-05-11 06:23:31<br>num.completed.cum: 565","EndDate: 2016-05-11 06:24:58<br>num.completed.cum: 566","EndDate: 2016-05-11 07:06:20<br>num.completed.cum: 567","EndDate: 2016-05-11 07:16:44<br>num.completed.cum: 568","EndDate: 2016-05-11 07:26:04<br>num.completed.cum: 569","EndDate: 2016-05-11 07:54:57<br>num.completed.cum: 570","EndDate: 2016-05-11 07:56:59<br>num.completed.cum: 571","EndDate: 2016-05-11 08:07:44<br>num.completed.cum: 572","EndDate: 2016-05-11 08:19:57<br>num.completed.cum: 573","EndDate: 2016-05-11 08:57:35<br>num.completed.cum: 574","EndDate: 2016-05-11 08:58:05<br>num.completed.cum: 575","EndDate: 2016-05-11 09:06:42<br>num.completed.cum: 576","EndDate: 2016-05-11 09:28:43<br>num.completed.cum: 577","EndDate: 2016-05-11 10:07:47<br>num.completed.cum: 578","EndDate: 2016-05-11 11:13:22<br>num.completed.cum: 579","EndDate: 2016-05-11 11:48:28<br>num.completed.cum: 580","EndDate: 2016-05-11 12:11:03<br>num.completed.cum: 581","EndDate: 2016-05-11 12:41:52<br>num.completed.cum: 582","EndDate: 2016-05-11 13:02:31<br>num.completed.cum: 583","EndDate: 2016-05-11 14:02:02<br>num.completed.cum: 584","EndDate: 2016-05-11 14:54:41<br>num.completed.cum: 585","EndDate: 2016-05-11 15:55:33<br>num.completed.cum: 586","EndDate: 2016-05-11 18:10:59<br>num.completed.cum: 587","EndDate: 2016-05-11 18:37:38<br>num.completed.cum: 588","EndDate: 2016-05-11 22:30:11<br>num.completed.cum: 589","EndDate: 2016-05-11 23:53:03<br>num.completed.cum: 590","EndDate: 2016-05-12 00:04:43<br>num.completed.cum: 591","EndDate: 2016-05-12 00:23:35<br>num.completed.cum: 592","EndDate: 2016-05-12 03:01:32<br>num.completed.cum: 593","EndDate: 2016-05-12 03:03:45<br>num.completed.cum: 594","EndDate: 2016-05-12 03:25:55<br>num.completed.cum: 595","EndDate: 2016-05-12 04:15:56<br>num.completed.cum: 596","EndDate: 2016-05-12 07:21:52<br>num.completed.cum: 597","EndDate: 2016-05-12 08:44:24<br>num.completed.cum: 598","EndDate: 2016-05-12 08:47:32<br>num.completed.cum: 599","EndDate: 2016-05-12 09:01:29<br>num.completed.cum: 600","EndDate: 2016-05-12 09:45:39<br>num.completed.cum: 601","EndDate: 2016-05-12 10:17:12<br>num.completed.cum: 602","EndDate: 2016-05-12 10:24:59<br>num.completed.cum: 603","EndDate: 2016-05-12 10:40:00<br>num.completed.cum: 604","EndDate: 2016-05-12 11:48:10<br>num.completed.cum: 605","EndDate: 2016-05-12 15:54:56<br>num.completed.cum: 606","EndDate: 2016-05-12 17:35:22<br>num.completed.cum: 607","EndDate: 2016-05-12 17:40:08<br>num.completed.cum: 608","EndDate: 2016-05-12 17:50:04<br>num.completed.cum: 609","EndDate: 2016-05-12 23:13:04<br>num.completed.cum: 610","EndDate: 2016-05-12 23:31:32<br>num.completed.cum: 611","EndDate: 2016-05-13 00:23:25<br>num.completed.cum: 612","EndDate: 2016-05-13 02:14:35<br>num.completed.cum: 613","EndDate: 2016-05-13 02:42:17<br>num.completed.cum: 614","EndDate: 2016-05-13 03:06:17<br>num.completed.cum: 615","EndDate: 2016-05-13 03:06:52<br>num.completed.cum: 616","EndDate: 2016-05-13 04:34:03<br>num.completed.cum: 617","EndDate: 2016-05-13 04:42:45<br>num.completed.cum: 618","EndDate: 2016-05-13 05:15:08<br>num.completed.cum: 619","EndDate: 2016-05-13 05:15:42<br>num.completed.cum: 620","EndDate: 2016-05-13 06:45:35<br>num.completed.cum: 621","EndDate: 2016-05-13 07:24:53<br>num.completed.cum: 622","EndDate: 2016-05-13 09:47:53<br>num.completed.cum: 623","EndDate: 2016-05-13 10:14:36<br>num.completed.cum: 624","EndDate: 2016-05-13 10:56:57<br>num.completed.cum: 625","EndDate: 2016-05-13 11:28:32<br>num.completed.cum: 626","EndDate: 2016-05-13 11:39:46<br>num.completed.cum: 627","EndDate: 2016-05-14 07:21:46<br>num.completed.cum: 628","EndDate: 2016-05-15 00:41:20<br>num.completed.cum: 629","EndDate: 2016-05-15 03:28:47<br>num.completed.cum: 630","EndDate: 2016-05-15 03:35:04<br>num.completed.cum: 631","EndDate: 2016-05-15 04:17:30<br>num.completed.cum: 632","EndDate: 2016-05-15 06:07:25<br>num.completed.cum: 633","EndDate: 2016-05-15 08:15:59<br>num.completed.cum: 634","EndDate: 2016-05-15 12:37:21<br>num.completed.cum: 635","EndDate: 2016-05-15 20:37:23<br>num.completed.cum: 636","EndDate: 2016-05-16 00:17:47<br>num.completed.cum: 637","EndDate: 2016-05-16 00:38:48<br>num.completed.cum: 638","EndDate: 2016-05-16 01:16:40<br>num.completed.cum: 639","EndDate: 2016-05-16 03:43:31<br>num.completed.cum: 640","EndDate: 2016-05-16 07:43:41<br>num.completed.cum: 641","EndDate: 2016-05-16 07:59:10<br>num.completed.cum: 642","EndDate: 2016-05-16 10:03:16<br>num.completed.cum: 643","EndDate: 2016-05-16 22:27:33<br>num.completed.cum: 644","EndDate: 2016-05-17 02:09:52<br>num.completed.cum: 645","EndDate: 2016-05-17 02:57:50<br>num.completed.cum: 646","EndDate: 2016-05-17 03:06:11<br>num.completed.cum: 647","EndDate: 2016-05-17 03:44:26<br>num.completed.cum: 648","EndDate: 2016-05-17 04:52:24<br>num.completed.cum: 649","EndDate: 2016-05-17 04:55:11<br>num.completed.cum: 650","EndDate: 2016-05-17 04:55:34<br>num.completed.cum: 651","EndDate: 2016-05-17 06:16:35<br>num.completed.cum: 652","EndDate: 2016-05-17 08:18:51<br>num.completed.cum: 653","EndDate: 2016-05-17 08:45:00<br>num.completed.cum: 654","EndDate: 2016-05-17 11:45:15<br>num.completed.cum: 655","EndDate: 2016-05-17 15:30:42<br>num.completed.cum: 656","EndDate: 2016-05-17 20:57:34<br>num.completed.cum: 657","EndDate: 2016-05-17 23:38:32<br>num.completed.cum: 658","EndDate: 2016-05-18 01:37:07<br>num.completed.cum: 659","EndDate: 2016-05-18 03:53:37<br>num.completed.cum: 660","EndDate: 2016-05-18 05:44:26<br>num.completed.cum: 661","EndDate: 2016-05-18 08:15:21<br>num.completed.cum: 662","EndDate: 2016-05-18 11:03:53<br>num.completed.cum: 663","EndDate: 2016-05-18 15:16:48<br>num.completed.cum: 664","EndDate: 2016-05-18 18:47:01<br>num.completed.cum: 665","EndDate: 2016-05-19 00:24:17<br>num.completed.cum: 666","EndDate: 2016-05-19 12:07:57<br>num.completed.cum: 667","EndDate: 2016-05-19 16:05:01<br>num.completed.cum: 668","EndDate: 2016-05-20 09:14:07<br>num.completed.cum: 669","EndDate: 2016-05-20 15:36:42<br>num.completed.cum: 670","EndDate: 2016-05-23 07:33:52<br>num.completed.cum: 671","EndDate: 2016-05-23 12:40:07<br>num.completed.cum: 672","EndDate: 2016-05-24 19:47:18<br>num.completed.cum: 673","EndDate: 2016-05-26 01:04:06<br>num.completed.cum: 674","EndDate: 2016-05-28 06:10:28<br>num.completed.cum: 675","EndDate: 2016-05-30 18:41:40<br>num.completed.cum: 676","EndDate: 2016-05-31 23:51:20<br>num.completed.cum: 677","EndDate: 2016-06-02 14:06:45<br>num.completed.cum: 678","EndDate: 2016-06-06 00:09:29<br>num.completed.cum: 679","EndDate: 2016-06-06 11:29:08<br>num.completed.cum: 680","EndDate: 2016-06-06 11:31:11<br>num.completed.cum: 681","EndDate: 2016-06-06 11:46:01<br>num.completed.cum: 682","EndDate: 2016-06-06 11:57:07<br>num.completed.cum: 683","EndDate: 2016-06-06 12:20:55<br>num.completed.cum: 684","EndDate: 2016-06-06 12:21:07<br>num.completed.cum: 685","EndDate: 2016-06-06 12:28:08<br>num.completed.cum: 686","EndDate: 2016-06-06 12:34:35<br>num.completed.cum: 687","EndDate: 2016-06-06 12:34:47<br>num.completed.cum: 688","EndDate: 2016-06-06 12:39:10<br>num.completed.cum: 689","EndDate: 2016-06-06 13:04:17<br>num.completed.cum: 690","EndDate: 2016-06-06 13:25:11<br>num.completed.cum: 691","EndDate: 2016-06-06 13:26:10<br>num.completed.cum: 692","EndDate: 2016-06-06 13:26:33<br>num.completed.cum: 693","EndDate: 2016-06-06 13:53:55<br>num.completed.cum: 694","EndDate: 2016-06-06 14:02:14<br>num.completed.cum: 695","EndDate: 2016-06-06 14:35:42<br>num.completed.cum: 696","EndDate: 2016-06-06 14:40:11<br>num.completed.cum: 697","EndDate: 2016-06-06 14:41:39<br>num.completed.cum: 698","EndDate: 2016-06-06 15:09:50<br>num.completed.cum: 699","EndDate: 2016-06-06 15:35:40<br>num.completed.cum: 700","EndDate: 2016-06-06 16:26:32<br>num.completed.cum: 701","EndDate: 2016-06-06 17:00:49<br>num.completed.cum: 702","EndDate: 2016-06-06 17:08:41<br>num.completed.cum: 703","EndDate: 2016-06-06 17:10:01<br>num.completed.cum: 704","EndDate: 2016-06-06 17:23:16<br>num.completed.cum: 705","EndDate: 2016-06-06 18:09:47<br>num.completed.cum: 706","EndDate: 2016-06-06 18:44:44<br>num.completed.cum: 707","EndDate: 2016-06-06 18:51:05<br>num.completed.cum: 708","EndDate: 2016-06-06 19:09:02<br>num.completed.cum: 709","EndDate: 2016-06-06 19:24:57<br>num.completed.cum: 710","EndDate: 2016-06-06 19:37:19<br>num.completed.cum: 711","EndDate: 2016-06-06 21:13:00<br>num.completed.cum: 712","EndDate: 2016-06-06 23:06:04<br>num.completed.cum: 713","EndDate: 2016-06-06 23:18:37<br>num.completed.cum: 714","EndDate: 2016-06-06 23:22:22<br>num.completed.cum: 715","EndDate: 2016-06-06 23:36:26<br>num.completed.cum: 716","EndDate: 2016-06-06 23:37:04<br>num.completed.cum: 717","EndDate: 2016-06-06 23:45:44<br>num.completed.cum: 718","EndDate: 2016-06-07 00:05:33<br>num.completed.cum: 719","EndDate: 2016-06-07 00:07:00<br>num.completed.cum: 720","EndDate: 2016-06-07 00:42:23<br>num.completed.cum: 721","EndDate: 2016-06-07 00:47:40<br>num.completed.cum: 722","EndDate: 2016-06-07 01:02:14<br>num.completed.cum: 723","EndDate: 2016-06-07 01:12:16<br>num.completed.cum: 724","EndDate: 2016-06-07 01:15:40<br>num.completed.cum: 725","EndDate: 2016-06-07 01:40:25<br>num.completed.cum: 726","EndDate: 2016-06-07 01:47:23<br>num.completed.cum: 727","EndDate: 2016-06-07 01:49:29<br>num.completed.cum: 728","EndDate: 2016-06-07 01:55:40<br>num.completed.cum: 729","EndDate: 2016-06-07 02:07:07<br>num.completed.cum: 730","EndDate: 2016-06-07 02:09:34<br>num.completed.cum: 731","EndDate: 2016-06-07 02:18:59<br>num.completed.cum: 732","EndDate: 2016-06-07 02:27:20<br>num.completed.cum: 733","EndDate: 2016-06-07 02:44:58<br>num.completed.cum: 734","EndDate: 2016-06-07 02:56:22<br>num.completed.cum: 735","EndDate: 2016-06-07 02:59:49<br>num.completed.cum: 736","EndDate: 2016-06-07 03:26:45<br>num.completed.cum: 737","EndDate: 2016-06-07 03:31:15<br>num.completed.cum: 738","EndDate: 2016-06-07 03:41:09<br>num.completed.cum: 739","EndDate: 2016-06-07 03:44:17<br>num.completed.cum: 740","EndDate: 2016-06-07 03:56:42<br>num.completed.cum: 741","EndDate: 2016-06-07 04:06:58<br>num.completed.cum: 742","EndDate: 2016-06-07 05:18:15<br>num.completed.cum: 743","EndDate: 2016-06-07 06:11:33<br>num.completed.cum: 744","EndDate: 2016-06-07 06:23:19<br>num.completed.cum: 745","EndDate: 2016-06-07 08:02:21<br>num.completed.cum: 746","EndDate: 2016-06-07 08:15:29<br>num.completed.cum: 747","EndDate: 2016-06-07 08:48:30<br>num.completed.cum: 748","EndDate: 2016-06-07 08:59:54<br>num.completed.cum: 749","EndDate: 2016-06-07 09:12:27<br>num.completed.cum: 750","EndDate: 2016-06-07 09:23:47<br>num.completed.cum: 751","EndDate: 2016-06-07 10:16:02<br>num.completed.cum: 752","EndDate: 2016-06-07 10:33:27<br>num.completed.cum: 753","EndDate: 2016-06-07 13:41:16<br>num.completed.cum: 754","EndDate: 2016-06-07 15:13:12<br>num.completed.cum: 755","EndDate: 2016-06-07 16:43:15<br>num.completed.cum: 756","EndDate: 2016-06-07 17:43:49<br>num.completed.cum: 757","EndDate: 2016-06-07 18:15:37<br>num.completed.cum: 758","EndDate: 2016-06-07 18:29:11<br>num.completed.cum: 759","EndDate: 2016-06-07 18:52:04<br>num.completed.cum: 760","EndDate: 2016-06-07 19:21:36<br>num.completed.cum: 761","EndDate: 2016-06-07 20:02:52<br>num.completed.cum: 762","EndDate: 2016-06-07 22:11:58<br>num.completed.cum: 763","EndDate: 2016-06-07 23:14:26<br>num.completed.cum: 764","EndDate: 2016-06-08 00:11:55<br>num.completed.cum: 765","EndDate: 2016-06-08 00:13:54<br>num.completed.cum: 766","EndDate: 2016-06-08 01:28:34<br>num.completed.cum: 767","EndDate: 2016-06-08 02:28:26<br>num.completed.cum: 768","EndDate: 2016-06-08 03:26:56<br>num.completed.cum: 769","EndDate: 2016-06-08 04:44:01<br>num.completed.cum: 770","EndDate: 2016-06-08 05:23:01<br>num.completed.cum: 771","EndDate: 2016-06-08 06:22:50<br>num.completed.cum: 772","EndDate: 2016-06-08 06:27:58<br>num.completed.cum: 773","EndDate: 2016-06-08 07:20:50<br>num.completed.cum: 774","EndDate: 2016-06-08 08:18:10<br>num.completed.cum: 775","EndDate: 2016-06-08 09:31:41<br>num.completed.cum: 776","EndDate: 2016-06-08 09:48:23<br>num.completed.cum: 777","EndDate: 2016-06-08 10:20:11<br>num.completed.cum: 778","EndDate: 2016-06-08 10:57:16<br>num.completed.cum: 779","EndDate: 2016-06-08 12:46:07<br>num.completed.cum: 780","EndDate: 2016-06-08 12:56:18<br>num.completed.cum: 781","EndDate: 2016-06-08 13:55:39<br>num.completed.cum: 782","EndDate: 2016-06-08 17:19:29<br>num.completed.cum: 783","EndDate: 2016-06-08 23:57:09<br>num.completed.cum: 784","EndDate: 2016-06-09 00:53:41<br>num.completed.cum: 785","EndDate: 2016-06-09 01:18:49<br>num.completed.cum: 786","EndDate: 2016-06-09 03:31:14<br>num.completed.cum: 787","EndDate: 2016-06-09 06:11:34<br>num.completed.cum: 788","EndDate: 2016-06-09 06:19:47<br>num.completed.cum: 789","EndDate: 2016-06-09 07:36:43<br>num.completed.cum: 790","EndDate: 2016-06-09 11:20:59<br>num.completed.cum: 791","EndDate: 2016-06-09 11:29:58<br>num.completed.cum: 792","EndDate: 2016-06-09 14:05:12<br>num.completed.cum: 793","EndDate: 2016-06-09 14:45:25<br>num.completed.cum: 794","EndDate: 2016-06-09 16:43:02<br>num.completed.cum: 795","EndDate: 2016-06-09 17:12:28<br>num.completed.cum: 796","EndDate: 2016-06-09 20:14:11<br>num.completed.cum: 797","EndDate: 2016-06-09 22:46:49<br>num.completed.cum: 798","EndDate: 2016-06-10 06:14:51<br>num.completed.cum: 799","EndDate: 2016-06-10 06:19:09<br>num.completed.cum: 800","EndDate: 2016-06-10 06:36:56<br>num.completed.cum: 801","EndDate: 2016-06-10 08:02:19<br>num.completed.cum: 802","EndDate: 2016-06-10 08:37:14<br>num.completed.cum: 803","EndDate: 2016-06-10 08:53:20<br>num.completed.cum: 804","EndDate: 2016-06-10 12:45:09<br>num.completed.cum: 805","EndDate: 2016-06-10 13:29:23<br>num.completed.cum: 806","EndDate: 2016-06-10 16:52:24<br>num.completed.cum: 807","EndDate: 2016-06-10 17:23:40<br>num.completed.cum: 808","EndDate: 2016-06-11 01:15:06<br>num.completed.cum: 809","EndDate: 2016-06-11 08:31:37<br>num.completed.cum: 810","EndDate: 2016-06-11 10:11:53<br>num.completed.cum: 811","EndDate: 2016-06-11 11:27:23<br>num.completed.cum: 812","EndDate: 2016-06-12 02:45:57<br>num.completed.cum: 813","EndDate: 2016-06-12 07:18:42<br>num.completed.cum: 814","EndDate: 2016-06-13 04:32:26<br>num.completed.cum: 815","EndDate: 2016-06-13 05:01:05<br>num.completed.cum: 816","EndDate: 2016-06-14 09:14:49<br>num.completed.cum: 817","EndDate: 2016-06-14 09:50:05<br>num.completed.cum: 818","EndDate: 2016-06-15 00:48:32<br>num.completed.cum: 819","EndDate: 2016-06-15 04:52:25<br>num.completed.cum: 820","EndDate: 2016-06-15 05:35:24<br>num.completed.cum: 821","EndDate: 2016-06-15 06:35:36<br>num.completed.cum: 822","EndDate: 2016-06-15 07:08:45<br>num.completed.cum: 823","EndDate: 2016-06-15 10:15:56<br>num.completed.cum: 824","EndDate: 2016-06-16 09:09:48<br>num.completed.cum: 825","EndDate: 2016-06-16 19:41:50<br>num.completed.cum: 826","EndDate: 2016-06-17 08:47:19<br>num.completed.cum: 827","EndDate: 2016-06-17 21:30:12<br>num.completed.cum: 828","EndDate: 2016-06-17 23:13:08<br>num.completed.cum: 829","EndDate: 2016-06-19 02:47:44<br>num.completed.cum: 830","EndDate: 2016-06-20 00:50:12<br>num.completed.cum: 831","EndDate: 2016-06-20 13:50:10<br>num.completed.cum: 832","EndDate: 2016-06-20 15:08:52<br>num.completed.cum: 833","EndDate: 2016-06-21 09:42:07<br>num.completed.cum: 834","EndDate: 2016-06-21 17:56:00<br>num.completed.cum: 835","EndDate: 2016-06-28 21:32:44<br>num.completed.cum: 836","EndDate: 2016-06-28 22:12:14<br>num.completed.cum: 837","EndDate: 2016-06-29 03:48:10<br>num.completed.cum: 838","EndDate: 2016-06-29 04:40:50<br>num.completed.cum: 839","EndDate: 2016-06-29 06:47:09<br>num.completed.cum: 840","EndDate: 2016-06-29 13:42:15<br>num.completed.cum: 841","EndDate: 2016-07-01 11:58:53<br>num.completed.cum: 842","EndDate: 2016-07-05 00:39:14<br>num.completed.cum: 843"],"key":null,"type":"scatter","mode":"lines","name":"","line":{"width":1.88976377952756,"color":"rgba(127,127,127,1)","dash":"solid","shape":"hv"},"showlegend":false,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1461196800,1461196800,null,1461283200,1461283200,null,1461369600,1461369600,null,1461888000,1461888000,null,1461974400,1461974400,null,1462233600,1462233600,null,1465344000,1465344000],"y":[-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1],"text":["as.numeric(email_day): 1461196800<br>email_type: Invitation  <br>Groups 1-3","as.numeric(email_day): 1461196800<br>email_type: Invitation  <br>Groups 1-3","as.numeric(email_day): 1461196800<br>email_type: Invitation  <br>Groups 1-3","as.numeric(email_day): 1461283200<br>email_type: Invitation  <br>Groups 4-6","as.numeric(email_day): 1461283200<br>email_type: Invitation  <br>Groups 4-6","as.numeric(email_day): 1461283200<br>email_type: Invitation  <br>Groups 4-6","as.numeric(email_day): 1461369600<br>email_type: Invitation  <br>Groups 7-8","as.numeric(email_day): 1461369600<br>email_type: Invitation  <br>Groups 7-8","as.numeric(email_day): 1461369600<br>email_type: Invitation  <br>Groups 7-8","as.numeric(email_day): 1461888000<br>email_type: Invitation  <br>Groups 10-13","as.numeric(email_day): 1461888000<br>email_type: Invitation  <br>Groups 10-13","as.numeric(email_day): 1461888000<br>email_type: Invitation  <br>Groups 10-13","as.numeric(email_day): 1461974400<br>email_type: Invitation  <br>Groups 14-15","as.numeric(email_day): 1461974400<br>email_type: Invitation  <br>Groups 14-15","as.numeric(email_day): 1461974400<br>email_type: Invitation  <br>Groups 14-15","as.numeric(email_day): 1462233600<br>email_type: Invitation  <br>Groups 16-28","as.numeric(email_day): 1462233600<br>email_type: Invitation  <br>Groups 16-28","as.numeric(email_day): 1462233600<br>email_type: Invitation  <br>Groups 16-28","as.numeric(email_day): 1465344000<br>email_type: Invitation  <br>Group 9","as.numeric(email_day): 1465344000<br>email_type: Invitation  <br>Group 9"],"key":null,"type":"scatter","mode":"lines","name":"Invitation  ","line":{"width":1.88976377952756,"color":"rgba(248,118,109,1)","dash":"solid"},"legendgroup":"Invitation  ","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1462320000,1462320000,null,1462924800,1462924800],"y":[-41.1,885.1,null,-41.1,885.1],"text":["as.numeric(email_day): 1462320000<br>email_type: Reminder  <br>Groups 1-8","as.numeric(email_day): 1462320000<br>email_type: Reminder  <br>Groups 1-8","as.numeric(email_day): 1462320000<br>email_type: Reminder  <br>Groups 1-8","as.numeric(email_day): 1462924800<br>email_type: Reminder  <br>Groups 10-28","as.numeric(email_day): 1462924800<br>email_type: Reminder  <br>Groups 10-28"],"key":null,"type":"scatter","mode":"lines","name":"Reminder  ","line":{"width":1.88976377952756,"color":"rgba(0,186,56,1)","dash":"solid"},"legendgroup":"Reminder  ","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"},{"x":[1465257600,1465257600,null,1465344000,1465344000,null,1467158400,1467158400],"y":[-41.1,885.1,null,-41.1,885.1,null,-41.1,885.1],"text":["as.numeric(email_day): 1465257600<br>email_type: Final reminder<br>Groups 10-28","as.numeric(email_day): 1465257600<br>email_type: Final reminder<br>Groups 10-28","as.numeric(email_day): 1465257600<br>email_type: Final reminder<br>Groups 10-28","as.numeric(email_day): 1465344000<br>email_type: Final reminder<br>Groups 1-8","as.numeric(email_day): 1465344000<br>email_type: Final reminder<br>Groups 1-8","as.numeric(email_day): 1465344000<br>email_type: Final reminder<br>Groups 1-8","as.numeric(email_day): 1467158400<br>email_type: Final reminder<br>Group 9","as.numeric(email_day): 1467158400<br>email_type: Final reminder<br>Group 9"],"key":null,"type":"scatter","mode":"lines","name":"Final reminder","line":{"width":1.88976377952756,"color":"rgba(97,156,255,1)","dash":"solid"},"legendgroup":"Final reminder","showlegend":true,"xaxis":"x","yaxis":"y","hoverinfo":"text"}],"layout":{"margin":{"b":27.8953922789539,"l":47.0236612702366,"t":27.1581569115816,"r":7.97011207970112},"plot_bgcolor":"rgba(255,255,255,1)","paper_bgcolor":"rgba(255,255,255,1)","font":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"xaxis":{"type":"linear","autorange":false,"tickmode":"array","range":[1460846836.85,1468019588.15],"ticktext":["April 18","April 25","May  2","May  9","May 16","May 23","May 30","June  6","June 13","June 20","June 27","July  4"],"tickvals":[1460937600,1461542400,1462147200,1462752000,1463356800,1463961600,1464566400,1465171200,1465776000,1466380800,1466985600,1467590400],"ticks":"outside","tickcolor":"rgba(179,179,179,1)","ticklen":3.98505603985056,"tickwidth":0.33208800332088,"showticklabels":true,"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":12.7521793275218},"tickangle":-0,"showline":false,"linecolor":null,"linewidth":0,"showgrid":true,"domain":[0,1],"gridcolor":"rgba(217,217,217,1)","gridwidth":0.33208800332088,"zeroline":false,"anchor":"y","title":"","titlefont":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"hoverformat":".2f"},"yaxis":{"type":"linear","autorange":false,"tickmode":"array","range":[-41.1,885.1],"ticktext":["0","200","400","600","800"],"tickvals":[0,200,400,600,800],"ticks":"outside","tickcolor":"rgba(179,179,179,1)","ticklen":3.98505603985056,"tickwidth":0.33208800332088,"showticklabels":true,"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":12.7521793275218},"tickangle":-0,"showline":false,"linecolor":null,"linewidth":0,"showgrid":true,"domain":[0,1],"gridcolor":"rgba(217,217,217,1)","gridwidth":0.33208800332088,"zeroline":false,"anchor":"x","title":"Cumulative number of responses","titlefont":{"color":"rgba(0,0,0,1)","family":"","size":15.9402241594022},"hoverformat":".2f"},"shapes":[{"type":"rect","fillcolor":"transparent","line":{"color":"rgba(179,179,179,1)","width":0.66417600664176,"linetype":"solid"},"yref":"paper","xref":"paper","x0":0,"x1":1,"y0":0,"y1":1}],"showlegend":true,"legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":12.7521793275218},"y":1},"hovermode":"closest"},"source":"A","config":{"modeBarButtonsToRemove":["sendDataToCloud"]},"base_url":"https://plot.ly"},"evals":[],"jsHooks":[]}</script>
```

### 2023-05-16 notebook/survey-static.qmd
Add all files related to original survey

--- 2023-05-16 notebook/survey-questions.qmd
@@
 ---
-title: "Survey questions"
+title: "Static survey"
 ---
@@
 
-:   Dropdown menu with [country names from the World Bank](/project/diss-ingos-in-autocracies/survey-countries/).
-
-    Though dropdown menus are poor UI, [adding an autocomplete field to Qualtrics is doable](/project/diss-ingos-in-autocracies/survey-notes/), but tricky and won't always work consistently (e.g.
-if a respondent disables JavaScript, validating their response nearly impossible since they'll have to type the name of the country in blindly—and perfectly—to make it match the validating regex).
+:   Dropdown menu with [country names from the World Bank](/notebook/survey-countries.qmd).
 
@@
 :   Checkboxes with multiple answers allowed; each country is an option
-
-    Horrible nasty UX here, but ¯\\\_(ツ)\_/¯. There's no good way to do this in Qualtrics
 
@@
 
-Enable "Loop and merge" for this block. Respondents can fill out this section as many times as they want for each of the countries they work in.
-
-[Qualtrics' solution for complicated looping and merging is pretty kludgy](https://support.qualtrics.com/survey-platform/edit-survey/block-options/loop-and-merge#LoopingBasedOnAYesNo).
-Respondents can repeat this block up to 5 times (regardless of how many countries they work in).
-The final question of this block, Q4.24, lets respondents either restart the block or continue to the next block.
-
-In order to end the cycle of loops early, **each question in this block** needs to have display logic hiding itself if the respondent chooses to end the loop:
-
-![Display logic for every question in the looped block](/files/images/survey-loop-display-logic.png){.pure-img-responsive}
-
-It's a mess, but it works.
+Respondents can fill out this section as many times as they want for each of the countries they work in.
 
@@
 
-:   Matrix table
+:   Qualtrics side-by-side table
 
@@
 
-    |                                                     | A great deal | A lot | A moderate amount | A little | Not at all | Don't know | Not applicable |
-    | --------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :--------: | :--------: | :------------: |
-    | Regulations regarding registration                  |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-    | Regulations regarding operations                    |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-    | Regulations regarding speech and advocacy           |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-    | Regulations regarding communication and cooperation |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-    | Regulations regarding assembly                      |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-    | Regulations regarding resources                     |      •       |   •   |         •         |    •     |     •      |     •      |       •        |
-
----
-
-*Q4.16a*: Please describe how your organization is affected by regulations regarding registration.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
-
-*Q4.16b*: Please describe how your organization is affected by regulations regarding operations.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
-
-*Q4.16c*: Please describe how your organization is affected by regulations regarding speech and advocacy.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
-
-*Q4.16d*: Please describe how your organization is affected by regulations regarding communication and cooperation.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
-
-*Q4.16e*: Please describe how your organization is affected by regulations regarding assembly.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
-
-*Q4.16f*: Please describe how your organization is affected by regulations regarding resources.
-
-:   Multiline text field
-
-    Only display if corresponding response in Q4.16 is "A great deal", "A lot", "A moderate amount", or "A little"
+    |                                                     | A great deal | A lot | A moderate amount | A little | Not at all | Don't know | Not applicable | Please explain briefly |
+    | --------------------------------------------------- | :----------: | :---: | :---------------: | :------: | :--------: | :--------: | :------------: | :--------------------: |
+    | Regulations regarding registration                  |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
+    | Regulations regarding operations                    |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
+    | Regulations regarding speech and advocacy           |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
+    | Regulations regarding communication and cooperation |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
+    | Regulations regarding assembly                      |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
+    | Regulations regarding resources                     |      •       |   •   |         •         |    •     |     •      |     •      |       •        |       Text field       |
 
@@
 
-:   Matrix table
+:   Qualtrics side-by-side table
 
-    |                                                   | Yes |  No | Don’t know | Not applicable |
-    | ------------------------------------------------- | :-: | :-: | :--------: | :------------: |
-    | We changed the sources of our funding             |  •  |  •  |     •      |       •        |
-    | We changed which issues we work on                |  •  |  •  |     •      |       •        |
-    | We changed how we communicate with the government |  •  |  •  |     •      |       •        |
-    | We changed how we communicate with our donors     |  •  |  •  |     •      |       •        |
-    | We changed which locations we work in             |  •  |  •  |     •      |       •        |
-    | We changed the location of our country office     |  •  |  •  |     •      |       •        |
-    | We used more local staff and/or volunteers        |  •  |  •  |     •      |       •        |
-    | We used more foreign staff and/or volunteers      |  •  |  •  |     •      |       •        |
-
----
-
-*Q4.21a*: Please describe how your organization changed its funding sources. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21b*: Please describe how your organization changed which issues it works on. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21c*: Please describe how your organization changed how it communicates with the government. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21d*: Please describe how your organization changed how it communicates with donors. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21e*: Please describe how your organization changed the locations it works in. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21f*: Please describe how your organization changed the location of its country office. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21g*: Please describe how your organization used more local staff or volunteers. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
-
-*Q4.21h*: Please describe how your organization used more foreign staff or volunteers. What regulation were you responding to?
-
-:   Multiline text field
-
-    Display if corresponding answer in Q4.21 is "Yes"
+    |                                                   | Yes |  No | Don’t know | Not applicable | Please explain briefly |
+    | ------------------------------------------------- | :-: | :-: | :--------: | :------------: | :--------------------: |
+    | We changed the sources of our funding             |  •  |  •  |     •      |       •        |       Text field       |
+    | We changed which issues we work on                |  •  |  •  |     •      |       •        |       Text field       |
+    | We changed how we communicate with the government |  •  |  •  |     •      |       •        |       Text field       |
+    | We changed how we communicate with our donors     |  •  |  •  |     •      |       •        |       Text field       |
+    | We changed which locations we work in             |  •  |  •  |     •      |       •        |       Text field       |
+    | We changed the location of our country office     |  •  |  •  |     •      |       •        |       Text field       |
+    | We used more local staff and/or volunteers        |  •  |  •  |     •      |       •        |       Text field       |
+    | We used more foreign staff and/or volunteers      |  •  |  •  |     •      |       •        |       Text field       |
 
@@
 
-*Q4.24*: That's all I need to know about your organization's work in `target_country`.<br><br>You can either answer the same set of questions for another country your organization works in (this would be helpful) or move on to the survey's final questions.
+*Q4.24*: That's all I need to know about your organization's work in `target_country`.
+You can either answer the same set of questions for another country your organization works in (this would be helpful) or move on to the survey's final questions.
 
@@
 *Q7.1*: This survey is only concerned with international NGOs, or NGOs that work in countries other than the ones they are based in.
-Based on your responses, your organization only works in `home_country`, indicating that you are not an international NGO.<br><br>If this is a mistake and your organization does work abroad, click here to restart the survey.
-Otherwise, click on the forward arrow below to end the survey.<br><br>Thanks for your time!
+Based on your responses, your organization only works in `home_country`, indicating that you are not an international NGO.
+If this is a mistake and your organization does work abroad, click here to restart the survey. Otherwise, click on the forward arrow below to end the survey.  
+Thanks for your time!
 

### 2023-05-16 notebook/survey-technical-details.qmd
Add all files related to original survey

---
title: "Survey technical details"
---

Sending out invitations to ≈30,000 e-mail addresses—many of which are dead and defunct—is tricky. That's a high volume of e-mail and having too many bounces runs the risk of blacklisting my domain.

I used a combination of a custom domain + ~~SendGrid~~ Mailgun + Zoho + fancy branding + Litmus to send out a lot of e-mail, maintain a good sending reputation, and hopefully boost response rates.

Here's what I did.

# Custom domain

I debated whether to send all the e-mails using my .edu e-mail address or something else. Using the .edu address has a built-in psychological benefit—messages probably look more legitimate and research based than blah@gmail.com. However, sending out such a high volume of e-mail from Duke's server is hard/impossible, as I discovered when running a survey of human trafficking NGOs in 2013. I also didn't want to flood my inbox with bounce notifications and survey responses.

Rather than make a Gmail account, which doesn't look as professional, I purchased the [ingoresearch.org](https://www.ingoresearch.org/) domain and created a survey@ingoresearch.org account. It used to be possible to use Google Apps for e-mail on custom domains, but they stopped offering that service in 2012. Instead, I used [Zoho](https://www.zoho.com/), which offers similar services.

- [Generic DNS settings for MX records](https://www.zoho.com/mail/help/adminconsole/configure-email-delivery.html)
- [SPF record](https://www.zoho.com/mail/help/adminconsole/spf-configuration.html)
- [DomainKey/DKIM public key](https://www.zoho.com/mail/help/adminconsole/domain-keys-configuration.html)

# SendGrid

I ran the human trafficking NGO survey using Excel (for tracking e-mails and responses), Word (for mail merge), and Outlook (for sending mail through my adviser's account). That survey only went out to ≈1,500 NGOs, and it was a technical nightmare.

So I did what all the cool kids do and used an e-mail delivery service. [GitHub's educational pack](https://education.github.com/pack) included a free student plan for [SendGrid](https://sendgrid.com/), so I made an account there and played around with it.

SendGrid is awesome.

Their API is powerful and lets you send lots of e-mail quickly. The [Python wrapper for the API](https://github.com/sendgrid/sendgrid-python) is easy to use and intuitive ([see?](https://github.com/andrewheiss/Dissertation/blob/master/Data/Survey/send_mail.py)). They have a nice templating engine and analytic and tracking features. Note to self: use SendGrid for all future survey administration.

To boost its reputation, I [whitelabeled](https://sendgrid.com/docs/User_Guide/Settings/Whitelabel/index.html) the ingoresearch.org domain and all outgoing links. Despite all this DNS whitelabeling, my reputation took a huge hit after the first round of 2,000 e-mails, likely because there were so many bounces (i.e. it dropped from 100% to 76% (!)). I also enabled [List-Unsubscribe](https://support.sendgrid.com/hc/en-us/articles/204379093-How-do-I-add-a-list-unsubscribe-header-to-my-emails-) in the SendGrid settings.

My [SendGrid reputation](https://sendgrid.com/docs/Classroom/Deliver/Address_Lists/list_scrubbing_guide.html) dropped below 75% after sending ≈8,000 e-mails, and my account was permanently suspended. Right before this happened (spurred on by fears that something like this would happen), I caved and spent $100 to clean and scrub my list of e-mails using [Email Hippo](https://www.emailhippo.com/en-US), which categorized e-mails as "Ok", "Unverifiable", and "Bad." Roughly 30% of the e-mail addresses I submitted were bad and would have bounced immediately, so I removed them. About 25% were unverifiable, and 45% were clean.

After getting kicked off of SendGrid, I switched to [Mailgun](https://mailgun.com), which offers similar services ([and is cheaper!](https://www.mailgun.com/pricing)). I started sending invitations to all unverifiable and clean addresses, assuming that "unverifiable" just meant that Email Hippo temporarily couldn't ping the address and that it was really okay. E-mails initially went really well, with only 12% of the messages getting dropped, and 4.8% bouncing. However, even though I thought this was great and low, Mailgun did not and I received a warning message that my account was on the verge of suspension.

I removed all the unverifiable addresses and sent invitations only to clean organizations, which was magic—I got a bounce rate of ≈1.5%, which lowered my account's overall bounce rate to 2.7% and delivery rate to 94%. I need to scrub the list of unverifiable addresses one last time to weed out any organizations that were temporarily unavailable from the organizations that are actually dead.

[MailTester.com](https://www.mail-tester.com) is incredibly useful for checking for issues with e-mails. For instance, it found that my e-mails were incredibly heavy, since the HTML template was heavily commented. I minified the CSS to resolve that issue.

All survey invitations come from survey@ingoresearch.org and all bounces are forwarded to bounces@ingoresearch.org.

I [randomly assigned each e-mail address](https://github.com/andrewheiss/Dissertation/blob/master/Data/Survey/master_ingo_list.R) to a group of roughly 1,000 organizations and ran the sending script on each group.

# Branding

Finally, based on previous research and experiences in big online surveys [@Buthe:2011; @EdwardsRobertsClarke:2009; @HeissKelley:2016], I created a simple unified brand for the survey (mostly just a logo and color scheme.)

I used two Creative Commons-licensed images from The Noun Project ([World, by Shmidt Sergey](https://thenounproject.com/term/world/149710/); and [World, by Dalpat Prajapati](https://thenounproject.com/term/world/64588/)). The UN has a set of unified visual icons in the public domain, but [the one for NGOs is kind of uninspiring](https://thenounproject.com/term/ngo-office/4403/).

## Fonts

- [Source Sans Pro](https://github.com/adobe-fonts/source-sans-pro) Light, Semibold, and Black

## Colors

- <span style="padding: 0.2em; background-color: #00529b; color: #ffffff;">Blue</span>: `#00529b`
- <span style="padding: 0.2em; background-color: #FF6719; color: #ffffff;">Orange</span>: `#FF6719`

## Full logo

![](img/ingo-survey-logo-big.png){width=80%}

## Small logo

![](img/ingo-survey-logo.png){width=200}

## E-mail template

[HTML e-mail templates](http://webdesign.tutsplus.com/tutorials/what-you-should-know-about-html-email--webdesign-12908) are a [massive pain](http://genius.com/7982100). I used [Litmus](https://litmus.com/) to (1) adapt a pre-built template styled off of MailChimp's default template and (2) preview it in different e-mail programs. I discovered [Foundation for Emails](http://foundation.zurb.com/emails.html) after I had already made and tested the template—next time I do this, I'll use their templating system first.

[View all the e-mail invitations.](/project/diss-ingos-in-autocracies/survey-invitations/)

![](img/ingo-survey-email.png)

# UX issues

Huge dropdown menus are a big UX problem, but smart people have invented [the ideal autocomplete country selector](http://baymard.com/labs/country-selector).

However, Qualtrics doesn't allow for complex forms with `data-alternative-spellings` and other custom attributes, so I can't use that cool system. I can use [generic jQuery UI autocomplete functions, though, and include a list of countries in Javascript](https://stackoverflow.com/questions/28952275/unsolved-adding-autocomplete-with-javascript-to-qualtrics).

In the header for the overall survey (under "Look and Feel"), add this:

```html
<script src="https://ajax.googleapis.com/ajax/libs/jquery/1.11.2/jquery.min.js"></script>
<script src="https://ajax.googleapis.com/ajax/libs/jquery/2.1.3/jquery.min.js"></script>
<script src="https://ajax.googleapis.com/ajax/libs/jquerymobile/1.4.5/jquery.mobile.min.js"></script>
<script src="https://ajax.googleapis.com/ajax/libs/jqueryui/1.11.3/jquery-ui.min.js"></script>
<script>
var $j = jQuery.noConflict();  
</script>
```

Then in the question itself, remove the `Qualtrics.SurveyEngine.addOnload(function()` and add:

```javascript
$j(function() {
    var availableTags = [
        "Afghanistan",
        "Albania",
        "Algeria",
        "..."
    ];
    $j( ".InputText" ).autocomplete({
        source: availableTags
    });
});
```

*[Get the full list of countries here](/notebook/survey-countries.qmd)*

Finally, the submenu needs some styling. Add this through the "Look and Feel" section:

```css
.ui-autocomplete {
    font-family: Roboto, "Helvetica Neue", Arial, sans-serif;
    padding: 0;
    list-style: none;
    background-color: #fff;
    width: 218px;
    border: 1px solid #B0BECA;
    max-height: 350px;
    overflow-x: hidden;
}

.ui-autocomplete .ui-menu-item {
    border-top: 1px solid #B0BECA;
    display: block;
    padding: 4px 6px;
    color: #353D44;
    cursor: pointer;
}

.ui-autocomplete .ui-menu-item:first-child {
    border-top: none;
}

.ui-autocomplete .ui-menu-item.ui-state-focus {
    background-color: #D5E5F4;
    color: #161A1C;
}
```

# References

### 2023-05-17 R/funs_analysis.R
Specify stats::binomial so that the mysterious warnings go away
targets was creating so many "<anonymous>: link ‘identity’ not available for ‘binomial’" and it's a mystery why

Using stats::binomial() fixes it though :shrug:

See https://github.com/ropensci/targets/discussions/1075

@@ -87,7 +87,7 @@ make_activities_models <- function(x) {
   initial_model <- brm(
     bf(num | trials(total) ~ 0 + Intercept), 
     data = list(num = 5, total = 5),
-    family = binomial(link = "identity"),
+    family = stats::binomial(link = "identity"),
     prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
     chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
   )
@@ -147,7 +147,7 @@ make_govt_positivity_regime_models <- function(x) {
   model <- brm(
     bf(num | trials(total) ~ 0 + Q4.11_collapsed),
     data = df_govt_positivity_regime_collapsed,
-    family = binomial(link = "identity"),
+    family = stats::binomial(link = "identity"),
     prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
     chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
   )
@@ -180,7 +180,7 @@ make_govt_positivity_issue_models <- function(x) {
   model <- brm(
     bf(num | trials(total) ~ 0 + Q4.11_collapsed),
     data = df_govt_positivity_issue_collapsed,
-    family = binomial(link = "identity"),
+    family = stats::binomial(link = "identity"),
     prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
     chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
   )

### 2023-05-18 notebook/desc-governments.qmd
Finish government relations section

@@
 tar_load(c(survey_orgs, survey_countries, survey_all))
-tar_load(c(df_govt_positivity_regime, models_govt_positivity_regime,
-           df_govt_positivity_issue, models_govt_positivity_issue))
+tar_load(c(
+  df_govt_positivity_regime, models_govt_positivity_regime,
+  df_govt_positivity_issue, models_govt_positivity_issue,
+  df_familiarity_regime, models_familiarity_regime,
+  df_familiarity_issue, models_familiarity_issue,
+  df_frequency_regime, models_frequency_regime,
+  df_registration_regime, models_registration_regime,
+  df_registration_issue, models_registration_issue
+))
 
@@
   labs(x = "Posterior proportion", y = "Relationship with target country") +
+  facet_wrap(vars("INGOs working in autocracies")) +
   theme_ingo()
@@
   mutate(Q4.11_collapsed = as.character(Q4.11_collapsed),
-         type = "Median proportions for NGOs working in autocracies") %>%
+         type = "Median proportions for INGOs working in autocracies") %>%
   rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
@@
   labs(x = "Posterior proportion", y = "Relationship with target country") +
+  facet_wrap(vars("INGOs with contentious issues")) +
   theme_ingo()
@@
 
+### Regime type
+
+```{r plot-familiarity-regime, warning=FALSE}
+ggplot(data = df_familiarity_regime) +
+  geom_mosaic(
+    aes(
+      x = product(target.regime.type, Q4.13_collapsed),
+      fill = target.regime.type
+    ),
+    divider = mosaic("v"),
+    offset = 0, color = "white", linewidth = 1
+  ) +
+  scale_fill_manual(
+    values = c(clrs$Prism[4], clrs$Prism[6]),
+    guide = "none"
+  ) +
+  labs(
+    x = "Target country regime type",
+    y = "Familiarity with regulations"
+  ) +
+  theme_ingo() +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    plot.title = element_markdown(lineheight = 1.2)
+  )
+```
+
+```{r plot-familiarity-regime-bayes, fig.height=4}
+p1 <- models_familiarity_regime$draws %>%
+  ggplot(aes(x = .epred, y = Q4.13_collapsed, fill = Q4.13_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(
+    values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+    guide = "none"
+  ) +
+  labs(x = "Posterior proportion", y = "Familiarity with regulations") +
+  facet_wrap(vars("INGOs working in autocracies")) +
+  theme_ingo()
+
+plot_data <- models_familiarity_regime$diffs %>%
+  mutate(diffs = factor(Q4.13_collapsed,
+    levels = c(
+      "Not familiar at all - Somewhat familiar",
+      "Somewhat familiar - Very familiar",
+      "Not familiar at all - Very familiar"
+    )
+  ))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- models_familiarity_regime$diffs %>% 
+  mutate(diffs = factor(Q4.13_collapsed,
+    levels = c(
+      "Not familiar at all - Somewhat familiar",
+      "Somewhat familiar - Very familiar",
+      "Not familiar at all - Very familiar"
+    )
+  )) %>%  
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp."),
+                     breaks = seq(-0.6, 0.2, by = 0.2)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-familiarity-regime-bayes}
+models_familiarity_regime$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.13_collapsed = as.character(Q4.13_collapsed),
+         type = "Median proportions for INGOs working in autocracies") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_familiarity_regime$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.13_collapsed = str_replace(Q4.13_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.13_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.13_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+### Issue contentiousness
+
+```{r plot-familiarity-issue, warning=FALSE}
+ggplot(data = df_familiarity_issue) +
+  geom_mosaic(aes(x = product(potential.contentiousness, Q4.13_collapsed), 
+                  fill = potential.contentiousness),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]),
+                    guide = "none") +
+  labs(x = "Contentiousness of INGO work",
+       y = "Familiarity with regulations") +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-familiarity-issue-bayes, fig.height=4}
+p1 <- models_familiarity_issue$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.13_collapsed, fill = Q4.13_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Familiarity with regulations") +
+  facet_wrap(vars("INGOs with contentious issues")) +
+  theme_ingo()
+
+plot_data <- models_familiarity_issue$diffs %>% 
+  mutate(diffs = factor(Q4.13_collapsed,
+    levels = c(
+      "Not familiar at all - Somewhat familiar",
+      "Somewhat familiar - Very familiar",
+      "Not familiar at all - Very familiar"
+    )
+  ))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- plot_data %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    # aes(y = after_stat(density * 1e5)),
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = "\n pp."),
+                     breaks = seq(-0.4, 0.1, by = 0.1)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-familiarity-issue-bayes}
+models_familiarity_issue$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.13_collapsed = as.character(Q4.13_collapsed),
+         type = "Median proportions for NGOs working on contentious issues") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_familiarity_issue$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.13_collapsed = str_replace(Q4.13_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.13_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.13_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
 ## Frequency of changes
+
+```{r plot-frequency-regime, warning=FALSE}
+ggplot(data = df_frequency_regime) +
+  geom_mosaic(
+    aes(
+      x = product(target.regime.type, Q4.14_collapsed),
+      fill = target.regime.type
+    ),
+    divider = mosaic("v"),
+    offset = 0, color = "white", linewidth = 1
+  ) +
+  scale_fill_manual(
+    values = c(clrs$Prism[4], clrs$Prism[6]),
+    guide = "none"
+  ) +
+  labs(
+    x = "Target country regime type",
+    y = "Frequency of changes in regulations"
+  ) +
+  theme_ingo() +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    plot.title = element_markdown(lineheight = 1.2)
+  )
+```
+
+```{r plot-frequency-regime-bayes, fig.height=4}
+p1 <- models_frequency_regime$draws %>%
+  ggplot(aes(x = .epred, y = Q4.14_collapsed, fill = Q4.14_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(
+    values = c(clrs$Prism[7], clrs$Prism[12], clrs$Prism[2]),
+    guide = "none"
+  ) +
+  labs(x = "Posterior proportion", y = "Frequency of changes in regulations") +
+  facet_wrap(vars("INGOs working in autocracies")) +
+  theme_ingo()
+
+plot_data <- models_frequency_regime$diffs %>%
+  mutate(diffs = factor(Q4.14_collapsed,
+    levels = c(
+      "Rarely or never - Once every few years",
+      "Once every few years - At least once a year",
+      "Rarely or never - At least once a year"
+    )
+  ))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- models_frequency_regime$diffs %>% 
+  mutate(diffs = factor(Q4.14_collapsed,
+    levels = c(
+      "Rarely or never - Once every few years",
+      "Once every few years - At least once a year",
+      "Rarely or never - At least once a year"
+    )
+  )) %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[12], clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[12], clrs$Prism[7], clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp."),
+                     breaks = seq(-0.6, 0.2, by = 0.2)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-frequency-regime-bayes}
+models_frequency_regime$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.14_collapsed = as.character(Q4.14_collapsed),
+         type = "Median proportions for INGOs working in autocracies") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_frequency_regime$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.14_collapsed = str_replace(Q4.14_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.14_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.14_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
 
@@
 
+```{r plot-change-how, fig.width=6, fig.height=2}
+df_change_how <- survey_countries %>%
+  unnest(Q4.15_value) %>%
+  group_by(Q4.15_value) %>%
+  summarise(num = n()) %>%
+  arrange(desc(num)) %>%
+  filter(!is.na(Q4.15_value)) %>%
+  mutate(how = fct_inorder(Q4.15_value)) %>%
+  mutate(how = fct_recode(how,
+    "Newspapers, television,\nand other media" = "Newspapers, television, and other media", 
+    NULL = "Don't know"
+  )) %>%
+  filter(!is.na(how))
+
+ggplot(df_change_how, aes(x = num, y = fct_rev(how))) +
+  geom_pointrange(aes(xmin = 0, xmax = num)) +
+  scale_x_continuous(
+    sec.axis = sec_axis(~ . / nrow(survey_countries),
+    labels = label_percent()
+  )) +
+  labs(x = "Times selected", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank())
+
+# What are the other ways?
+df_change_how_other <- survey_countries %>%
+  filter(!is.na(Q4.15_other_TEXT)) %>%
+  select(clean.id, Q4.15_other_TEXT) %>%
+  arrange(Q4.15_other_TEXT)
+```
+
 ## Are NGOs registered?
+
+### Regime type
+
+```{r plot-registration-regime, warning=FALSE}
+ggplot(data = df_registration_regime) +
+  geom_mosaic(
+    aes(
+      x = product(target.regime.type, Q4.4_collapsed),
+      fill = target.regime.type
+    ),
+    divider = mosaic("v"),
+    offset = 0, color = "white", linewidth = 1
+  ) +
+  scale_fill_manual(
+    values = c(clrs$Prism[4], clrs$Prism[6]),
+    guide = "none"
+  ) +
+  labs(
+    x = "Target country regime type",
+    y = "Registration status"
+  ) +
+  theme_ingo() +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    plot.title = element_markdown(lineheight = 1.2)
+  )
+```
+
+```{r plot-registration-regime-bayes, fig.height=4}
+p1 <- models_registration_regime$draws %>%
+  ggplot(aes(x = .epred, y = Q4.4_collapsed, fill = Q4.4_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(
+    values = c(clrs$Prism[7], clrs$Prism[2]),
+    guide = "none"
+  ) +
+  labs(x = "Posterior proportion", y = "Registration status") +
+  facet_wrap(vars("INGOs working in autocracies")) +
+  theme_ingo()
+
+plot_data <- models_registration_regime$diffs %>%
+  mutate(diffs = factor(Q4.4_collapsed))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- models_registration_regime$diffs %>% 
+  mutate(diffs = factor(Q4.4_collapsed)) %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp."),
+                     breaks = seq(-0.4, 0.4, by = 0.1)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-registration-regime-bayes}
+models_registration_regime$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.4_collapsed = as.character(Q4.4_collapsed),
+         type = "Median proportions for INGOs working in autocracies") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_registration_regime$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.4_collapsed = str_replace(Q4.4_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.4_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.4_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+### Issue contentiousness
+
+```{r plot-registration-issue, warning=FALSE}
+ggplot(data = df_registration_issue) +
+  geom_mosaic(aes(x = product(potential.contentiousness, Q4.4_collapsed), 
+                  fill = potential.contentiousness),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]),
+                    guide = "none") +
+  labs(x = "Contentiousness of INGO work",
+       y = "Registration status") +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-registration-issue-bayes, fig.height=4}
+p1 <- models_registration_issue$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.4_collapsed, fill = Q4.4_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = c(clrs$Prism[7], clrs$Prism[2]),
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Registration status") +
+  facet_wrap(vars("INGOs with contentious issues")) +
+  theme_ingo()
+
+plot_data <- models_registration_issue$diffs %>% 
+  mutate(diffs = factor(Q4.4_collapsed))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- plot_data %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    # aes(y = after_stat(density * 1e5)),
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Prism[7]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = "\n pp."),
+                     breaks = seq(-0.4, 0.1, by = 0.1)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-registration-issue-bayes}
+models_registration_issue$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.4_collapsed = as.character(Q4.4_collapsed),
+         type = "Median proportions for NGOs working on contentious issues") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_registration_issue$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.4_collapsed = str_replace(Q4.4_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.4_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.4_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
 
@@
 ## Contact and reporting frequency
+
+```{r plot-report-frequency}
+df_freq_report <- survey_all %>%
+  mutate(Q4.8.collapsed = fct_recode(Q4.8.clean,
+    `More than once a year` = "More than once a week",
+    `More than once a year` = "Once a week",
+    `More than once a year` = "More than once a month,\nless than once a week",
+    `More than once a year` = "Once a month",
+    `More than once a year` = "More than once a year,\nless than once a month",
+    `Annually` = "Once a year",
+    `Once every 2+ years` = "Once every 2+ years",
+    `Never` = "Rarely",
+    `Never` = "Never",
+    `As necessary` = "As necessary/depends",
+    NULL = "Don't know"
+  )) %>%
+  mutate(Q4.8.collapsed = fct_relevel(Q4.8.collapsed, "As necessary", after = 1)) %>%
+  filter(!is.na(Q4.8.collapsed)) %>%
+  group_by(target.regime.type, Q4.8.collapsed) %>%
+  summarise(num = n()) %>%
+  rename(freq = Q4.8.collapsed)
+```
+
+```{r plot-contact-frequency}
+df_freq_contact <- survey_all %>%
+  mutate(Q4.5.collapsed = fct_recode(Q4.5.clean,
+    `More than once a year` = "More than once a week",
+    `More than once a year` = "Once a week",
+    `More than once a year` = "More than once a month,\nless than once a week",
+    `More than once a year` = "Once a month",
+    `More than once a year` = "More than once a year,\nless than once a month",
+    `Annually` = "Once a year",
+    `Once every 2+ years` = "Once every 2+ years",
+    `Never` = "Rarely",
+    `Never` = "Never",
+    `As necessary` = "As necessary/depends",
+    NULL = "Don't know"
+  )) %>%
+  mutate(Q4.5.collapsed = fct_relevel(Q4.5.collapsed, "As necessary", after = 1)) %>%
+  filter(!is.na(Q4.5.collapsed)) %>%
+  group_by(target.regime.type, Q4.5.collapsed) %>%
+  summarise(num = n()) %>%
+  rename(freq = Q4.5.collapsed)
+```
+
+```{r plot-freq-govt-both, fig.width=6, fig.height=3}
+df_freq_both <- bind_rows(
+  df_freq_contact,
+  df_freq_report,
+  .id = "report.type"
+) %>%
+  mutate(report.type = recode(
+    report.type,
+    `1` = "Contact with the government",
+    `2` = "Reporting to the government"
+  ))
+
+ggplot(
+  df_freq_both,
+  aes(
+    x = num, y = freq,
+    colour = target.regime.type
+  )
+) +
+  geom_pointrange(
+    aes(xmin = 0, xmax = num),
+    position = position_dodge(width = 0.5),
+    size = 0.5
+  ) +
+  scale_colour_manual(
+    values = c(clrs$Prism[4], clrs$Prism[6]), name = NULL
+  ) +
+  guides(colour = guide_legend(reverse = TRUE)) +
+  labs(x = "Number of responses", y = NULL) +
+  facet_wrap(vars(report.type)) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank())
+```
+
+```{r plot-officials-contact, fig.width=6, fig.height=3}
+df_officials_contact_most <- survey_all %>%
+  group_by(Q4.7) %>%
+  summarise(num = n()) %>%
+  arrange(desc(num)) %>%
+  filter(!is.na(Q4.7)) %>%
+  mutate(issue = factor(Q4.7, levels = rev(Q4.7), ordered = TRUE))
+
+ggplot(
+  df_officials_contact_most,
+  aes(x = num, y = issue)
+) +
+  geom_pointrange(aes(xmin = 0, xmax = num)) +
+  labs(x = "Times selected", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank())
+```

### 2023-05-18 R/funs_analysis.R

@@ -192,3 +192,168 @@ make_govt_positivity_issue_models <- function(x) {
   return(lst(data = df_govt_positivity_issue_collapsed, 
              model, draws, diffs, diffs_summary))
 }
+
+make_familiarity_regime <- function(x) {
+  df_familiarity_regime <- x %>%
+    select(Q4.13_collapsed, target.regime.type) %>%
+    filter(!is.na(Q4.13_collapsed), Q4.13_collapsed != "NULL") %>% 
+    mutate(Q4.13_collapsed = fct_drop(Q4.13_collapsed))
+  
+  return(df_familiarity_regime)
+}
+
+make_familiarity_regime_models <- function(x) {
+  df_familiarity_regime_collapsed <- x %>% 
+    group_by(Q4.13_collapsed, target.regime.type) %>%
+    summarize(num = n()) %>% 
+    group_by(Q4.13_collapsed) %>%
+    mutate(total = sum(num)) %>% 
+    filter(target.regime.type == "Autocracy")
+  
+  model <- brm(
+    bf(num | trials(total) ~ 0 + Q4.13_collapsed),
+    data = df_familiarity_regime_collapsed,
+    family = stats::binomial(link = "identity"),
+    prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
+  )
+  
+  draws <- extract_posterior_draws(model, prop = TRUE)
+  diffs <- extract_diffs(model, prop = TRUE)
+  diffs_summary <- extract_diffs_summary(diffs)
+  
+  return(lst(data = df_familiarity_regime_collapsed, 
+             model, draws, diffs, diffs_summary))
+}
+
+make_familiarity_issue <- function(x) {
+  df_familiarity_issue <- x %>%
+    select(Q4.13_collapsed, potential.contentiousness) %>%
+    filter(!is.na(Q4.13_collapsed), Q4.13_collapsed != "NULL") %>% 
+    mutate(Q4.13_collapsed = fct_drop(Q4.13_collapsed))
+  
+  return(df_familiarity_issue)
+}
+
+make_familiarity_issue_models <- function(x) {
+  df_familiarity_issue_collapsed <- x %>% 
+    group_by(Q4.13_collapsed, potential.contentiousness) %>%
+    summarize(num = n()) %>% 
+    group_by(Q4.13_collapsed) %>%
[…]

### 2023-05-18 _targets.R

@@ -8,28 +8,35 @@ library(tibble)
 # This hardcodes the absolute path in _targets.yaml, so to make this more
 # portable, we rewrite it every time this pipeline is run (and we don't track
 # _targets.yaml with git)
-tar_config_set(store = here::here('_targets'),
-               script = here::here('_targets.R'))
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
 
-options(tidyverse.quiet = TRUE,
-        dplyr.summarise.inform = FALSE,
-        # Treat ordered factors as treatments in models
-        contrasts = rep("contr.treatment", 2))
+options(
+  tidyverse.quiet = TRUE,
+  dplyr.summarise.inform = FALSE,
+  contrasts = rep("contr.treatment", 2)  # Treat ordered factors as treatments in models
+)
 
-set.seed(71215)  # From random.org
+set.seed(71215) # From random.org
 
 # Bayesian stuff
 suppressPackageStartupMessages(library(brms))
-options(mc.cores = 4,
-        brms.backend = "cmdstanr")
+options(
+  mc.cores = 4,
+  brms.backend = "cmdstanr"
+)
 
-BAYES_SEED <- 907680  # From random.org
+BAYES_SEED <- 907680 # From random.org
 CHAINS <- 4
 ITER <- 2000
 WARMUP <- 1000
 
-tar_option_set(packages = c("tidyverse"),
-               format = "qs")
+tar_option_set(
+  packages = c("tidyverse"),
+  format = "qs"
+)
 
 # here::here() returns an absolute path, which then gets stored in tar_meta and
 # becomes computer-specific (i.e. /Users/andrew/Research/blah/thing.Rmd).
@@ -44,46 +51,92 @@ lapply(list.files("R", full.names = TRUE, recursive = TRUE), source)
 # Actual pipeline ---------------------------------------------------------
 list(
   ## Raw data files ----
-  tar_target(survey_orgs_file, 
-             here_rel("data", "raw-data", "survey_orgs_clean.rds"), 
-             format = "file"),
-  tar_target(survey_countries_file, 
-             here_rel("data", "raw-data", "survey_countries_clean.rds"), 
-             format = "file"),
-  tar_target(survey_all_file, 
-             here_rel("data", "raw-data", "survey_clean_all.rds"), 
-             format = "file"),
+  tar_target(survey_orgs_file,
+    here_rel("data", "raw-data", "survey_orgs_clean.rds"),
[…]

### 2023-05-18 _dependencies.R
Update renv again

@@ -1,0 +1,5 @@
+# Things that need to be installed but didn't get installed automatically as 
+# dependencies for whatever reason
+library(cmdstanr)
+library(quarto)
+library(collapse)

### 2023-12-17 notebook/desc-restrictions.qmd
Split descriptive stuff across multiple qmd files
Start updating restrictions notebook

--- 2023-05-10 notebook/desc-governments.qmd
@@
 ---
-title: "INGOs and governments"
+title: "INGOs and restrictions"
 format:
@@
 ```
+
+```{r load-libraries-data, warning=FALSE, message=FALSE}
+library(tidyverse)
+library(targets)
+library(scales)
+library(glue)
+library(gt)
+library(ggmosaic)
+library(ggtext)
+library(patchwork)
+library(tidybayes)
+library(here)
+library(ggpattern)
+library(countrycode)
+
+tar_config_set(store = here('_targets'),
+               script = here('_targets.R'))
+
+tar_load(c(survey_orgs, survey_countries, survey_all, dcjw, gwf))
+tar_load(c(
+  df_restrictions_regime, models_restrictions_regime,
+  df_restrictions_issue, models_restrictions_issue,
+  df_restrictions_reg_regime, models_restrictions_reg_regime
+))
+
+# Plotting functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+set_annotation_fonts()
+```
+
+# Routine regulation vs. burdensome regulation
+
+```{r plot-dcjw-registration, fig.width=6, fig.height=2, warning=FALSE}
+dcjw_registration <- dcjw %>%
+  mutate(question = recode(question,
+    q_2a = "registration",
+    q_2b = "burdensome",
+    q_2c = "appeal",
+    q_2d = "diff.foreign"
+  )) %>%
+  filter(question %in% c("registration", "burdensome"))
+
+dcjw_registration_panel <- dcjw_registration %>%
+  tidyr::expand(Country, question,
+    year = min(.$year, na.rm = TRUE):2013
+  ) %>%
+  left_join(
+    dcjw_registration,
+    by = c("Country", "question", "year")
+  ) %>%
+  # Bring most recent legislation forward
+  group_by(Country, question) %>%
+  mutate(value = zoo::na.locf(value, na.rm = FALSE)) %>%
+  ungroup() %>%
+  mutate(value = ifelse(is.na(value), 0, value)) %>%
+  mutate(cowcode = countrycode(Country, "country.name", "cown",
+    custom_match = c(`Serbia` = 340L)
+  ))
+
+regime_types <- gwf %>%
+  select(cowcode, year, gwf.ever.autocracy) %>%
+  group_by(cowcode) %>%
+  summarise(ever.autocracy = any(gwf.ever.autocracy, na.rm = TRUE))
+
+dcjw_registration_summary <- dcjw_registration_panel %>%
+  left_join(regime_types, by = "cowcode") %>%
+  # There are a few countries that didn't have regime type from full.data
+  mutate(ever.autocracy = case_when(
+    .$Country %in% c(
+      "Bahrain", "Equatorial Guinea", "Kuwait", "Oman",
+      "Singapore", "United Arab Emirates"
+    ) ~ TRUE,
+    .$Country == "Serbia" ~ FALSE,
+    TRUE ~ .$ever.autocracy
+  )) %>%
+  group_by(year, question, ever.autocracy) %>%
+  summarise(prop.with.reg = sum(value) / n()) %>%
+  ungroup() %>%
+  mutate(
+    question =
+      factor(question,
+        levels = c("registration", "burdensome"),
+        labels = c(
+          "Registration required",
+          "Registration burdensome"
+        )
+      )
+  ) %>%
+  mutate(
+    ever.autocracy =
+      factor(ever.autocracy,
+        levels = c(TRUE, FALSE),
+        labels = c("Autocracies", "Democracies")
+      )
+  ) %>%
+  mutate(ever.autocracy = factor(ever.autocracy,
+    levels = rev(levels(ever.autocracy)),
+    ordered = TRUE
+  )) %>%
+  filter(year > 1990)
+
+ggplot(
+  dcjw_registration_summary,
+  aes(x = year, y = prop.with.reg, colour = ever.autocracy)
+) +
+  geom_line() +
+  labs(x = NULL, y = "Proportion of countries\nwith regulations") +
+  scale_y_continuous(labels = label_percent()) +
+  coord_cartesian(ylim = c(0, 0.65)) +
+  scale_colour_manual(values = c(clrs$Prism[4], clrs$Prism[6]), 
+    name = NULL, na.translate = FALSE) +
+  theme_ingo() +
+  facet_wrap(vars(question))
+```
+
+# Overall restriction
+
+## Regime type
+
+```{r plot-restrictions-regime, warning=FALSE}
+ggplot(data = df_restrictions_regime) +
+  geom_mosaic(aes(x = product(target.regime.type, Q4.17_collapsed), 
+                  fill = target.regime.type),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[4], clrs$Prism[6]),
+                    guide = "none") +
+  labs(x = "Target country regime type",
+       y = "Level of restriction in target country") +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-restrictions-regime-bayes, fig.width=7.5, fig.height=4}
+# Template: 60% of INGOs that reported feeling very restricted work in autocracies
+p1 <- models_restrictions_regime$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.17_collapsed, fill = Q4.17_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$Peach[c(1, 3, 5, 7)],
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Level of restriction in target country") +
+  facet_wrap(vars("Proportion of INGOs that reported level\nof restriction that work in autocracies")) +
+  theme_ingo()
+
+plot_data <- models_restrictions_regime$diffs %>%
+  mutate(diffs = factor(Q4.17_collapsed,
+    levels = c(
+      "Very restricted - Moderately restricted",
+      "Moderately restricted - Slightly restricted",
+      "Slightly restricted - Not restricted"
+    )
+  ))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- models_restrictions_regime$diffs %>% 
+  mutate(diffs = factor(Q4.17_collapsed,
+    levels = c(
+      "Very restricted - Moderately restricted",
+      "Moderately restricted - Slightly restricted",
+      "Slightly restricted - Not restricted"
+    )
+  )) %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Peach[7], clrs$Peach[5], clrs$Peach[3]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Peach[5], clrs$Peach[3], clrs$Peach[1]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = " pp."),
+                     breaks = seq(-0.6, 0.2, by = 0.2)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-restrictions-regime-bayes}
+models_restrictions_regime$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.17_collapsed = as.character(Q4.17_collapsed),
+         type = "Median proportions for INGOs working in autocracies") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_restrictions_regime$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.17_collapsed = str_replace(Q4.17_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.17_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.17_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+## Issue contentiousness
+
+```{r plot-restrictions-issue, warning=FALSE}
+ggplot(data = df_restrictions_issue) +
+  geom_mosaic(aes(x = product(potential.contentiousness, Q4.17_collapsed), 
+                  fill = potential.contentiousness),
+              divider = mosaic("v"), 
+              offset = 0, color = "white", linewidth = 1) +
+  scale_fill_manual(values = c(clrs$Prism[2], clrs$Prism[8]),
+                    guide = "none") +
+  labs(x = "Contentiousness of INGO work",
+       y = "Level of restriction in target country") +
+  theme_ingo() +
+  theme(panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_blank(),
+        plot.title = element_markdown(lineheight = 1.2))
+```
+
+```{r plot-restrictions-issue-bayes, fig.width=7.5, fig.height=4}
+p1 <- models_restrictions_issue$draws %>% 
+  ggplot(aes(x = .epred, y = Q4.17_collapsed, fill = Q4.17_collapsed)) +
+  stat_halfeye() +
+  scale_x_continuous(labels = label_percent()) +
+  scale_fill_manual(values = clrs$Peach[c(1, 3, 5, 7)],
+                    guide = "none") +
+  labs(x = "Posterior proportion", y = "Level of restriction in target country") +
+  facet_wrap(vars("INGOs with contentious issues")) +
+  theme_ingo()
+
+plot_data <- models_restrictions_issue$diffs %>% 
+  mutate(diffs = factor(Q4.17_collapsed,
+    levels = c(
+      "Very restricted - Moderately restricted",
+      "Moderately restricted - Slightly restricted",
+      "Slightly restricted - Not restricted"
+    )
+  ))
+
+diffs_summary <- plot_data %>% 
+  group_by(diffs) %>% 
+  median_qi(.epred, .width = c(0.5, 0.8, 0.95))
+
+p2 <- plot_data %>% 
+  ggplot(aes(x = .epred, fill = diffs, pattern_fill = diffs)) +
+  geom_density_pattern(
+    # aes(y = after_stat(density * 1e5)),
+    pattern = "stripe",
+    pattern_density = 0.5,
+    pattern_spacing = 0.2,
+    pattern_size = 0,
+    trim = TRUE,
+    linewidth = 0
+  ) +
+  geom_pointinterval(data = diffs_summary, aes(x = .epred, xmin = .lower, xmax = .upper)) +
+  geom_vline(xintercept = 0, linewidth = 0.5, color = clrs$Prism[8]) +
+  facet_wrap(vars(diffs), ncol = 1) +
+  scale_fill_manual(values = c(clrs$Peach[7], clrs$Peach[5], clrs$Peach[3]),
+                    guide = "none") +
+  scale_pattern_fill_manual(values = c(clrs$Peach[5], clrs$Peach[3], clrs$Peach[1]),
+                            guide = "none") +
+  scale_x_continuous(labels = label_number(scale = 100, style_negative = "minus",
+                                           suffix = "\n pp."),
+                     breaks = seq(-0.4, 0.4, by = 0.2)) +
+  labs(x = "Percentage point differences", y = NULL) +
+  theme_ingo() +
+  theme(panel.grid.major.y = element_blank(),
+        axis.text.y = element_blank())
+
+p1 | p2
+```
+
+```{r tab-restrictions-issue-bayes}
+models_restrictions_issue$draws %>% 
+  median_qi(.epred) %>% 
+  mutate(Q4.17_collapsed = as.character(Q4.17_collapsed),
+         type = "Median proportions for NGOs working on contentious issues") %>%
+  rename(y = .epred, ymin = .lower, ymax = .upper) %>% 
+  bind_rows(models_restrictions_issue$diffs_summary) %>% 
+  mutate(across(c(y, ymin, ymax, p_greater_0), 
+                list(nice = ~label_number(accuracy = 0.01)(.)))) %>% 
+  mutate(nice_value = glue("{y_nice}<br>({ymin_nice} – {ymax_nice})")) %>% 
+  mutate(Q4.17_collapsed = str_replace(Q4.17_collapsed, " - ", " − ")) %>% 
+  select(type, Q4.17_collapsed, nice_value, p_greater_0_nice) %>% 
+  group_by(type) %>% 
+  gt() %>% 
+  cols_label(
+    Q4.17_collapsed = "",
+    nice_value = "Posterior median",
+    p_greater_0_nice = "p > 0"
+  ) %>% 
+  fmt_markdown(nice_value) %>% 
+  sub_missing(p_greater_0_nice) %>% 
+  tab_footnote(footnote = "95% credible intervals shown in parentheses") %>% 
+  opts_theme()
+```
+
+# Registration and restrictions
+
+```{r plot-registration-restrictions, fig.width=6.5, fig.height=2}
+ggplot(data = df_restrictions_reg_regime) +
+  geom_mosaic(
+    aes(
+      x = product(regime_registered, Q4.17_collapsed),
+      fill = regime_registered
+    ),
+    divider = mosaic("v"),
+    offset = 0, color = "white", linewidth = 1, na.rm = TRUE
+  ) +
+  scale_x_productlist(
+    expand = c(0, 0.02),
+    labels = c("Registered", "", "Not registered", "")) +
+  scale_y_productlist(expand = c(0, 0.02)) +
+  scale_fill_manual(
+    values = c(
+      clrs$Prism[1], clrs$Prism[11],
+      clrs$Prism[7], clrs$Prism[6]
+    ),
+    guide = "none"
+  ) +
+  facet_wrap(vars(target.regime.type), ncol = 2) +
+  theme_ingo() +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
+```
+
+```{r tab-registration-restrictions-diffs}
+#| tbl-cap: Median differences in proportion of registered and non-registered INGOs selecting frequency of type of restriction. Probability that the proportion is greater than 0 given in parentheses.
+models_restrictions_reg_regime %>% 
+  unnest(diffs_summary) %>% 
+  mutate(nice_value = glue::glue(
+    "{diff}<br>({p})",
+    diff = label_number(style_negative = "minus", accuracy = 0.01)(y),
+    p = label_number(accuracy = 0.01)(p_greater_0))
+  ) %>% 
+  ungroup() %>% 
+  select(Q4.17_collapsed, target.regime.type, nice_value) %>% 
+  pivot_wider(names_from = "target.regime.type", values_from = "nice_value") %>% 
+  gt() %>%
+  fmt_markdown(columns = 2:3) %>%
+  cols_align(align = "left", columns = Q4.17_collapsed) %>%
+  cols_label(Q4.17_collapsed = "") %>% 
+  tab_footnote(footnote = "Values show the differences in proportion of registered and non-registered INGOs providing each response (not registered proportion − registered proportion)") %>% 
+  opts_theme()
+```
+
+# Gatekeeping and program capture restrictions
+
+# Reactions to restrictions
+
+## Size
+
+## Other instrumental concerns

### 2023-12-17 R/funs_analysis.R

@@ -19,15 +19,14 @@ extract_posterior_draws <- function(model, prop = FALSE) {
   return(post)
 }
 
-extract_diffs <- function(model, prop = FALSE) {
+extract_diffs <- function(model, prop = FALSE, comparison = "pairwise") {
   post <- extract_posterior_draws(model, prop = prop)
   
   var_name <- labels(terms(as.formula(model$formula)))
 
-  post %>% 
-    ungroup() %>% 
-    compare_levels(.epred, by = var_name,
-                   comparison = "pairwise")
+  post %>%
+    ungroup() %>%
+    compare_levels(.epred, by = var_name, comparison = !!comparison)
 }
 
 extract_diffs_summary <- function(diffs) {
@@ -356,4 +355,114 @@ make_registration_issue_models <- function(x) {
   
   return(lst(data = df_registration_issue_collapsed, 
              model, draws, diffs, diffs_summary))
+}
+
+make_restrictions_regime <- function(x) {
+  df_restrictions_regime <- x %>%
+    select(Q4.17_collapsed, target.regime.type) %>%
+    filter(!is.na(Q4.17_collapsed), Q4.17_collapsed != "NULL") %>% 
+    mutate(Q4.17_collapsed = fct_drop(Q4.17_collapsed))
+  
+  return(df_restrictions_regime)
+}
+
+make_restrictions_regime_models <- function(x) {
+  df_restrictions_regime_collapsed <- x %>% 
+    group_by(Q4.17_collapsed, target.regime.type) %>%
+    summarize(num = n()) %>% 
+    group_by(Q4.17_collapsed) %>%
+    mutate(total = sum(num)) %>% 
+    filter(target.regime.type == "Autocracy")
+  
+  model <- brm(
+    bf(num | trials(total) ~ 0 + Q4.17_collapsed),
+    data = df_restrictions_regime_collapsed,
+    family = stats::binomial(link = "identity"),
+    prior = c(prior(beta(5, 5), class = b, lb = 0, ub = 1)),
+    chains = CHAINS, iter = ITER, warmup = WARMUP, seed = BAYES_SEED, refresh = 0
+  )
+  
+  draws <- extract_posterior_draws(model, prop = TRUE)
+  diffs <- extract_diffs(model, prop = TRUE, comparison = "ordered")
+  diffs_summary <- extract_diffs_summary(diffs)
+  
[…]

### 2023-12-17 R/funs_data.R

@@ -74,3 +74,96 @@ load_world_map <- function(path) {
   
   return(world_map)
 }
+
+clean_dcjw <- function(path) {
+  # This is copied from my older dissertation R code: 
+  # https://github.com/andrewheiss/Dissertation/blob/master/Data/R/clean_merge_data.R#L1044
+  # I didn't really update it to more modern tidyverse R (i.e. it still uses 
+  # gather() and separate())
+  library(readxl)
+  library(countrycode)
+  
+  dcjw <- read_excel(path)[, 1:50] %>%
+    select(-c(
+      dplyr::contains("source"), dplyr::contains("burden"),
+      dplyr::contains("subset"), Coder, Date
+    )) %>%
+    gather(key, value, -Country) %>%
+    separate(key, c("question", "var.name"), 4) %>%
+    filter(!is.na(Country)) %>%
+    mutate(var.name = ifelse(var.name == "", "value", gsub("_", "", var.name))) %>%
+    spread(var.name, value) %>%
+    mutate(
+      year.actual = ymd(paste0(year, "-01-01"), quiet = TRUE),
+      country.name = countrycode(Country, "country.name", "country.name")
+    )
+  
+  return(dcjw)
+}
+
+clean_gwf <- function(path) {
+  # GWF Autocratic regimes
+  # http://sites.psu.edu/dictators/
+  # This is included in V-Dem, but only `gwf_regimetype` and `gwf_nonautocracy`
+  regime.types.simple <- tribble(
+    ~gwf.unified, ~gwf.simple, ~gwf.binary,
+    "democracy", "democracy", "democracy",
+    "provisional", "other", "",
+    "foreign-occupied", "other", "",
+    "warlord", "other", "",
+    "not-independent", "other", "",
+    "warlord/foreign-occupied", "other", "",
+    "personal", "autocracy", "autocracy",
+    "party-personal", "autocracy", "autocracy",
+    "military", "autocracy", "autocracy",
+    "military-personal", "autocracy", "autocracy",
+    "party", "autocracy", "autocracy",
+    "indirect military", "autocracy", "autocracy",
+    "party-military", "autocracy", "autocracy",
+    "oligarchy", "autocracy", "autocracy",
+    "party-military-personal", "autocracy", "autocracy",
+    "monarchy", "autocracy", "autocracy"
+  )
+  
[…]

### 2023-12-17 _targets.R

@@ -70,12 +70,22 @@ list(
     ),
     format = "file"
   ),
+  tar_target(dcjw_file,
+    here_rel("data", "raw-data", "dcjw-ngo-laws", "DCJW_NGO_Laws.xlsx"),
+    format = "file"
+  ),
+  tar_target(gwf_file,
+    here_rel("data", "raw-data", "gwf-autocratic-regimes", "GWF_AllPoliticalRegimes.dta"),
+    format = "file"
+  ),
 
   ## Process and clean data ----
   tar_target(survey_orgs, clean_survey_orgs(survey_orgs_file)),
   tar_target(survey_countries, clean_survey_countries(survey_countries_file)),
   tar_target(survey_all, clean_survey_all(survey_all_file)),
   tar_target(world_map, load_world_map(naturalearth_raw_file)),
+  tar_target(dcjw, clean_dcjw(dcjw_file)),
+  tar_target(gwf, clean_gwf(gwf_file)),
 
   ## Graphics ----
   tar_target(graphic_functions, lst(
@@ -132,6 +142,24 @@ list(
   tar_target(
     models_registration_issue,
     make_registration_issue_models(df_registration_issue)
+  ),
+  
+  tar_target(df_restrictions_regime, make_restrictions_regime(survey_countries)),
+  tar_target(
+    models_restrictions_regime,
+    make_restrictions_regime_models(df_restrictions_regime)
+  ),
+  
+  tar_target(df_restrictions_issue, make_restrictions_issue(survey_countries)),
+  tar_target(
+    models_restrictions_issue,
+    make_restrictions_issue_models(df_restrictions_issue)
+  ),
+  
+  tar_target(df_restrictions_reg_regime, make_restrictions_reg_regime(survey_countries)),
+  tar_target(
+    models_restrictions_reg_regime,
+    make_restrictions_reg_regime_models(df_restrictions_reg_regime)
   ),
 
   # Manuscript and analysis notebook ----

### 2023-12-17 manuscript/manuscript.qmd
Add draft from Ulysses

@@
 ---
-title: "Amicable Contempt: A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
+title: "Amicable Contempt"
+subtitle: "A Conceptual Framework for Understanding International NGO Behavior in the Era of Closing Civic Space"
 short-title: "Amicable Contempt"
@@
 bibliography: references.bib
+abstract: |
+  I use evidence from a global survey of international NGOs to define each INGO-related element of the theory of amicable contempt.
+I find that INGOs are primarily motivated by their core vision and values, but that they have to balance the pursuit of their missions with instrumental concerns such as fundraising, time, staffing, and collaboration.
+These concerns both limit and enable INGO activities—without substantial instrumental resources and programmatic flexibility, organizations are unable to carry out their mission, while too much emphasis on resource concerns distracts organizations from their core programming and reduces their effectiveness.
+
+  Amid this internal struggle between mission and money, I then introduce how the civil society regulatory environment of INGO host countries is designed to target each element of this struggle.
+Gatekeeping regulations limit which organizations are allowed to enter the country and constrain the flexibility of organizations already present in the country.
+These regulations are primarily defensive and are designed to protect the regime against the potentially destabilizing effects of INGO advocacy and service provision.
+Program capture regulations, on the other hand, are more offensive and target organizational missions instead of their flexibility.
+These laws are designed to co-opt and reshape INGO programming to fall more in line with government preferences, allowing regimes to take advantage of INGO activities.
 ---
 
-Lorem ipsum dolor sit amet, consectetur adipisicing elit [@Mayer:2010], sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Lots of work on closing space - DPR2015
 
-# References
+the legal environment for civil society organizations is becoming increasingly restricted.
+
+In its 2017 report on global civic space, CIVICUS found that only 3% of the world's population lives in open societies with minimal restrictions on associational activity [@CIVICUS:2017], with the majority living in countries with obstructed or repressed civic space (see @fig:civicus-map).
+
+The space for civil society does indeed appear to be closing, but many INGOs have found creative ways to work around legal restrictions to continue their work.
+For example, the Cairo Institute for Human Rights Studies (CIHRS) has worked in Egypt since 1993 as a think tank, research center, and hub for human rights advocacy for the larger Middle East.
+Between 2012–2014, however, the legal environment for INGOs working Egypt became increasingly restricted and CIHRS faced significant threats and legal pressure to end its research.
+In response, in December 2014 CIHRS moved its regional and international operations to Tunisia.[^1] Civic space had closed in Egypt, but CIHRS found a way around the restrictions and continues to engage in research throughout the region.
+
+Other INGOs have made similar adaptations.
+In 2014, for instances, Venezuela faced a deep economic recession while simultaneously cracking down on civic space and barring international aid agencies from the country.
+A group of Venezuelan-Americans in Florida founded El Programa de Ayuda Humanitaria para Venezuela (PAHPV) as a response to the growing humanitarian crisis.[^2] Prohibited from setting up an office in Venezuela itself, PAHPV collected medical equipment, supplies, and other donations throughout the southeastern United States.
+Lacking official legal status in the country, PAHPV initially partnered with domestic Venezuelan NGOs to obtain proper permits for importing goods.
+Later, when unable to obtain permission, PAHPV volunteers flew to Caracas carrying supplies and cash in their luggage, distributing the donations to local NGOs upon arrival.
+Civic space in Venezuela was closed to foreigners, but PAHPV and similar organizations still found their way in.
+
+Hundreds of INGOs face similar regulatory dilemmas and must decide how to respond to increasing government oversight of their programs.
+Civic space is closing around the world, and INGOs are adapting, but not all adapt equally or with the same success.
+
+What determines whether an INGO can avoid becoming captured by the regime and when it can stay actively engaged in its host country? How do
+
+In this article, I provide a theoretical framework for explaining the dynamic relationship between international NGOs and their host country governments.
+
+I theorize that each party is aware that the other both threatens and supports their existence, thus creating a state of *amicable contempt*.
+Governments see global civil society as a strategic player in their domestic political landscape.
+International NGOs can help governments maintain by providing services and expertise, and by bestowing international legitimacy and reputation.
+At the same time, though, INGOs pose a risk to governments.
+Their missions and goals might conflict with the ruling regime’s—for instance, a human rights INGO might condemn a leader who relies on torture to control dissidents.
+To address this dilemma, governments enact regulations and restrictions that offset the costs and risks of letting INGOs operate in their country while simultaneously capturing the political, social, and other practical benefits of these organizations.
+
+International NGOs understand this contentious relationship with their host countries and work to adapt to the political environment.
+Parallel to the cost-benefit calculus of their host governments, INGOs seek to balance their need to pursue their work (often in opposition to the regime) against the risk of acting as a political pawn of the regime and propping it up.
+Rather than passively accepting the regulatory environment imposed on them, INGOs work to either shape that environment or adjust their programs and strategies to maintain access to the country.
+
+Because of the costs involved in confronting and adapting to their regulatory environment, not all INGOs are able to make these adjustments, and organizations often adjust to fit regime preferences or exit the country.
+I theorize that an INGO’s ability to respond to government regulations is determined by two organizational factors: (1) the degree of an INGO’s programmatic and instrumental flexibility influences how it responds to gatekeeping regulations, and (2) an INGO’s commitment to its core mission, vision and values influences how it responds to program capture regulations.
+
+I explore the testable implications of this theory with data from a global survey of INGOs.
+This article provides rich descriptions of INGO responses to regulations.
+While much work has been done on closing civic space, general INGO responses to regulation, and detailed country-specific work, this article provides rich descriptions
+
+In this article, I use rich descriptive data from a global survey of international NGOs to operationalize and define each element of the theory of amicable contempt.
+I find that INGOs are primarily motivated by their core vision and values, but that they have to balance the pursuit of their missions with instrumental concerns such as fundraising, time, staffing, and collaboration.
+These concerns both limit and enable INGO activities—without substantial instrumental resources and programmatic flexibility, organizations are unable to carry out their mission, while too much emphasis on resource concerns distracts organizations from their core programming and reduces their effectiveness.
+
+Similar to DeMattee’s typology, I don’t test any hypotheses or make any causal claims.
+Rather, I present a conceptual framework for understanding the dynamic relationship between INGOs and host governments and illustrate its mechanisms using survey data.
+
+# Theory
+
+Brief lit review stuff on nonprofit motivations and relationships to regimes
+Aseem Prakash + Bloodgood + Tremblay-Boire + Anthony
+
+An INGO's mission and menu of programs will often conflict with the preferences of the regime.
+Accordingly, an organization must decide how to adapt its programming to fit the requirements and needs of its host country.
+This decision can be difficult, pitting conflicting organizational values against each other.
+If the organization is too antagonistic, contentious, or principled, it runs the risk of expulsion, potentially leaving the INGO unable to continue its work in the country.
+However if the organization is too cooperative, its selection of programs may not be credible or effective as the INGO kowtows to the dictator's demands.
+
+I use an adaptation of negotiation theory [@Raiffa:1982; @Mayer:2010] to conceptualize this dynamic relationship between governments and INGOs.[^3] I model the interaction between regimes and INGOs in any given issue area (human rights, development, advocacy, etc.) in simple two-dimensional policy space (see @fig:theory-full).
+Each actor has a preference for a certain level of advocacy or service provision, marked as solid circles in the figure (Regime~ideal~ and INGO~ideal~).
+Governments set *de jure* policies to prevent INGO programming from going beyond the regime's ideal point, while INGOs will engage in programming that, when possible, fits within the bounds set by the regime.
+Each actor has a range of flexibility in the implementation of their regulations or their programming, shown in the horizontal lines flanking the ideal points.
+The space where the two ranges overlap determines both the regime's *de facto* level of restrictions and the INGO's actual mix of programming in that country and constitutes the practical operating environment for the INGO.
+
+![Programming preferences in two-dimensional policy space](../../Graphics/theory-full){#fig:theory-full}
+
+A regime's preferences comprise two components: (1) formal *de jure* legislation, represented by the ideal point, and (2) *de facto* implementation of those policies, represented by the negotiation space around the ideal point.
+Regimes establish a regulatory environment for international civil society that ranges in permissiveness—some countries allow for a large degree of contentious INGO activity, while others are highly restrictive and provide little room for dissonance.
+In turn, and analogous to the regime's preferences, an INGO's negotiation preferences comprise two components: (1) the organization's normative principles and ideals, represented by the ideal point, (2) the organization's programmatic flexibility in actually implementing those principles, represented by the negotiation space.
+INGOs have a desire to engage in a certain level of advocacy, generally defined by their mission, vision, and values.
+INGOs with more instrumental flexibility—that is, a diverse menu of programs, professionalized staff, consistent revenue streams, and collaborative relationships with governments, foundations, and other NGOs—can fine tune their programs to fit the regulatory environments they face, while those with less flexibility are less able to make such adjustments.
+
+The interaction between the actors' negotiation positions introduces two additional dynamics that are crucial for determining how authoritarian regimes regulate INGOs and how well INGOs can respond correspondingly.
+First, the distance between the two parties ideal points determines the contentiousness of their relationship.
+INGOs that engage in programming close to the regime's preferences are naturally more cooperative, either providing services that the government needs or advocating for issues that are unlikely to lead to political instability.
+Accordingly, INGOs that are more cooperative will be *compliant* with the legal limits imposed by the regime.
+Organizations that pursue more contentious programming further from the regime's ideal point, on the other hand, will have an *antagonistic* relationship and will be more likely to openly resist the restrictions imposed on them.
+
+Second, the size of the two actors' overlapping negotiation spaces determines the practical operating environment for INGOs.
+This space falls along a continuum of restrictiveness, ranging from *tolerance*, or very few legal or actual restrictions on INGO programs, to *expulsion*, or a complete ban of all INGO activities.
+The larger the practical operating environment, the more tolerant the regime will be about international NGOs working in their regimes, and vice versa—when there is no overlap, an INGO will face expulsion.
+
+![Possible regulatory environments and regime–INGO relationships](../../Graphics/theory-grid){#fig:theory-grid}
+
+The relationship between INGOs and regimes is dynamic, and shifts in INGO flexibility and de facto regime civil society regulations can create different practical operating environments, demonstrated in @fig:theory-grid.
+For instance, there are two circumstances where INGOs will feel less restricted.
+First, as seen in the top left quadrant of @fig:theory-grid, if the distance between the two parties' ideal points is short and the negotiation spaces overlap—as with INGOs providing non-contentious programming like disaster relief, humanitarian services, or education—INGOs will be cooperative and face a tolerant operating environment.
+Because of preference alignment, these INGOs will not need to rely on their flexibility to maintain access to their host countries.
+
+More contentious organizations with preferences that diverge from the regime's ideal point, on the other hand, can also face a tolerant environment as long as they have a large amount of programmatic flexibility (see bottom left quadrant of @fig:theory-grid).
+For example, @Heiss:2019 explores how human rights INGOs advocate for democratization, political reform, and increased respect for human rights by relying on networks of field offices, funded by dozens of private foundations and government grants—resources that give these organizations the flexibility to remain in their host countries and maintain a fairly tolerant operating environment.
+
+Likewise, there are two circumstances where INGOs will feel restricted, or even expelled.
+Most often, organizations that face restricted operating environments engage in contentious programming and work in countries where regimes have limited de facto regulatory environments, leaving little room for negotiation or overlap (see bottom right quadrant of @fig:theory-grid).
+In contrast, INGOs that are naturally less contentious and more prone to compliance can face expulsion if they lack flexibility or it the civil society regulatory environment is too constrained (see top right quadrant of @fig:theory-grid).
+
+# Data and methods: a global survey of international NGOs
+
+Studying INGO responses to legal regulations—particularly for organizations working in highly restrictive countries—poses a difficult methodological challenge.
+There is extensive cross-country research on the relationship between restrictive governments and *domestic* institutions like civil society [@FrantzKendall-Taylor:2014; @Kendall-TaylorFrantz:2014a; @FrantzEzrow:2011], as well as detailed case studies of specific regimes [@Chen:2012; @Teets:2014; @Hildebrandt:2013], and cross-national quantitative work [@DeMattee; @that-one-group-in-europe], but few studies have examined the motivations and strategies of INGOs themselves.
+
+One reason for this is an absence of data.
+INGOs publish a wealth of unstructured data, such as annual reports, budgets, press releases, or calls to advocacy, but few have systematically compiled these data sources into usable datasets.
+Existing research tends to rely on event data parsed from large corpora of news reports, or presents highly specific in-depth case studies focused on a handful of prominent organizations, resulting in findings and theories that are likely not very generalizable [@BloodgoodSchmitz:2013; @MitchellSchmitz:2014].
+While there is utility in amassing thick descriptions of INGO activities, more must be done.
+@MitchellSchmitz:2014 argue that INGO case studies need to be combined with large, more representative analyses to better understand the organizations that work on specific issue areas as a whole.
+To this end, I illustrate this framework of INGO behavior using the results from a global survey of international NGOs that work in countries that have imposed NGO regulations.
+
+Complete technical details of the survey are provided in the online appendix.
+I define an INGO as any organization that is not incorporated as a governmental entity or as a profit-seeking private firm that conducts advocacy, provides services, or otherwise works in at least *one* country other than the one it is headquartered in.
+Of the 17,590 organizations that potentially received an e-mail invitation to participate in the online survey, 537 completed the survey and 104 provided a partial (but usable) response.
+This yielded a participation rate of 3.8%, which is admittedly low, but comparable to other internet-based organizational surveys [@BaruchHoltom:2008; @HeissKelley:2016].
+Respondents were allowed to answer country-specific questions for multiple countries, thus yielding 641 organization-level responses and 659 country-level responses.
+The survey included 36 open-ended questions, and most respondents answered between 8–16, providing a wealth of qualitative insights into INGO experiences with their host governments.
+To give voice to these organizations, I quote extensively from these responses with minimal editing or correction.
+I guaranteed respondents anonymity to encourage candor in responses and to protect privacy.
+Accordingly, I assign each respondent a random four-digit ID number, and I strip all potentially identifying information from excerpts and quotes from their responses.
+I also anonymize any country-specific information, replacing references to country names with general geographic regions.
+
+Those who filled out the survey were quite familiar with their organizations' work and had an intimate perspective of their organizations' experiences and strategies.
+More than half of the respondents indicated that they were the executive director, president, secretary general, CEO, or other high-level officer for their organization, and roughly a third were staff members or program officers.
+
+Respondents span the globe and work on a wide variety of issues and policies.
+The sample of INGOs have their headquarters spread across 93 different countries (see @fig:hq-countries), with roughly two thirds based in either Europe or the Americas, primarily in the US, UK, and Switzerland (see left panel of @fig:work-hq-regions).
+
+![Countries where INGOs are headquartered](../../Output/figures/3-hq-countries){#fig:hq-countries}
+
+![Regions where INGOs are headquartered vs. regions about which INGOs answered questions](../../Output/figures/3-work-hq-regions){#fig:work-hq-regions}
+
+While comparatively few INGOs are headquartered outside the Global North, these organizations have a worldwide reach.
+In total, INGOs answered questions about their work in 148 different countries.
+The regional distribution of INGO target countries reflects their broader scope and is almost a mirror image of these organizations' home regions—nearly two-thirds of respondents answered questions about their work in Africa and Asia (see right panel of @fig:work-hq-regions), the most underrepresented regions for NGO headquarters.
+This disparity could reflect the fact that INGOs from the Global South without a clear English-language internet presence were excluded from the sample, but the pattern also corresponds to similar findings in other surveys of global NGOs [@Limoncelli:2016; @HeissKelley:2016; @FootToftCesare:2015], reinforcing the idea that Northern-based NGOs tend to focus their work in the South.
+Organizations also operate in a variety of political contexts.
+Unsurprisingly, given the concentration of INGOs in the Global North, the vast majority of respondents (90%) are headquartered in democracies.
+The countries these organizations work in, though, show more diversity in regime type—a third of respondents answered questions about their work in autocratic countries.
+
+# Illustration of framework
+
+To illustrate the mechanics of this framework, I use the results from the global survey of INGOs to provide rich descriptive details of how organizations have navigated the tensions between their core organizational principles and their instrumental constraints and programmatic flexibility.
+I use the survey results to examine the overlap between organizational programmatic flexibility and a regime's regulatory environment, which constitutes the practical operating environment that INGOs must work within.
+
+## Core mission
+
+TODO: mission, vision, values
+
+An organization's foundational mission, vision, and values are represented by the ideal point in the model.
+What exactly these values are, though, has been the subject of a decades-long debate over the role of NGOs in global politics.
+International NGOs were initially seen as a "magic bullet" for global governance: highly principled voluntary organizations that promoted human rights, alleviated poverty, provided needed services following disasters, and generally behaved altruistically under the leadership of well-intentioned mangers [@Reimann:2005; @Skjelsbaek:1971; @NyeKeohane:1971; @Bartelson:2006].
+However, later research highlighted INGOs' lack of public accountability, potential for corruption, dependence on the financial support of governments they were designed to criticize, and emphasis on pursuing funding over mission [@HulmeEdwards:1997a; @HulmeEdwards:1997b; @Marzouk:1997; @BanksHulmeEdwards:2015; @Reimann:2005].
+
+Building on these critiques, a new trend emerged that treated transnational actors as simultaneously normative and strategic [@Cooley:2002; @Keck:1999; @Kelley:2009a].
+@MitchellSchmitz:2014 summarized this debate with their theory of nonprofit principled instrumentalism, or the notion that INGOs must balance their normative mission-driven principles against the instrumental needs of organizational survival.
+Unlike governments that work toward producing social value (such as maximizing national security or promoting general welfare) and unlike firms that focus on financial performance (such as maximizing profits for shareholders), nonprofit organizations face a tradeoff between their social mission and their need for resources and must pursue both concurrently—they must "instrumentally pursue their principled objectives within the economic constraints and political opportunity structures imposed by their external environments" [@MitchellSchmitz:2014, 489].
+
+INGOs are motivated primarily by their foundational mission and values, and they structure their strategies around this vision to ensure that their programming furthers their mission [@Moore:2000].
+Survey respondents confirm this motivation, describing their core mission both in aspirational terms, including "fighting poverty and holding leaders accountable,"[^4] encouraging "awareness and pro-action towards sustainable development,"[^5] and promoting "democracy and open society" and "governments' respect for the human rights of children";[^6] and through more specific statements, such as "improv[ing] healthcare, specifically neurological services, in the least developed nations,"[^7] or ending "the use of immigration detention around the world."[^8]
+
+Most respondents report a tight link between programs and missions, stating that "[o]ur mission, values and vision are reflected in everything that we do," that "all our work is geared towards the accomplishment of this objective," and that "our approach matches our mission precisely."[^9] For many organizations, the "mission and values are the reason we work on these objectives"[^10]—the normative goals of the organization provide strong motivation to engage in pro-social advocacy and services.
+Specific programming strategies are also closely linked to INGO missions.
+For instance, an organization working in South Asia has ambitions to "[b]uild the capacity of local organisations to equip adolescent girls to access their rights and address gender inequality through sport." As expected, much of their programming is centered on sports education and leadership training, but importantly, the organization makes a point that nothing they do is implemented directly: because their core mission is to build local capacity, they ensure that "all the work we do is through local organisations."[^11] Organizations thus work to ensure that their strategies align with and reflect their core missions, visions, and values.
+
+## Ideal point distance and contentiousness
+
+The distance between the government's preferences for a given issue and an INGO's core mission and vision for that issue determine how contentious their relationship will be, ranging from cooperative to antagonistic (see @fig:theory-dot-distance).
+This distance, in turn, influences how governments regulate INGO work.
+The alignment of organizational missions and strategies with government preferences, therefore, is crucial for understanding government regulation of INGOs.
+Organizations working on issues that align with regime preferences will be treated more favorably and with less regulatory pressure than INGOs working on more threatening, less aligned issues.
+
+![Distance between regime and INGO ideal points: contentiousness of relationship](../../Graphics/theory-dot-distance){#fig:theory-dot-distance}
+
+To analyze the favorability of INGO programming to government preferences, I divide the self-reported respondent issues into two levels of potential high or low regime contentiousness based on the potential compatibility of the issue with domestic politics in the host regime [@see Bush:2015 for a similar categorization].
+I code programming as highly contentious if it potentially targets government activities that are core to regime survival, thus posing a direct threat to domestic policies and stability.
+As seen in @fig:issues-worked-on, contentious issues include human rights, advocacy, human trafficking, freedom of expression, conflict, and democracy assistance.
+
+![Issues INGOs work on the most, divided by potential contentiousness](../../Output/figures/3-issues-worked-on){#fig:issues-worked-on}
+
+These highly contentious issues contrast with less contentious topics like education, development, health, and the environment.
+Governments are more willing to accept intervention and assistance in these areas because doing so poses less of a direct threat to regime stability.
+Providing a public platform for opposition leaders can empower rival institutions; digging wells typically does not.
+It is easier for a repressive government to improve its domestic reputation and offset challenges to its political stability by embracing relief organizations, permitting community sport organizations, or partnering with health and environment INGOs.
+
+![Frequency of INGO engagement in different types of activities; organizations answered about one or more activities](../../Output/figures/3-main-activities){#fig:main-activities}
+
+This division of INGOs into contentious and non-contentious programming aligns well with the activities INGOs report engaging in.
+@fig:main-activities shows how frequently responding organizations work on various types of programming.[^12] If the division of contentiousness is correct, low contention INGOs should provide direct aid and services and engage in research and public education most frequently, since these types of programming pose little threat to the target country regime.
+High contention INGOs, on the other hand, should deal most often with more threatening activities like advocacy, political mobilization, and government monitoring.
+There are substantial differences in how frequently high and low contention organizations engage in these types of activities.
+High contention INGOs are more likely to report always engaging in advocacy, monitoring governments, and mobilizing people than their low contention counterparts, which tend to always provide direct aid.[^13] As seen in the figure, 60% of low contention organizations indicated they almost always provide aid, half almost always engage in research, and less than 40% monitor the government or mobilize people.
+Interestingly, about half of low contention organizations reported regularly engaging in advocacy.
+However, this form of advocacy appears to still be non-contentious: respondents describe advocating for "expanded public health programs,"[^14] "agr[i]culture,"[^15] "volunteerism,"[^16] "girls completing secondary education,"[^17] or expanding "access [to] health and justice."[^18]
+
+As expected, high contention organizations are most likely to report always engaging in advocacy (63%) and monitoring government policies (53%), including advocating for the recognition and safety of human rights defenders,[^19]assisting with the "rehabilitation of repentant terrorists,"[^20] promoting religious freedom and human rights, [^21] and "holding … leaders accountable" for their policies and actions.[^22] In aggregate, these more contentious organizations engage in research and public education as the third most common primary activity (53%).
+The educational activities respondents describe clearly pose more of a threat to the government and are more focused on human rights, such as maintaining a death penalty policy database,[^23] organizing activist training sessions and hackathons,[^24] or developing country-specific media literacy training programs.[^25] These organizations only sometimes provide direct aid and services, in contrast to their low contention counterparts.
+Finally, both kinds of INGOs are least likely to report always engaging in political mobilization, which is understandable for low contention organizations but surprising for those working on more contentious issues.
+INGOs may have conflated this kind of work with engaging in research—organizations mentioned political mobilization and campaigns in many of their explanations of their research and public education work.
+
+Though a substantial number of organizations engage in contentious programming, in general, INGOs have a fairly positive relationship with their host governments (@fig:govt-positivity-both), since maintaining some level of government tolerance is essential to staying in the country.
+Only 10% of respondents report having a somewhat or extremely negative relationship with their host governments, while the remainder either have a positive relationship or are ambivalent.[^26] Opinions of the positivity of this relationship depend on the type of government and the contentiousness of the INGO's issue.
+60% of INGOs that reported a negative relationship work in autocracies, while only 20–30% with a positive or ambivalent relationship work in similar regimes.[^27] Similarly, 50% of organizations with a negative relationship work on contentious issues.
+In fact, 17% of high contention INGOs have a negative relationship with their hosts, in contrast to only 8% of low contention organizations.[^28]
+
+![Opinions of relationship with host government, separated by regime type and issue contentiousness (cell heights represent proportion of responses; cell widths represent proportion of organizations working in regime type or on issue)](../../Output/figures/3-govt-positivity-both){#fig:govt-positivity-both}
+
+Organizations working on low contention issues that align with government needs report having a close and cordial working relationship with their hosts.
+A health organization working in West Africa explains that "[w]e work very closely with government hospitals and universities, [and we meet with] various health ministers [regularly],"[^29]and a development organization working in Central America reports that "[w]e work very closely with the trade unions, many of whom have representatives in the National Assembly," and that they have a good relationship with the host government's foreign ministry and with their ambassador in the organization's home country.[^30] Government officials are often enthusiastic about NGO work and sometimes "verbally express their gratitude to work with" foreign NGOs.[^31] One education INGO working in a South Asian dictatorship summarizes the experiences of many low-contention organizations optimistically: "We really do not have any problem with them, mater [sic] of fact they work with us so well that when we need any kind of help they are there for us to assist.
+We have a great relationship."[^32]
+
+Not all organizations enjoy such a warm relationship with the government.
+Some low contention organizations have poor relationships with their host governments because of poor governance, with one disaster relief INGO working in Southeast Asia reporting that "[t]here is a lot of bureaucracy and corruption. We spend so much time to get approval in the projects. We don't agree to pay bribe[s], which makes or [sic] work even more difficult."[^33] More commonly, though, highly contentious INGOs working in authoritarian countries having a more negative relationship with the regime government activities are often the raison d'être for contentious programming.
+A human rights INGO in Latin America notes dryly, "most typically, [governments] are the driving force of the human rights abuse we document."[^34] An organization working in Central Africa also identifies their programming as the source of this poor relationship:
+
+> we document and report human rights violation, we organise presse conference to denounce and alert the peoples on pertinent cases, the government is against this and task us to be instrumantalised by europeans and americans, we undergo threats of all forms and some times watch our meetings monitored.
+[sic][^35]
+
+This organization's mission to report on human rights violations makes its relationship with the government naturally combative, and the government responds by conflating INGO programming with former imperial influence and by closely following the organization's activities.
+The link between contentious programming and poor relationships is reiterated by other human rights INGOs working in Oceania and the Middle East:
+
+> We are highly critical of them and their policies and laws. We are human rights defenders at risk of prosecution for our work in sharing information with the UN human rights mechanisms. We are monitored by the security agency.[^36]
+
+> The government does not want us to document violations of human rights and fundamental freedoms, including systematic torture and abuse of civilians, civil society activists and women rights defenders.[^37]
+
+The distance between the government and INGO preferences explains the potential contentiousness of the relationship between the two parties—the wider the distance, the more antagonistic the relationship.
+Results from the survey show that contentious INGOs are more likely to face stricter regulations, increased scrutiny, and worse relationships with their host governments.
+Interestingly, however, half of contentious INGOs report strong and positive relationships with the government despite their ideological distance.
+Differences in preferences thus do not fully account for the de facto relationship.
+For a more complete explanation, we must look at interplay between two other elements of the model: an organization's programmatic flexibility and its overlap with government regulations.
+
+## Programmatic flexibility
+
+According to @MitchellSchmitz:2014, nonprofit organizations are primarily *driven* by their missions and *constrained* by instrumental concerns: worries about money and other resources get in the way of pursuing deeper normative principles.
+I argue, however, that this view of instrumentality is insufficient.
+Instrumental concerns, including time, money, or political connections, are not simply constraints.
+These resources are what allow INGOs to pursue their principled ideals in the first place—they provide organizations with the flexibility to engage in programming and adapt to the political and regulatory environments they face.
+The region surrounding the organization's ideal point represents its reserve of *programmatic* flexibility (see @fig:theory-ngo-space), or the organization's ability and willingness to make changes to its programs in response to regulations.
+
+![Space around INGO ideal point: instrumental flexibility](../../Graphics/theory-ngo-space){#fig:theory-ngo-space}
+
+Flexibility has a dual function.
+First, it is what allows an INGO to carry out its core mission.
+Programmatic flexibility is influenced by instrumental concerns, including an organization's size, diversity of funding sources, professionalization of staff, knowledge of the host country—essentially any resource-oriented strategy that permits an organization to implement its mission effectively in dynamic environments.
+This flexibility is also a function of organization norms—INGOs must be willing to use their instrumental resources to make appropriate adjustments to stay in the country.
+In some cases, an organization might have substantial income and highly professional staff, but will purposely choose to not engage in advocacy in a restrictive country because of its organizational vision or norms (i.e.
+its ideal point).
+
+The link between an organization's ideals and its flexibility represents a tension unique to third sector organizations.
+INGOs must balance their normative principles against the instrumental need of organizational survival.
+Nonprofit organizations must concern themselves with resources: ignoring necessary overhead concerns in favor of pursuing its vision will limit the organization's ability to effectively fund or carry out that mission (see @Moore:2000, 195).
+At the same time, the pursuit of flexibility is constrained by nonprofit norms.
+Dedicating too much time to expanding flexibility through overhead activities like fundraising, professionalization, and marketing can erode public trust in the organization.
+
+Second, programmatic flexibility provides INGOs with a protective margin around their core missions, and their reserve of resources determines how effectively they can respond to different forms of government restriction and regulation.
+When host regimes constrict the allowable space for INGO activity and put pressure on their ideal points, organizations can respond by relying on their programmatic flexibility to make marginal adjustments to their non-core programming—organizations can marshal new resources, collaborate with more partner organizations, request the support of more powerful external actors, relocate their programs to other countries, or pursue other strategies to circumvent, mitigate, or otherwise reduce the impact of those constraints.
+The more flexibility an INGO has, the better they can adapt and the more creative and antagonistic they can potentially be; the less flexibility they have, the less so.
+
+The majority of INGOs in the survey maintain a positive relationship with their host countries.
+This is the "amicable" side of the theory of amicable contempt—organizations can help guarantee their access to the country by acting friendly towards the regime, even if their programming might challenge the regime.
+But the need for amicability does not mean that organizations must give up on their core vision and mission, taming their programs to completely match their host governments' preferences, nor does it entail that governments will always be friendly to the INGOs they allow in: half of organizations with negative host-country relationships work on contentious issues, but by extension, half of the INGOs at odds with the government engage in less contentious programming.
+The ability of INGOs to remain in their host countries, avoid restrictions, and maintain positive relationships with the government does not depend entirely on ideal preferences.
+Both actors can emphasize the "contempt" of amicable contempt by making changes to the space around their ideal points.
+
+The survey reveals multiple sources of programmatic flexibility.
+Most of the organizations that responded to the survey were small, with half employing eight or fewer staff members.
+This does not mean, however, that the INGO sector as a whole employs few people—because of dozens of large organizations with hundreds (and even thousands) of employees, the average staff size is 50.
+These larger, better-staffed organizations inherently need to have access to more financial resources to pay their employees, which entails a greater need for consistent revenue flows.
+At the same time, having more employees provides these larger organizations with more flexibility in the face of restrictions—if an organization is limited in one country, it can more easily shift programs and staff around to work in other countries or on other topics.
+
+<div id="fig:funding-size">
+![Source of funding](../../Output/figures/3-funding-size-totals){#fig:funding-size-totals}
+
+![Reliance on funding sources](../../Output/figures/3-funding-size-pct){#fig:funding-size-pct}
+
+Level of reliance on sources of funding, divided by organization size
+</div>
+
+Variation in funding sources also helps determine an organization's flexibility.
+Government grants—from host countries, target countries, and other donor countries—are the most common stream of income reported by respondents, followed by individual donations, grants from NGOs and foundations, and corporate giving (see @fig:funding-size-totals).
+Additionally, dozens of respondents report generating their own income through fundraising efforts, member fees, consulting services, and unrelated business income.
+The size of the organization is related to the funding sources it relies on.
+Organizations that employ more than 50 people selected an average of 4 streams of funding, while smaller organizations reported an average of 3.
+The mix and selection of funding sources can also depend on organization size (see @fig:funding-size-pct).
+Smaller organizations are most likely to rely primarily on fundraising, member fees, and individual donations, and less heavily on grants from NGOs, foundations, and corporations.
+Larger organizations are far more likely than their smaller counterparts to draw money from governments, IGOs, and corporations.
+Diversification in income sources provides flexibility—if an organization fails to obtain a government grant, it can turn to foundations, fundraising, or other sources to compensate.
+Organizations with more sources of funding are thus likely more flexible when facing restrictions on their programs abroad.
+
+![Main obstacles to INGO mission; multiple obstacles allowed](../../Output/figures/3-obstacles){#fig:obstacles}
+
+Flexibility is self-reinforcing.
+The presence of some forms of flexibility, such as a professionalized staff with employees dedicated to fundraising, make it easier to obtain additional resources [@Fogal:2010], and vice versa—the absence of flexibility imposes a host of challenges to INGO missions.
+Nearly 70% of respondents identified funding as the primary obstacle to pursuing their mission (see @fig:obstacles), followed by other instrumental obstacles like needing to professionalize staff, struggling to work well with local employees and staff, and coordinating efficiently with other NGOs.
+Without consistent funding, organizations struggle to hire staff, train volunteers, build relationships with local bureaucrats and politicians, or engage in long-term programs in their host countries.
+A health advocacy organization working in East Africa notes the dampening effect a lack of funding has on its flexibility, stating that the biggest obstacle to fulfilling its mission is
+
+> [c]ore funding so we can do our work and stop spending so much time on raising money to do our work.
+We are activists, researchers, communications experts, we don’t want to spend our lives raising money, schmoozing funding partners and writing proposals.[^38]
+
+These obstacles and challenges to flexibility shape and limit how well INGOs can pursue their missions, but INGOs do not generally redefine their missions in response to these challenges.
+Rather, when organizations make strategic adjustments to enhance access to funds, professionalize staff, or improve programmatic flexibility in general, they attempt do so without modifying their core missions.
+"The overall goal of the organization should remain the same," explains an anti-human trafficking INGO working in Southeast Asia, while "strategies to achieve that goal should change and grow on a regular basis, in order to adapt to the development of trends and new technologies."[^39] Similarly, a development INGO in the Caribbean identified a need to adjust instrumental strategies while maintaining their core mission: "Our goals are sound, and the way we do our work is effective, but I feel we need to revamp our fundraising strategy."[^40] Protecting the core mission is essential in the face of financial constraints, and organizations will engage in creative adjustments to maintain their values.
+For instance, a development INGO in Latin America relates that "[f]unding is always an issue, but in the last 5 years we have changed our strategy to work as a consultancy firm (*without losing our values, vision and mission*) so we can achieve our annual budget."[^41] Even though it changed its legal organizational form, the organization claims that the shift enabled it to more effectively "improve the business ecosystem" and "create value to society" throughout Latin America.
+
+A human rights INGO working in Latin America summarizes the importance of flexibility succinctly, explaining that the largest obstacle to carrying out their mission is "the small size of the organization and the lack of economic resources to ensure the maintenance of activities independently of the public authorities."[^42] Without robust programmatic flexibility, INGOs risk losing both access to their host countries and independence from interference by their host countries.
+
+Thus, international NGOs are generally driven by their core missions and principles, but must pursue their programming within instrumental constraints.
+The results from the survey strengthen previous work by @MitchellSchmitz:2014 and others, demonstrating how INGOs find themselves caught in a dilemma between principles and instrumentality.
+I add to this work by arguing that instrumental concerns are not always constraints—the pursuit of resources enables INGO missions in the first place and provides organizations with programmatic flexibility.
+Additionally, flexibility allows organizations to protect their core missions and avoid changing them in the face of obstacles.
+The difficulty for nonprofit organizations is to strike the proper balance—focusing too much on mission and ignoring the need for resources can lead to untenable and unfunded programming, while focusing too much on obtaining resources and enhancing flexibility can become an inferior substitute for an organization's more principled goals.
+
+## Practical operating environment
+
+Even under favorable political circumstances, nonprofit organizations walk a difficult tightrope between the dual pressures of mission and money.
+This balancing act becomes even more difficult when institutional environments work to constrict, target, and limit their programming [@HeissKelley:2017].
+Beyond financial and staffing constraints, a third of respondents indicated that domestic politics, laws, bureaucracies, corruption, and conflict also pose substantial burdens to their programming (see @fig:obstacles).
+Respondents note that they are limited by "shrinking civil space"[^43] and "increasingly restrictive laws in countries where our members operate"[^44] in the countries they target, by "[c]onstant attempts by public and private actors to restrict freedom of expression and media freedom"[^45] and by direct government interference in their activities.[^46]
+
+Host governments expand and contract the de facto allowable space for civil society advocacy based on concerns for regime stability and other shifts in internal politics, external threats, and reputational pressures.
+For their part, INGOs must ensure that their activities fall within the bounds set by the regime.
+The overlap of an organization's programmatic flexibility and a government's de facto regulatory environment determines the practical operating environment for the INGO.
+NGO regulations are not inherently limiting—many regulations exist to help regularize INGO-state relations and represent a large overlapping space [@BloodgoodTremblay-Boire:2016].
+As the size of the overlap decreases, however, the practical operating environment for INGOs becomes constrained and organizations risk expulsion.
+
+Because governments set the initial conditions for operating, keeping track of the regulatory environment is crucial for INGOs to make appropriate adjustments and maintain legal status their host countries.
+INGOs tend to be quite aware of the regulatory environment of their host countries, with more than 80% of respondents somewhat or very familiar with the laws regulating their activities (see @fig:familiarity-both).[^47] Familiarity is affected by the type of regime organizations work in.
+More than 75% of respondents who answered that they do not know anything about regulations work in democracies, while those most familiar with the regulatory environment are split roughly equally between democracies and autocracies.[^48] INGOs working in dictatorships are the most likely to be the most familiar with regulations, likely because deep knowledge of the legal environment is more essential to operate safely and effectively.
+The contentiousness of the issues INGOs work on does not help determine their familiarity—high contention INGOs are not more or less likely to be more aware of the legal environment.[^49]
+
+![Knowledge of regulatory environment in host government, separated by regime type and issue contentiousness (cell heights represent proportion of responses; cell widths represent proportion of organizations working in regime type or on issue)](../../Output/figures/3-familiarity-both){#fig:familiarity-both}
+
+INGOs report that the regulatory environment can change frequently—half of respondents report that regulations and laws change every few years, and nearly 20% say regulations change at least once a year (see @fig:frequency).[^50] The regime type of the host country is closely related to how frequently INGOs see changes in regulations.
+Nearly two thirds of the INGOs that report changes at least once a year work in autocracies, which contrasts starkly with the two thirds of INGOs that experience a static legal environment in democratic host countries.[^51]
+
+![Frequency of changes in regulatory environment for NGOs in host country, separated by regime type (cell heights represent proportion of responses; cell widths represent proportion of organizations working in regime type)](../../Output/figures/3-frequency){#fig:frequency}
+
+Given their frequency, the regulatory changes INGOs observe do not necessarily correlate with formal statutory developments.
+These laws give bureaucrats and politicians significant interpretive leeway, however, and allow them to reshape the regulatory environment for international NGOs [@TODO-chaudhry-heiss-2022].
+Because of this dynamic discretionary de facto environment, INGOs actively seek out information about changes in laws, rules, and regulations.
+International NGOs are most likely to hear about new legal changes from other NGOs in the country, both from their local partners and from other foreign organizations.
+They also receive news about changes directly from government officials, sometimes at inopportune moments.
+One INGO working in East Africa, unaware of any changes in regulations, discovered new funding requirements for foreign NGOs when requesting permits to expand their operations in the country—the organization ultimately decided to not expand as a result.[^52] INGOs also find out about changes in laws through the media and through internet research, including websites that aggregate information about civil society regulations like Civicus and the International Center for Not-for-Profit Law (ICNL).
+
+Due to increased concerns of regime stability in authoritarian countries [@competitve-authnism], regime type influences the size of the de facto regulatory environment.
+Following the framework, autocracies should have a narrow allowable space, leading to a smaller overlap or practical operating environment.
+Nearly two-thirds of the survey respondents that feel the most constrained by government regulations work in autocracies, compared to 25% of organizations that report facing no restrictions in similar regimes (see @fig:restriction-both).[^53] The relationship between host country regime type and feelings of restriction is quite marked, with the proportion of respondents working in autocracies decreasing steadily as the feeling of restriction decreases.
+
+![Feeling of restriction in host country across regime type separated by regime type (cell heights represent proportion of responses; cell widths represent proportion of organizations working in regime type)](../../Output/figures/3-restriction-both){#fig:restriction-both}
+
+The overlap of INGO programmatic flexibility and a government's de facto regulatory environment thus determines the practical operating environment for INGO activities, which in turn imposes additional constraints on these organizations.
+All nonprofit organizations face an internal conflict between mission and money, but nonprofits working as guests in repressive host countries are subject to regulatory vagaries linked to domestic political struggles.
+INGOs spend resources to remain aware of changes in the regulatory environment and generally work to ensure that their programs do not lead to expulsion.
+For most INGOs, maintaining access to the country is critical for successfully undertaking their missions, and as a result, most organizations—including half of the more contentious respondents—try to uphold somewhat of a good relationship with their host governments.
+
+# Discussion and conclusion
+
+International NGOs are motivated by different concerns when contemplating how to react to government restrictions, and institutional and organizational characteristics—namely the contentiousness of the INGO–government relationship and the amount of programmatic flexibility enjoyed by the INGO—help determine these organizations' reactions.
+Authoritarian governments design their civil society regulatory environment to target different elements of an INGO's organizational preferences—gatekeeping regulations keep potentially harmful organizations out of the country and seek to limit the practical operating environment by reducing organizational flexibility, while program capture regulations allow regimes to take advantage of their guest organizations and seek to distort organizational values.
+@tbl:ingo-reactions-summary provides a helpful overview of these different pressures, concerns, and reactions.
+
+\stgroup
+\footnotesize
+\renewcommand\arraystretch{1.6}
+!INCLUDE "../../Output/tables/3-ingo-reactions-summary.md"
+\fingroup
+
+When confronting gatekeeping regulations, an INGO's primary concern is to gain or maintain access to the country.
+An INGO's level of contentiousness, in concert with the government's civil society regulatory environment, determines how much regulatory pressure the INGO will face.
+Highly contentious organizations will face higher scrutiny as regimes attempt to limit their access to the country, head off potential political threats, and make the practical operating environment more difficult.
+In response, organizations that enjoy greater programmatic flexibility can make creative adjustments on the margins of their missions (i.e.
+without redefining their core) to adapt to these laws.
+Organizations with less flexibility, on the other hand, are less likely to be able to adjust to the operating environment and will cease their work, exit the country, avoid entering the country in the first place, or maintain a low profile and avoid contact with the government as much as possible.
+Correspondingly, because they pose less of a political threat to the regime, low contention organizations will face less pressure and scrutiny and should not need to make as many creative adjustments to remain in the country.
+
+In contrast, when facing regulations designed to capture their programs, INGOs are concerned with protecting their core mission and ensuring that complying with government regulations, cooperating with the host government, and allowing for a degree of control or co-optation does not conflict with their values.
+While gatekeeping regulations are designed to target all potential organizations and act as a filter, program capture regulations target only those organizations allowed in the country.
+Organizations with high programmatic flexibility will be able to resist or adjust to government attempts at co-optation, while those with fewer resources and less flexibility will be more likely to either concede to government demands or exit the country.
+High contention organizations face a different dynamic.
+INGOs that are able to overcome gatekeeping regulations and *enter* the country are more likely to have high flexibility, and are thus more likely to be able to resist co-optation, while INGOs that remain *outside* of the country and work from exile because of strict gatekeeping laws also are more likely to have high flexibility and can more easily resist co-optation.
+
+[^1]:	Cairo Institute for Human Rights Studies, "After 20 years: CIHRS moves its regional and international programs outside Egypt," accessed August 2, 2017, [http://www.cihrs.org/?p=10298&lang=en](http://www.cihrs.org/?p=10298&lang=en).
+
+[^2]:	See [http://www.ayudahumanitariavenezuela.org](http://www.ayudahumanitariavenezuela.org), accessed August 2, 2017.
+
+[^3]:	The best way to understand the theory is to visit an explorable explanation at [ingorestrictions.org/theory/](https://ingorestrictions.org/theory/) and see the different outcomes dynamically [@Gourarie:2016].
+
+[^4]:	Response 1193.
+
+[^5]:	Response 1267.
+
+[^6]:	Responses 1328 and 1252.
+
+[^7]:	Response 1257.
+
+[^8]:	Response 1376.
+
+[^9]:	Response 1245, 1267, and 1272.
+
+[^10]:	Response 1643.
+
+[^11]:	Response 1799.
+
+[^12]:	"Always" and "Most of the time" responses are collapsed to "Almost always"; "About half the time" and "Sometimes" responses are collapsed to "Sometimes."
+
+[^13]:	The probability that the difference in proportion of high and low contention INGOs selecting "Almost always" is greater than zero is generally substantial: high contention organizations = advocacy ($P(\Delta > 0) = 0.01$), monitoring ($P(\Delta > 0) = 0.03$), and mobilizing ($P(\Delta > 0) = 0.13$); low contention organizations = aid and services ($P(\Delta > 0) = 0.87$); there is no substantial difference between the responses of high and low contention organizations for engaging in research and public education ($P(\Delta > 0) = 0.47$).
+All posterior probabilities are available in @tbl:main-activities-p in the appendix.
+
+[^14]:	Response 1385.
+
+[^15]:	Response 1605.
+
+[^16]:	Response 1472.
+
+[^17]:	Response 1419.
+
+[^18]:	Response 1448.
+
+[^19]:	Response 1339.
+
+[^20]:	Response 1233.
+
+[^21]:	Responses 1304 and 1703.
+
+[^22]:	Response 1193.
+
+[^23]:	Response 1558.
+
+[^24]:	Responses 1487 and 1660.
+
+[^25]:	Response 1643.
+
+[^26]:	"Extremely negative" and "Somewhat negative" are collapsed to "Negative"; "Somewhat positive" and "Extremely positive" are collapsed to "Positive."
+
+[^27]:	This difference is significant: $P(\% \text{ Negative}_\text{Autocracies} - \% \text{ Positive}_\text{Autocracies} > 0) = 0.97$.
+
+[^28]:	This difference is also significant: $P(\% \text{ Negative}_\text{Autocracies} - \% \text{ Positive}_\text{Autocracies} > 0) = 0.97$.
+
+[^29]:	Response 1189.
+
+[^30]:	Response 1192.
+
+[^31]:	Responses 1243, 1253, 1284 and 1323.
+
+[^32]:	Response 1507.
+
+[^33]:	Response 1224.
+
+[^34]:	Response 1375.
+
+[^35]:	Response 1339.
+
+[^36]:	Response 1408.
+
+[^37]:	Response 1458.
+
+[^38]:	Response 1211.
+
+[^39]:	Response 1194.
+
+[^40]:	Response 1574.
+
+[^41]:	Response 1225, emphasis added.
+
+[^42]:	Response 1188, original in Spanish.
+
+[^43]:	Response 1296.
+
+[^44]:	Response 1428.
+
+[^45]:	Response 1317.
+
+[^46]:	Response 1193.
+
+[^47]:	It is important to remember that this high percentage is likely tied to who responded to the survey—as explained previously, more than 50% of respondents were the organization's CEO, executive director, or other high-level officer.
+
+	"Extremely familiar" and "Very familiar" are collapsed to "Very familiar"; "Moderately familiar" and "Slightly familiar" are collapsed to "Somewhat familiar."
+
+[^48]:	$P(\% \text{ Very familiar}_\text{Autocracies} - \% \text{ Not familiar at all}_\text{Autocracies} > 0) = 0.99$.
+
+[^49]:	$P(\% \text{ Very familiar}_\text{High contention} - \% \text{ Not familiar at all}_\text{High contention} > 0) = 0.45$.
+
+[^50]:	"Once a month" and "Once a year" are collapsed to "At least once a year."
+
+[^51]:	$P(\% \text{ At least once a year}_\text{Autocracies} - \% \text{ Rarely or never}_\text{Autocracies} > 0) = 0.97$.
+
+[^52]:	Response 1211.
+
+[^53]:	"Very restricted" and "Extremely restricted" are collapsed to "Very restricted."
+
+	$P(\% \text{ Very restricted}_\text{Autocracies} - \% \text{ Not restricted}_\text{Autocracies} > 0) = 1$.

### 2023-12-17 manuscript/manuscript.qmd
fix errant nbsps
Uncurl quotes since pandoc deals with that

@@
 Other INGOs have made similar adaptations.
-In 2014, for instances, Venezuela faced a deep economic recession while simultaneously cracking down on civic space and barring international aid agencies from the country.
+In 2014, for instance, Venezuela faced a deep economic recession while simultaneously cracking down on civic space and barring international aid agencies from the country.
 A group of Venezuelan-Americans in Florida founded El Programa de Ayuda Humanitaria para Venezuela (PAHPV) as a response to the growing humanitarian crisis.[^2] Prohibited from setting up an office in Venezuela itself, PAHPV collected medical equipment, supplies, and other donations throughout the southeastern United States.
@@
 At the same time, though, INGOs pose a risk to governments.
-Their missions and goals might conflict with the ruling regime’s—for instance, a human rights INGO might condemn a leader who relies on torture to control dissidents.
+Their missions and goals might conflict with the ruling regime's—for instance, a human rights INGO might condemn a leader who relies on torture to control dissidents.
 To address this dilemma, governments enact regulations and restrictions that offset the costs and risks of letting INGOs operate in their country while simultaneously capturing the political, social, and other practical benefits of these organizations.
@@
 Because of the costs involved in confronting and adapting to their regulatory environment, not all INGOs are able to make these adjustments, and organizations often adjust to fit regime preferences or exit the country.
-I theorize that an INGO’s ability to respond to government regulations is determined by two organizational factors: (1) the degree of an INGO’s programmatic and instrumental flexibility influences how it responds to gatekeeping regulations, and (2) an INGO’s commitment to its core mission, vision and values influences how it responds to program capture regulations.
+I theorize that an INGO's ability to respond to government regulations is determined by two organizational factors: (1) the degree of an INGO's programmatic and instrumental flexibility influences how it responds to gatekeeping regulations, and (2) an INGO's commitment to its core mission, vision and values influences how it responds to program capture regulations.
 
@@
 
-Similar to DeMattee’s typology, I don’t test any hypotheses or make any causal claims.
+Similar to DeMattee's typology, I don't test any hypotheses or make any causal claims.
 Rather, I present a conceptual framework for understanding the dynamic relationship between INGOs and host governments and illustrate its mechanisms using survey data.
@@
 Not all organizations enjoy such a warm relationship with the government.
-Some low contention organizations have poor relationships with their host governments because of poor governance, with one disaster relief INGO working in Southeast Asia reporting that "[t]here is a lot of bureaucracy and corruption. We spend so much time to get approval in the projects. We don't agree to pay bribe[s], which makes or [sic] work even more difficult."[^33] More commonly, though, highly contentious INGOs working in authoritarian countries having a more negative relationship with the regime government activities are often the raison d'être for contentious programming.
+Some low contention organizations have poor relationships with their host governments because of poor governance, with one disaster relief INGO working in Southeast Asia reporting that "[t]here is a lot of bureaucracy and corruption.
+We spend so much time to get approval in the projects.
+We don't agree to pay bribe[s], which makes or [sic] work even more difficult."[^33] More commonly, though, highly contentious INGOs working in authoritarian countries having a more negative relationship with the regime government activities are often the raison d'être for contentious programming.
 A human rights INGO in Latin America notes dryly, "most typically, [governments] are the driving force of the human rights abuse we document."[^34] An organization working in Central Africa also identifies their programming as the source of this poor relationship:
@@
 
-> We are highly critical of them and their policies and laws. We are human rights defenders at risk of prosecution for our work in sharing information with the UN human rights mechanisms. We are monitored by the security agency.[^36]
+> We are highly critical of them and their policies and laws.
+We are human rights defenders at risk of prosecution for our work in sharing information with the UN human rights mechanisms.
+We are monitored by the security agency.[^36]
 
@@
 > [c]ore funding so we can do our work and stop spending so much time on raising money to do our work.
-We are activists, researchers, communications experts, we don’t want to spend our lives raising money, schmoozing funding partners and writing proposals.[^38]
+We are activists, researchers, communications experts, we don't want to spend our lives raising money, schmoozing funding partners and writing proposals.[^38]
 

### 2023-12-18 manuscript/manuscript.qmd
Add initial computational stuff

@@
 - name: Andrew Heiss
-  affiliation: Georgia State University
+  affiliations: 
+    - id: gsu
+      name: Georgia State University
+      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
+      address: "55 Park Place NE, #464"
+      city: Atlanta
+      region: GA
+      country: USA
+      postal-code: 30303
+  url: https://www.andrewheiss.com/
   email: aheiss@gsu.edu
   orcid: 0000-0002-3948-3914
-bibliography: references.bib
+code-repo: "Access the code, data, and analysis at <https://github.com/andrewheiss/truthful-tuna>"
 abstract: |
@@
 These laws are designed to co-opt and reshape INGO programming to fall more in line with government preferences, allowing regimes to take advantage of INGO activities.
+
+bibliography: references.bib
+csl: csl/apa.csl
+link-citations: true
+word-count: "9,878"
 ---
+
+```{r setup, include=FALSE}
+if (is.null(knitr::pandoc_to())) {
+  fmt_out <- "interactive"
+} else {
+  fmt_out <- knitr::pandoc_to()
+}
+
+knitr::opts_chunk$set(
+  echo = FALSE, include = FALSE,
+  warning = FALSE, message = FALSE,
+  fig.align = "center", fig.retina = 3,
+  fig.width = 6, fig.height = (6 * 0.618),
+  out.width = "100%", collapse = TRUE
+)
+
+options(
+  digits = 3, width = 120,
+  dplyr.summarise.inform = FALSE
+)
+```
+
+```{r libraries-data}
+library(tidyverse)
+library(scales)
+library(tidybayes)
+library(marginaleffects)
+library(patchwork)
+library(glue)
+library(janitor)
+library(gt)
+library(targets)
+
+# Generated via random.org
+set.seed(8511)
+
+# Targets stuff
+tar_config_set(
+  store = here::here("_targets"),
+  script = here::here("_targets.R")
+)
+
+# Plotting and modelsummary functions
+invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
+invisible(list2env(tar_read(table_functions), .GlobalEnv))
+
+theme_set(theme_ingo())
+set_annotation_fonts()
+```
 

### 2023-12-22 manuscript/appendix.qmd
Add theory illustration

@@
   orcid: 0000-0002-3948-3914
-bibliography: references.bib
+bibliography: references.json
 crossref: 

### 2023-12-22 manuscript/manuscript.qmd
Add theory illustration

@@
 abstract: |
-  I use evidence from a global survey of international NGOs to define each INGO-related element of the theory of amicable contempt.
-I find that INGOs are primarily motivated by their core vision and values, but that they have to balance the pursuit of their missions with instrumental concerns such as fundraising, time, staffing, and collaboration.
-These concerns both limit and enable INGO activities—without substantial instrumental resources and programmatic flexibility, organizations are unable to carry out their mission, while too much emphasis on resource concerns distracts organizations from their core programming and reduces their effectiveness.
+  Stuff here
 
-  Amid this internal struggle between mission and money, I then introduce how the civil society regulatory environment of INGO host countries is designed to target each element of this struggle.
-Gatekeeping regulations limit which organizations are allowed to enter the country and constrain the flexibility of organizations already present in the country.
-These regulations are primarily defensive and are designed to protect the regime against the potentially destabilizing effects of INGO advocacy and service provision.
-Program capture regulations, on the other hand, are more offensive and target organizational missions instead of their flexibility.
-These laws are designed to co-opt and reshape INGO programming to fall more in line with government preferences, allowing regimes to take advantage of INGO activities.
-
-bibliography: references.bib
+bibliography: references.json
 csl: csl/apa.csl
@@
 library(marginaleffects)
+library(sf)
+library(ggtext)
+library(ggalluvial)
 library(patchwork)
@@
 library(janitor)
+library(countrycode)
 library(gt)
@@
 )
+
+tar_load(c(
+  survey_orgs, survey_countries, survey_all,
+  world_map
+))
 
@@
 The space for civil society does indeed appear to be closing, but many INGOs have found creative ways to work around legal restrictions to continue their work.
-For example, the Cairo Institute for Human Rights Studies (CIHRS) has worked in Egypt since 1993 as a think tank, research center, and hub for human rights advocacy for the larger Middle East.
+For example, since 1993 the Cairo Institute for Human Rights Studies (CIHRS) worked in Egypt as a think tank, research center, and hub for human rights advocacy for the larger Middle East.
 Between 2012–2014, however, the legal environment for INGOs working Egypt became increasingly restricted and CIHRS faced significant threats and legal pressure to end its research.
-In response, in December 2014 CIHRS moved its regional and international operations to Tunisia.[^1] Civic space had closed in Egypt, but CIHRS found a way around the restrictions and continues to engage in research throughout the region.
+In response, in December 2014 CIHRS moved its regional and international operations to Tunisia [@CIHRS:2014].
+Civic space had closed in Egypt, but CIHRS found a way around the restrictions and continues to engage in research throughout the region.
 
@@
 If the organization is too antagonistic, contentious, or principled, it runs the risk of expulsion, potentially leaving the INGO unable to continue its work in the country.
-However if the organization is too cooperative, its selection of programs may not be credible or effective as the INGO kowtows to the dictator's demands.
+However if the organization is too cooperative, its selection of programs may not be credible or effective as the INGO bends to the government's demands.
 
-I use an adaptation of negotiation theory [@Raiffa:1982; @Mayer:2010] to conceptualize this dynamic relationship between governments and INGOs.[^3] I model the interaction between regimes and INGOs in any given issue area (human rights, development, advocacy, etc.) in simple two-dimensional policy space (see @fig:theory-full).
-Each actor has a preference for a certain level of advocacy or service provision, marked as solid circles in the figure (Regime~ideal~ and INGO~ideal~).
-Governments set *de jure* policies to prevent INGO programming from going beyond the regime's ideal point, while INGOs will engage in programming that, when possible, fits within the bounds set by the regime.
+I use an adaptation of negotiation theory [@Raiffa:1982; @Mayer:2010] to conceptualize this dynamic relationship between governments and INGOs.
+I represent the interaction between regimes and INGOs in any given issue area (human rights, development, advocacy, etc.) in simple two-dimensional policy space (see @fig-theory-full).
+Each actor has a preference for a certain level of advocacy or service provision, marked as solid circles in the figure.
+Governments set *de jure* policies to prevent INGO activities from going beyond the regime's ideal point, while INGOs will engage in programming that, when possible, fits within the bounds set by the regime.
 Each actor has a range of flexibility in the implementation of their regulations or their programming, shown in the horizontal lines flanking the ideal points.
@@
 
-![Programming preferences in two-dimensional policy space](../../Graphics/theory-full){#fig:theory-full}
+```{r}
+#| label: fig-theory-full
+#| fig-cap: "Programming preferences in two-dimensional policy space"
+#| out-width: "100%"
+#| include: true
+
+knitr::include_graphics("graphics-manual/out/theory-full.png", auto_pdf = TRUE)
+```
 
@@
 This space falls along a continuum of restrictiveness, ranging from *tolerance*, or very few legal or actual restrictions on INGO programs, to *expulsion*, or a complete ban of all INGO activities.
-The larger the practical operating environment, the more tolerant the regime will be about international NGOs working in their regimes, and vice versa—when there is no overlap, an INGO will face expulsion.
+The larger the practical operating environment, the more tolerant the regime will be about international NGOs working in their regimes, and vice versa—when there is no overlap, an INGO will no longer be allowed to operate in the country.
 
-![Possible regulatory environments and regime–INGO relationships](../../Graphics/theory-grid){#fig:theory-grid}
+```{r}
+#| label: tbl-theory-grid
+#| include: true
+#| tbl-cap: "Possible combinations of INGO/regime relationships and practical 
+#|   operating environments"
 
-The relationship between INGOs and regimes is dynamic, and shifts in INGO flexibility and de facto regime civil society regulations can create different practical operating environments, demonstrated in @fig:theory-grid.
+tibble(
+  col1 = c(
+    "**Cooperative**", rep("", 2),
+    "**Antagonistic**", rep("", 2)
+  ),
+  Tolerance = c(
+    "The INGO's core mission is close to regime preferences and the INGO/regime relationship is cooperative.
+De jure laws may be stricter than the INGO's ideal preferences, but because there is overlap between de facto regulations and INGO programs, the regime tolerates the INGO's work and the organization operates comfortably in the country.",
+    "cooperation-tolerance",
+    "*Example*: The Red Cross or Oxfam in most countries",
+    "The INGO's core mission is far from regime preferences and the INGO/regime relationship is antagonistic.
+Because there are substantial associational rights and freedom for advocacy, and because the INGO has a range of possible programming, the regime tolerates the INGO's work and the organization operates comfortably in the country.",
+    "antagonism-tolerance",
+    "*Example*: Amnesty International in the United States"
+  ),
+  Expulsion = c(
+    "The INGO's core mission is close to regime preferences and the INGO/regime relationship should theoreticaly be cooperative.
+However, because the de facto civil society regulatory environment is highly constricted, and because the INGO has limited programmatic flexibility, the regime severely limits or expels the organization.",
+    "cooperation-expulsion",
+    "*Example*: Ford Foundation or Mercy Corps in India after 2015",
+    "The INGO's core mission is far from regime preferences and the INGO/regime relationship is antagonistic.
+Because the de facto civil society regulatory environment is highly constricted, the regime restricts, bans, or expels the organization even if the INGO has substantial programmatic flexibility.",
+    "antagonism-expulsion",
+    "*Example*: Amnesty International with North Korea"
+  )
+) |>
+  group_by(group = "Nature of relationship") |> 
+  gt(id = "theory-table") |>
+  tab_spanner(
+    label = "Practical operating environment",
+    columns = c(Tolerance, Expulsion)
+  ) |> 
+  cols_label(col1 = "") |>
+  fmt_markdown(columns = everything(), rows = c(1, 3, 4, 6)) |>
+  text_transform(
+    cells_body(columns = c(Tolerance, Expulsion), rows = c(2, 5)),
+    fn = \(x) local_image(filename = glue("graphics-manual/out/{x}.png"))
+  ) |>
+  tab_style(
+    style = cell_borders(sides = "all", color = NULL),
+    locations = cells_body()
+  ) |>
+  tab_style(
+    style = cell_borders(
+      sides = "top",
+      color = "#D3D3D3",
+      weight = px(2)
+    ),
+    locations = cells_body(columns = everything(), rows = c(4))
+  ) |>
+  tab_style(
+    style = cell_text(v_align = "top"),
+    locations = cells_body()
+  ) |>
+  tab_style(
+    style = cell_text(align = "center"),
+    locations = cells_column_labels(columns = everything())
+  ) |> 
+  tab_style(
+    style = cell_fill("#FCF2E6"),
+    locations = cells_row_groups()
+  ) |> 
+  tab_style(
+    style = cell_fill("#EFECF4"),
+    locations = cells_column_spanners()
+  ) |> 
+  tab_options(
+    quarto.disable_processing = TRUE,
+    column_labels.border.top.color = "#ffffff",
+    column_labels.font.weight = "bold",
+    stub_row_group.border.color = "#ffffff",
+    stub_row_group.font.weight = "bold",
+    heading.align = "center",
+    row_group.as_column = TRUE
+  )
+```
+
+The relationship between INGOs and regimes is dynamic, and shifts in INGO flexibility and de facto regime civil society regulations can create different practical operating environments, demonstrated in @tbl-theory-grid.
 For instance, there are two circumstances where INGOs will feel less restricted.
-First, as seen in the top left quadrant of @fig:theory-grid, if the distance between the two parties' ideal points is short and the negotiation spaces overlap—as with INGOs providing non-contentious programming like disaster relief, humanitarian services, or education—INGOs will be cooperative and face a tolerant operating environment.
+First, as seen in the top left quadrant of @tbl-theory-grid, if the distance between the two parties' ideal points is short and the negotiation spaces overlap—as with INGOs providing non-contentious programming like disaster relief, humanitarian services, or education—INGOs will be cooperative and face a tolerant operating environment.
 Because of preference alignment, these INGOs will not need to rely on their flexibility to maintain access to their host countries.
 
-More contentious organizations with preferences that diverge from the regime's ideal point, on the other hand, can also face a tolerant environment as long as they have a large amount of programmatic flexibility (see bottom left quadrant of @fig:theory-grid).
-For example, @Heiss:2019 explores how human rights INGOs advocate for democratization, political reform, and increased respect for human rights by relying on networks of field offices, funded by dozens of private foundations and government grants—resources that give these organizations the flexibility to remain in their host countries and maintain a fairly tolerant operating environment.
+More contentious organizations with preferences that diverge from the regime's ideal point, on the other hand, can also face a tolerant environment as long as they have a large amount of programmatic flexibility (see bottom left quadrant of @tbl-theory-grid).
+For example, @Heiss:2019a explores how human rights INGOs advocate for democratization, political reform, and increased respect for human rights by relying on networks of field offices, funded by dozens of private foundations and government grants—resources that give these organizations the flexibility to remain in their host countries and maintain a fairly tolerant operating environment.
 
 Likewise, there are two circumstances where INGOs will feel restricted, or even expelled.
-Most often, organizations that face restricted operating environments engage in contentious programming and work in countries where regimes have limited de facto regulatory environments, leaving little room for negotiation or overlap (see bottom right quadrant of @fig:theory-grid).
-In contrast, INGOs that are naturally less contentious and more prone to compliance can face expulsion if they lack flexibility or it the civil society regulatory environment is too constrained (see top right quadrant of @fig:theory-grid).
+Most often, organizations that face restricted operating environments engage in contentious programming and work in countries where regimes have limited de facto regulatory environments, leaving little room for negotiation or overlap (see bottom right quadrant of @tbl-theory-grid).
+In contrast, INGOs that are naturally less contentious and more prone to compliance can face expulsion if they lack flexibility or it the civil society regulatory environment is too constrained (see top right quadrant of @tbl-theory-grid).
+For instance, TODO in 2015, less contentious INGOs like Mercy Corps were restricted after India's de facto environment constricted [@Carothers:2015].
+No formal laws were changed, but the amount of leeway granted to INGOs shrunk considerably and Modi's government froze assets and cancelled registrations of hundreds of INGOs.
 
@@
 
+Growing body of work on the government side of the the model, looking at how and why regimes regulate INGOs and why they differentially enforce regulations.
+Less work has been done on the INGO side… TODO
+ There is extensive cross-country research on the relationship between restrictive governments and *domestic* institutions like civil society [@FrantzKendall-Taylor:2014; @Kendall-TaylorFrantz:2014a; @FrantzEzrow:2011], as well as detailed case studies of specific regimes [@Chen:2012; @Teets:2014; @Hildebrandt:2013], and cross-national quantitative work [@DeMattee; @that-one-group-in-europe], but few studies have examined the motivations and strategies of INGOs themselves.
+
 Studying INGO responses to legal regulations—particularly for organizations working in highly restrictive countries—poses a difficult methodological challenge.
-There is extensive cross-country research on the relationship between restrictive governments and *domestic* institutions like civil society [@FrantzKendall-Taylor:2014; @Kendall-TaylorFrantz:2014a; @FrantzEzrow:2011], as well as detailed case studies of specific regimes [@Chen:2012; @Teets:2014; @Hildebrandt:2013], and cross-national quantitative work [@DeMattee; @that-one-group-in-europe], but few studies have examined the motivations and strategies of INGOs themselves.
 
@@
 
-Complete technical details of the survey are provided in the online appendix.
+Complete technical details of the survey are provided in the appendix.
 I define an INGO as any organization that is not incorporated as a governmental entity or as a profit-seeking private firm that conducts advocacy, provides services, or otherwise works in at least *one* country other than the one it is headquartered in.
@@
 Respondents span the globe and work on a wide variety of issues and policies.
-The sample of INGOs have their headquarters spread across 93 different countries (see @fig:hq-countries), with roughly two thirds based in either Europe or the Americas, primarily in the US, UK, and Switzerland (see left panel of @fig:work-hq-regions).
+The sample of INGOs have their headquarters spread across 93 different countries (see @fig-hq-countries), with roughly two thirds based in either Europe or the Americas, primarily in the US, UK, and Switzerland (see left panel of @fig-work-hq-regions).
 
-![Countries where INGOs are headquartered](../../Output/figures/3-hq-countries){#fig:hq-countries}
+```{r}
+#| label: fig-hq-countries
+#| fig-width: 6
+#| fig-asp: 0.542
+#| fig-cap: "Countries where INGOs are headquartered"
+#| include: true
+# Through lots of trial and error, I found that the best size for this map that
+# eliminates extra whitespace on the top/bottom and left/right is 6x3.25, or an
+# aspect ratio of 0.542ish
 
-![Regions where INGOs are headquartered vs. regions about which INGOs answered questions](../../Output/figures/3-work-hq-regions){#fig:work-hq-regions}
+df_hq_countries <- survey_orgs |>
+  group_by(Q2.2_iso3) |>
+  summarize(num_ngos = n()) |>
+  ungroup() |>
+  mutate(
+    num_ngos_ceiling = ifelse(num_ngos >= 30, 30, num_ngos),
+    ngo_presence = ifelse(num_ngos >= 1, "At least one NGO respondent", NA),
+    prop = num_ngos / sum(num_ngos, na.rm = TRUE)
+  ) |>
+  mutate(country_name = countrycode(Q2.2_iso3, "iso3c", "country.name")) |>
+  arrange(desc(num_ngos))
+
+map_hq <- world_map |> 
+  left_join(df_hq_countries, by = join_by(ISO_A3 == Q2.2_iso3)) |> 
+  # Remove Fiji for the sake of plotting
+  filter(ISO_A3 != "FJI")
+
+ggplot() +
+  geom_sf(
+    data = map_hq, aes(fill = num_ngos_ceiling, text = ISO_A3),
+    linewidth = 0.1, color = "grey30"
+  ) +
+  scale_fill_binned(
+    low = clrs$Peach[1], high = clrs$Peach[7], na.value = "grey95",
+    labels = c(1, 10, 20, "30+"), breaks = c(1, 10, 20, 30),
+    name = "Number of NGOs: ",
+    guide = guide_colorsteps(
+      barwidth = 7, barheight = 0.4,
+      title.vjust = 1
+    )
+  ) +
+  coord_sf(crs = "+proj=robin") +
+  theme_ingo_map()
+```
+
+```{r}
+#| label: fig-work-hq-regions
+#| include: true
+#| fig-width: 4
+#| fig-height: 2
+#| out-width: "80%"
+#| fig-cap: "Regions where INGOs are headquartered vs. regions about which 
+#|   INGOs answered questions"
+
+continents_marked <- survey_orgs |>
+  select(home = Q2.2_iso3, target = Q2.5_iso3) |>
+  unnest(target) |> 
+  mutate(across(c(home, target), 
+                list(continent = ~countrycode(., "iso3c", "continent",
+                                              custom_match = c("XKX" = "Europe"))))) |> 
+  mutate(across(ends_with("_continent"),
+                ~recode(., Oceania = "Asia & Oceania", Asia = "Asia & Oceania"))) |> 
+  group_by(home_continent, target_continent) |>
+  summarize(times_marked = n()) |> 
+  ungroup() |> 
+  mutate(id = 1:n()) |> 
+  pivot_longer(ends_with("continent"), names_to = "x", values_to = "continent") |> 
+  mutate(continent_total = sum(times_marked), .by = x) |> 
+  group_by(x, continent) |> 
+  mutate(prop = sum(times_marked) / continent_total) |> 
+  ungroup() |> 
+  mutate(nice_label = glue(
+    '{continent}<br><span style="font-size: 6.5px">{label_percent(accuracy = 1)(prop)}</span>'
+  ))
+
+ggplot(
+  continents_marked,
+  aes(x = x, y = times_marked, stratum = continent, alluvium = id, fill = continent)
+) +
+  geom_flow() +
+  geom_stratum(color = "grey30", alpha = 0.5, linewidth = 0.1) +
+  geom_richtext(
+    fill = NA, label.color = NA, label.padding = grid::unit(rep(0, 4), "pt"),
+    stat = "stratum", aes(label = nice_label, color = continent), 
+    size = 2.2, lineheight = 0.9,
+    family = "Fira Sans Semibold"
+  ) +
+  scale_x_discrete(
+    labels = c("Home region", "Target region"),
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(expand = c(0, 0)) +
+  scale_fill_manual(
+    values = c(clrs$Prism[6], clrs$Prism[8], clrs$Prism[11], clrs$Prism[2]),
+    guide = "none"
+  ) +
+  scale_color_manual(
+    values = colorspace::darken(c(
+      clrs$Prism[6], clrs$Prism[8],
+      clrs$Prism[11], clrs$Prism[2]
+    ), 0.5),
+    guide = "none"
+  ) +
+  labs(x = NULL, y = NULL) +
+  theme_ingo() +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    axis.text.x = element_text(family = "Fira Sans Semibold", size = rel(0.7)),
+    axis.text.y = element_blank()
+  )
+```
 
@@
 In total, INGOs answered questions about their work in 148 different countries.
-The regional distribution of INGO target countries reflects their broader scope and is almost a mirror image of these organizations' home regions—nearly two-thirds of respondents answered questions about their work in Africa and Asia (see right panel of @fig:work-hq-regions), the most underrepresented regions for NGO headquarters.
+The regional distribution of INGO target countries reflects their broader scope and is almost a mirror image of these organizations' home regions—nearly two-thirds of respondents answered questions about their work in Africa and Asia (see right panel of @fig-work-hq-regions), the most underrepresented regions for NGO headquarters.
 This disparity could reflect the fact that INGOs from the Global South without a clear English-language internet presence were excluded from the sample, but the pattern also corresponds to similar findings in other surveys of global NGOs [@Limoncelli:2016; @HeissKelley:2016; @FootToftCesare:2015], reinforcing the idea that Northern-based NGOs tend to focus their work in the South.
@@
 
-Building on these critiques, a new trend emerged that treated transnational actors as simultaneously normative and strategic [@Cooley:2002; @Keck:1999; @Kelley:2009a].
+Building on these critiques, a new trend emerged that treated transnational actors as simultaneously normative and strategic [@Cooley:2002; @Keck:1998; @Kelley:2009a].
 @MitchellSchmitz:2014 summarized this debate with their theory of nonprofit principled instrumentalism, or the notion that INGOs must balance their normative mission-driven principles against the instrumental needs of organizational survival.
@@
 INGOs are motivated primarily by their foundational mission and values, and they structure their strategies around this vision to ensure that their programming furthers their mission [@Moore:2000].
-Survey respondents confirm this motivation, describing their core mission both in aspirational terms, including "fighting poverty and holding leaders accountable,"[^4] encouraging "awareness and pro-action towards sustainable development,"[^5] and promoting "democracy and open society" and "governments' respect for the human rights of children";[^6] and through more specific statements, such as "improv[ing] healthcare, specifically neurological services, in the least developed nations,"[^7] or ending "the use of immigration detention around the world."[^8]
+Survey respondents confirm this motivation, describing their core mission both in aspirational terms, including "fighting poverty and holding leaders accountable,"[^1193] encouraging "awareness and pro-action towards sustainable development,"[^1267] and promoting "democracy and open society" and "governments' respect for the human rights of children";[^1328_1252] and through more specific statements, such as "improv[ing] healthcare, specifically neurological services, in the least developed nations,"[^1257] or ending "the use of immigration detention around the world."[^1376]
 
-Most respondents report a tight link between programs and missions, stating that "[o]ur mission, values and vision are reflected in everything that we do," that "all our work is geared towards the accomplishment of this objective," and that "our approach matches our mission precisely."[^9] For many organizations, the "mission and values are the reason we work on these objectives"[^10]—the normative goals of the organization provide strong motivation to engage in pro-social advocacy and services.
+Most respondents report a tight link between programs and missions, stating that "[o]ur mission, values and vision are reflected in everything that we do," that "all our work is geared towards the accomplishment of this objective," and that "our approach matches our mission precisely."[^1245_1267_1272] For many organizations, the "mission and values are the reason we work on these objectives"[^1643]—the normative goals of the organization provide strong motivation to engage in pro-social advocacy and services.
 Specific programming strategies are also closely linked to INGO missions.
-For instance, an organization working in South Asia has ambitions to "[b]uild the capacity of local organisations to equip adolescent girls to access their rights and address gender inequality through sport." As expected, much of their programming is centered on sports education and leadership training, but importantly, the organization makes a point that nothing they do is implemented directly: because their core mission is to build local capacity, they ensure that "all the work we do is through local organisations."[^11] Organizations thus work to ensure that their strategies align with and reflect their core missions, visions, and values.
+For instance, an organization working in South Asia has ambitions to "[b]uild the capacity of local organisations to equip adolescent girls to access their rights and address gender inequality through sport." As expected, much of their programming is centered on sports education and leadership training, but importantly, the organization makes a point that nothing they do is implemented directly: because their core mission is to build local capacity, they ensure that "all the work we do is through local organisations."[^1799] Organizations thus work to ensure that their strategies align with and reflect their core missions, visions, and values.
 
@@
 
-The distance between the government's preferences for a given issue and an INGO's core mission and vision for that issue determine how contentious their relationship will be, ranging from cooperative to antagonistic (see @fig:theory-dot-distance).
+The distance between the government's preferences for a given issue and an INGO's core mission and vision for that issue determine how contentious their relationship will be, ranging from cooperative to antagonistic.
 This distance, in turn, influences how governments regulate INGO work.
@@
 Organizations working on issues that align with regime preferences will be treated more favorably and with less regulatory pressure than INGOs working on more threatening, less aligned issues.
-
-![Distance between regime and INGO ideal points: contentiousness of relationship](../../Graphics/theory-dot-distance){#fig:theory-dot-distance}
 
@@
 These resources are what allow INGOs to pursue their principled ideals in the first place—they provide organizations with the flexibility to engage in programming and adapt to the political and regulatory environments they face.
-The region surrounding the organization's ideal point represents its reserve of *programmatic* flexibility (see @fig:theory-ngo-space), or the organization's ability and willingness to make changes to its programs in response to regulations.
-
-![Space around INGO ideal point: instrumental flexibility](../../Graphics/theory-ngo-space){#fig:theory-ngo-space}
+The region surrounding the organization's ideal point represents its reserve of programmatic flexibility, or the organization's ability and willingness to make changes to its programs in response to regulations.
 
@@
 Given their frequency, the regulatory changes INGOs observe do not necessarily correlate with formal statutory developments.
-These laws give bureaucrats and politicians significant interpretive leeway, however, and allow them to reshape the regulatory environment for international NGOs [@TODO-chaudhry-heiss-2022].
+These laws give bureaucrats and politicians significant interpretive leeway, however, and allow them to reshape the regulatory environment for international NGOs [@ChaudhryHeiss:2022].
 Because of this dynamic discretionary de facto environment, INGOs actively seek out information about changes in laws, rules, and regulations.
@@
 
-[^1]:	Cairo Institute for Human Rights Studies, "After 20 years: CIHRS moves its regional and international programs outside Egypt," accessed August 2, 2017, [http://www.cihrs.org/?p=10298&lang=en](http://www.cihrs.org/?p=10298&lang=en).
+---
+
+Can apply to other situations, like looking at regime laws or other stuff like that
 
@@
 
-[^3]:	The best way to understand the theory is to visit an explorable explanation at [ingorestrictions.org/theory/](https://ingorestrictions.org/theory/) and see the different outcomes dynamically [@Gourarie:2016].
+[^1193]: Response 1193.
 
-[^4]:	Response 1193.
+[^1267]: Response 1267.
 
-[^5]:	Response 1267.
+[^1328_1252]: Responses 1328 and 1252.
 
-[^6]:	Responses 1328 and 1252.
+[^1257]: Response 1257.
 
-[^7]:	Response 1257.
+[^1376]: Response 1376.
 
-[^8]:	Response 1376.
+[^1245_1267_1272]: Response 1245, 1267, and 1272.
 
-[^9]:	Response 1245, 1267, and 1272.
+[^1643]: Response 1643.
 
-[^10]:	Response 1643.
-
-[^11]:	Response 1799.
+[^1799]: Response 1799.
 
@@
  $P(\% \text{ Very restricted}_\text{Autocracies} - \% \text{ Not restricted}_\text{Autocracies} > 0) = 1$.
+
+\newpage
+
+# References
+
+::: {#refs}
+:::
+
+\newpage
+
+:::: {#appendix-count}
+
+# Appendix
+
+::::

### 2023-12-22 R/funs_graphics.R

@@ -30,6 +30,7 @@ theme_ingo <- function(base_size = 11, base_family = "Fira Sans") {
           axis.title.x = element_text(hjust = 0, margin = margin(t = 10)),
           axis.title.y = element_text(hjust = 1, margin = margin(r = 10)),
           legend.position = "bottom",
+          legend.text = element_text(size = rel(0.7)),
           legend.title = element_text(size = rel(0.7), vjust = 0.5,
                                       family = "Fira Sans", face = "plain"),
           legend.key.size = unit(0.7, "line"),

### 2023-12-22 manuscript/manuscript.qmd
Substantial edits to theory section

@@
 
+::: {.content-visible when-format="html"}
+# Introduction {.hide}
+:::
+
 Lots of work on closing space - DPR2015
+
+@ChristensenWeinstein:2013; @DupuyRonPrakash:2015; @DupuyRonPrakash:2016; @BakkeMitchellSmidt:2020
 
@@
 
-I use an adaptation of negotiation theory [@Raiffa:1982; @Mayer:2010] to conceptualize this dynamic relationship between governments and INGOs.
-I represent the interaction between regimes and INGOs in any given issue area (human rights, development, advocacy, etc.) in simple two-dimensional policy space (see @fig-theory-full).
-Each actor has a preference for a certain level of advocacy or service provision, marked as solid circles in the figure.
-Governments set *de jure* policies to prevent INGO activities from going beyond the regime's ideal point, while INGOs will engage in programming that, when possible, fits within the bounds set by the regime.
-Each actor has a range of flexibility in the implementation of their regulations or their programming, shown in the horizontal lines flanking the ideal points.
-The space where the two ranges overlap determines both the regime's *de facto* level of restrictions and the INGO's actual mix of programming in that country and constitutes the practical operating environment for the INGO.
-
 ```{r}
@@
 
-A regime's preferences comprise two components: (1) formal *de jure* legislation, represented by the ideal point, and (2) *de facto* implementation of those policies, represented by the negotiation space around the ideal point.
+I conceptualize this dynamic relationship between governments and INGOs using an adaptation of negotiation theory [@Raiffa:1982; @Mayer:2010].
+I represent the interaction between regimes and INGOs in any given issue area (human rights, development, advocacy, etc.) in simple two-dimensional policy space (see @fig-theory-full).
+Each actor has a preference for a certain level of contentiousness in INGO advocacy or service provision.
+Regime preferences comprise two components: (1) formal *de jure* legislation, marked as a point, and (2) *de facto* implementation of those policies, represented by the space around the ideal point.
 Regimes establish a regulatory environment for international civil society that ranges in permissiveness—some countries allow for a large degree of contentious INGO activity, while others are highly restrictive and provide little room for dissonance.
-In turn, and analogous to the regime's preferences, an INGO's negotiation preferences comprise two components: (1) the organization's normative principles and ideals, represented by the ideal point, (2) the organization's programmatic flexibility in actually implementing those principles, represented by the negotiation space.
-INGOs have a desire to engage in a certain level of advocacy, generally defined by their mission, vision, and values.
-INGOs with more instrumental flexibility—that is, a diverse menu of programs, professionalized staff, consistent revenue streams, and collaborative relationships with governments, foundations, and other NGOs—can fine tune their programs to fit the regulatory environments they face, while those with less flexibility are less able to make such adjustments.
 
-The interaction between the actors' negotiation positions introduces two additional dynamics that are crucial for determining how authoritarian regimes regulate INGOs and how well INGOs can respond correspondingly.
-First, the distance between the two parties ideal points determines the contentiousness of their relationship.
+In turn, INGO preferences comprise two components: (1) the organization's normative principles and ideals, represented the point, and (2) the organization's programmatic flexibility in actually implementing those principles, represented by the space around the point.
+INGOs have a desire to engage in a certain level of contentiousness programming, defined by their mission, vision, and values.
+INGOs with more programmatic flexibility—that is, a diverse menu of programs, professionalized staff, consistent revenue streams, and collaborative relationships with governments, foundations, and other NGOs—can fine tune their programs to fit the regulatory environments they face, while those with less flexibility are less able to make such adjustments.
+
+The interaction between the actors' positions introduces two additional dynamics that are crucial for determining how governments regulate INGOs and how well INGOs can respond.
+First, the distance between the two parties' ideal points determines the nature of their relationship.
 INGOs that engage in programming close to the regime's preferences are naturally more cooperative, either providing services that the government needs or advocating for issues that are unlikely to lead to political instability.
-Accordingly, INGOs that are more cooperative will be *compliant* with the legal limits imposed by the regime.
+Accordingly, INGOs that are more cooperative will be *cooperative* with the legal limits imposed by the regime.
 Organizations that pursue more contentious programming further from the regime's ideal point, on the other hand, will have an *antagonistic* relationship and will be more likely to openly resist the restrictions imposed on them.
@@
 The relationship between INGOs and regimes is dynamic, and shifts in INGO flexibility and de facto regime civil society regulations can create different practical operating environments, demonstrated in @tbl-theory-grid.
-For instance, there are two circumstances where INGOs will feel less restricted.
-First, as seen in the top left quadrant of @tbl-theory-grid, if the distance between the two parties' ideal points is short and the negotiation spaces overlap—as with INGOs providing non-contentious programming like disaster relief, humanitarian services, or education—INGOs will be cooperative and face a tolerant operating environment.
-Because of preference alignment, these INGOs will not need to rely on their flexibility to maintain access to their host countries.
+For instance, INGOs can enjoy a tolerant practical operating environment when facing both cooperative and antagonistic relationships with the host government.
+The environment will be tolerant and cooperative when the distance between the two parties' ideal points is small and the negotiation spaces overlap, as with INGOs like the Red Cross and Oxfam, which provide non-contentious programming like disaster relief or humanitarian services.
+More antagonistic organizations with preferences that diverge from the regime's ideal point, on the other hand, can also face a tolerant environment as long as (1) the regime provides substantial openness and freedom for advocacy when enforcing its laws, and (2) the organizations have a large amount of flexibility in pursuing their programs.
+For instance, advocacy organizations like Amnesty International or Reporters Without Borders often target democratic governments that violate human rights but do not face expulsion from those countries because of robust associational laws that permit such advocacy.
+Because of the alignment of the practical operating environment, INGOs in both situations are tolerated by their host governments and maintain access to the country.
 
-More contentious organizations with preferences that diverge from the regime's ideal point, on the other hand, can also face a tolerant environment as long as they have a large amount of programmatic flexibility (see bottom left quadrant of @tbl-theory-grid).
-For example, @Heiss:2019a explores how human rights INGOs advocate for democratization, political reform, and increased respect for human rights by relying on networks of field offices, funded by dozens of private foundations and government grants—resources that give these organizations the flexibility to remain in their host countries and maintain a fairly tolerant operating environment.
-
-Likewise, there are two circumstances where INGOs will feel restricted, or even expelled.
-Most often, organizations that face restricted operating environments engage in contentious programming and work in countries where regimes have limited de facto regulatory environments, leaving little room for negotiation or overlap (see bottom right quadrant of @tbl-theory-grid).
-In contrast, INGOs that are naturally less contentious and more prone to compliance can face expulsion if they lack flexibility or it the civil society regulatory environment is too constrained (see top right quadrant of @tbl-theory-grid).
-For instance, TODO in 2015, less contentious INGOs like Mercy Corps were restricted after India's de facto environment constricted [@Carothers:2015].
-No formal laws were changed, but the amount of leeway granted to INGOs shrunk considerably and Modi's government froze assets and cancelled registrations of hundreds of INGOs.
+At the core of the phenomenon of closing civic space is the fact that INGOs can feel restricted—or even expelled—regardless of whether their relationship with the host government is cooperative or antagonistic.
+INGOs that have a naturally antagonistic relationship with their host governments—for instance, human rights organizations targeting authoritarian states—can face a limited (or even nonexistent) practical operating environment if the de facto civil society regulatory environment is highly constricted.
+These organizations can still work under restrictive conditions as long as they can rely on their programmatic flexibility.
+For example, @Heiss:2019a explores how human rights INGOs in the Middle East advocate for democratization, political reform, and increased respect for human rights by relying on networks of field offices, funded by dozens of private foundations and government grants—resources that give these organizations the flexibility to remain in their host countries and maintain a narrow practical operating environment.
+INGOs that (1) lack this flexibility, or that (2) hope to work in countries with overly constricted civil society regulations—face expulsion.
+In contrast, INGOs that have a naturally more cooperative relationship with their host governments can also face restrictions if they lack flexibility or it the civil society regulatory environment becomes too constrained.
+For instance, in the wake of shifts in domestic political dynamics, non-contentious humanitarian INGOs like Mercy Corps were restricted after India's de facto environment constricted in 2015 [@Carothers:2015].
+No formal laws were changed, but the amount of leeway granted to INGOs shrunk considerably as Narendra Modi's government froze assets and cancelled registrations of hundreds of INGOs.
 
